### 2024-08-27 paper/ms.tex
Add paper

\documentclass[linenumbers, twocolumn]{aastex631}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{newtxtext,newtxmath}
\usepackage{hyperref}
\usepackage{gensymb}
\usepackage{enumitem}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\Msun}{\ensuremath{M_{\odot}}}
\newcommand{\Gyr}{\ensuremath{\textrm{Gyr}}}
\newcommand{\Myr}{\ensuremath{\textrm{Myr}}}
\newcommand{\yr}{\ensuremath{\textrm{yr}}}
\newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
\newcommand{\pc}{\ensuremath{\textrm{pc}}}
\newcommand{\kms}{\ensuremath{\textrm{km}/\textrm{s}}}
\newcommand{\tocite}{\textcolor{blue}{cite}}
\newcommand{\FeH}{\ensuremath{[\textrm{Fe}/\textrm{H}]}}
\newcommand{\MgFe}{\ensuremath{[\textrm{Mg}/\textrm{Fe}]}}
\newcommand{\OFe}{\ensuremath{[\textrm{O}/\textrm{Fe}]}}
\newcommand{\alphaFe}{\ensuremath{[\alpha/\textrm{Fe}]}}
\newcommand{\tform}{\ensuremath{t_{\textrm{form}}}}
\newcommand{\dex}{\ensuremath{\textrm{dex}}}
\newcommand{\Msunyr}{\ensuremath{\Msun/\textrm{yr}}}

\newcommand{\red}[1]{\textcolor{red}{#1}}

% \received{March 1, 2021}
% \revised{April 1, 2021}
%\accepted{\today}

\shorttitle{The Milky Way's Phoenix Phase}
\shortauthors{Beane et al.}

\graphicspath{{./}{fig/}}

\begin{document}

\title{Something something}

\author{Angus Beane}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}

\author{James W. Johnson}
\affiliation{The Observatories of the Carnegie Institution for Science, Pasadena, CA, USA}

\author{Vadim Semenov}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}

\author{Lars Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}

\author{et al}

\begin{abstract}
    The Milky Way is known to host at least two modes in the present day distribution of chemical abundances. The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive sattelite (Gaia-Sausage-Enceladus) at $z\sim2$. However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality. We present a case study of a galaxy at $z=1.5$ in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase. In the fiducial simulation, this galaxy does not host any multimodality in its chemical abundance plane. However, when an artificial slope in \alphaFe{} as a function of time is added (older stars are given boosted \alphaFe{}), we show that the distribution becomes strikingly multimodal. This suggests that, for this creation avenue, multimodality can only be created at times when \alphaFe{} is rapidly declining, as expected at high-$z$. It also provides additional support that models must produce galaxies with this declination. We suggest that TNG50 fails in this respect because the resolved star formation efficiency at high densities is too low.
  \end{abstract}

  \keywords{Classical Novae (251) --- Ultraviolet astronomy(1736) --- History of astronomy(1868) --- Interdisciplinary astronomy(804)}

\section{Introduction}\label{sec:intro}
For most elements, their stellar surface abundances retain the composition of their natal gas cloud. Therefore, the present-day distribution of stellar surface abundances encodes the chemical history of a galaxy. Two elements have received particular interest in the Milky Way: Fe and $\alpha$-elements (elements produced through the $\alpha$-process). Fe is produced in both Type Ia and Type II SNe whereas $\alpha$-elements are produced predominantly through Type II SNe. Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr for Type Ia), the ratio between $\alpha$-elements and Fe generally decreases with time.

This decline of \alphaFe{} over time has long been recognized \citep{1979ApJ...229.1046T}. This trend is only generally true, though, with non-monotonic behavior observed in observations and even one-zone chemical models \citep[e.g.][]{2022arXiv220402989C}.

Two types of supernovae (SNe) are responsible for most of the production of Fe and $\alpha$-elements: Type II and Type Ia \citep{2023A&ARv..31....1A}. Type II SNe originate from massive stars whose lifetimes are rather short (10s of Myr). Type Ia SNe, on the other hand, are thought to originate from white dwarfs whose masses have exceeded the Chandrasekar limit due to accretion from a donor star.

\section{Methods}\label{sec:methods}
\subsection{IllustrisTNG Sample}\label{ssec:tng}
We have made use of the Illustris TNG50 simulation \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$) It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG model \citep{2017MNRAS.465.3291W, 2018MNRAS.473.4077P}. This model includes several subgrid processes: a wind generation model, chemical enrichment from supernovae and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.

Using the public catalog, we selected a sample of subhalos at $z=1.5$ (snapshot 40) according to the following criteria: (1) the subhalo is central (i.e., the most massive subhalo within its halo), and (2) the subhalo's stellar mass is between $10^{10}$ and $10^{10.5}\,\Msun/\textrm{h}$. There were a total of 168 subhalos that met both criteria. The chosen mass range is broadly consistent with the expected mass of the Milky Way at this redshift \citep{2013ApJ...771L..35V}. We chose to make our selection of galaxies at $z=1.5$ instead of at lower redshift because we wished to capture the \textit{formation} of any multimodal structure. We did not want contamination by mergers at lower redshift which we know contribute very little to the Milky Way's disk stars \citep[e.g.][]{2016ARA&A..54..529B}.

\subsection{Observations}\label{ssec:obs}

\section{Results}\label{sec:results}
\subsection{Abundance Plane}\label{ssec:plane}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{fig/172175.pdf}
  \caption{\textbf{Test.}}
  \label{fig:fig1}
\end{figure}

The main result of our paper is given in Figure~\ref{fig:fig1}. Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle column). The colored vertical lines show 1D conditional histograms at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0$ \red{check}. The Milky Way shows a clear bimodal population, with a high-$\alpha$ sequence most clearly distinct from the low-$\alpha$ sequence at low metallicity. The two sequences merge around solar metallicity.

Our subhalo of interest, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column). There is some structure in the $\FeH=-0.75$ and $\FeH=0$ bins, but the peaks are close together ($<0.1\dex$) and the trough-to-peak ratio is high ($\sim1/2$ and $1/5$, respectively). It is not obvious that this distribution would have any structure with observational errors.

The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with an artificial declination in \MgFe{}. Star particles are given an additive offset of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ and $t_{\textrm{form}}$ is the formation time of the star particle. Only stars formed before $z=1.5$ are shown. Here, one can see a striking multimodal structure with three clear modes at $\MgFe\sim0.8$, $0.5$, and $0.2\,\dex$. These modes display more contrasted structure, with the distance between modes increasing (to $\sim0.2\,\dex$) as well as the trough-to-peak ratio decreasing to $\sim0.4$ between the $0.8$ and $0.5$ modes and practically vanishing between the $0.5$ and $0.2$ modes.

\subsection{Time Dependence}\label{sec:timedep}

\section{Discussion}\label{sec:disc}
In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our subhalo of interest. The result is quite simple, and indicates a fairly straightforward conclusion: multimodality is enhanced when \alphaFe{} more strongly declines with time.

\subsection{Cause of $\alpha$ Decline}\label{ssec:sfe}
As discussed in Section~\ref{sec:intro}, it has long been known that the \alphaFe{} ratio should decline with time \red{cite}. This declination is caused by the relative enrichment contribution between Type II and Type Ia SNe, with the former contributing the bulk of the $\alpha$-elements and both contributing to Fe. However, this picture is complicated by the details of galaxy evolution. Inflows and outflows, radial gas transfer, and unmixed local enrichment all have a strong effect on the \alphaFe{} ratio.

A detailed accounting of all these processes is beyond the scope of this work, and much of it is impossible with the sparse snapshot spacing in TNG. However, we do offer one possible explanation for the relatively minor declination of \alphaFe{} in the simulation: the SFE at high surface densities in TNG is too low.

First, we demonstrate the impact of the SFE on the \alphaFe{} ratio using a simple one-zone chemical evolution model with the publicly available code \texttt{VICE}. The details of our setup is given in Section~\red{X}. We vary the star formation timescale, $\tau_{*}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio asa function of time. We find that shorter star formation timescales lead to a more rapid reduction in \MgFe{}. A close match to our subhalo of interest in TNG is not attempted.

In TNG, the SF timescale is set to a fixed value of $2.2\,\Gyr$. However, this value is the SF timescale used to set the SFR of an individual cell. What is relevant for comparison to these models is the SF timescale averaged over some well-mixed region.

\subsection{Full Sample}\label{ssec:fullsamp}

A version of Figure~\ref{fig:fig1} for the rest of the subhalos in our original sample are given in the Appendix. They display a variety of morphologies, likely arising from a similar variety of processes. They are the subject of continuing work.

\begin{acknowledgements}
This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
\end{acknowledgements}

\bibliography{ref}{}
\bibliographystyle{aasjournal}

% \input{src/app.tex}

\end{document}

### 2024-08-28 paper/ms.tex
Insert figures into paper
Add figure captions

@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/392276.pdf}
+  \caption{\textbf{When old stars are $\alpha$-enhanced, our subhalo of interest from TNG displays a prominent bimodality.} The upper left panel shows the distribution in the \MgFe{}-\FeH{} plane of the Milky Way, demonstrating a clear bimodality (data selection given in text).
+The lower left panel shows the 1D histograms of \MgFe{} at fixed \FeH{} values of $-0.5$, $-0.25$, $0$, and $0.25$ (blue, orange, green, and red, respectively).
+In the Milky Way, the bimodality is strongest at low metallicities while disappearing at high metallicities.
+The middle column shows the same plots but for our TNG subhalo of interest (392276) and with the fixed \FeH{} values $0.25\,\dex$ lower.
+No clear bimodality is detected at any metallicity.
+The right column shows the same subhalo but after increasing the \MgFe{} value of star particles formed before $z=1.5$ linearly with formation time (specifically by incrementing \MgFe{} by $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ if $t_{\textrm{form}} < t_{1.5}$, where $t_{1.5}$ is the age of the universe at $z=1.5$).
+A clear bimodality is shown in these panels which, unlike in the Milky Way, is present at all metallicities.}
+  \label{fig:fig1}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/392276_alpha.pdf}
+  \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs in simulation.} The upper panels show \MgFe{} as a function of age for our subhalo in TNG.
+The colors indicate stellar populations at fixed values of \FeH{}, which are the same as in Figure~\ref{fig:fig1}.
+A gap in the relation occurs at an age of approximately $10.75\,\Gyr$, which we indicate with a vertical dashed line.
+The effect of the $\alpha$-enhancement is clear, as it more clearly separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$).
+The lower panels show on the left the Milky Way and on the center and right the data from TNG but with $10\%$ age errors and $0.01\,\dex$ errors in \MgFe{}.
+When the simulations are given these errors, we see that the before and after star particles smear such that the two populations significantly overlap in ages.
+This feature more closely resembles the Milky Way, which displays such populations where the bimodality is strongest -- $\FeH=-0.5$ (blue) and $-0.25$ (orange).}
+  \label{fig:alpha}
+\end{figure*}
+
 \begin{figure}
   \centering
-  \includegraphics[width=\columnwidth]{fig/172175.pdf}
-  \caption{\textbf{Test.}}
-  \label{fig:fig1}
+  \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200.pdf}
+  \caption{\textbf{The evolutionary history of our subhalo of interest.} The upper panel shows the SFH of our subhalo.
+This SFH is generated using the formation times of all star particles in the subhalo at $z=0$.
+In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha}, which delineates the separation between the high- and low-$\alpha$ sequences.
+The gap in ages is naturally associated with a gap in the SFH located at the dashed line.
+The middle panel shows the BH accretion rate as a fraction of the maximum (Eddington) accretion rate across time.
+At early times the accretion rate is high, but the gap in ages is also coincident with a local spike in the accretion rate.
+In the lower panel we show the mass assembly of the halo, given as the mass within the radius that encloses $200\times$ the mean density of the universe.
+In this plot mergers are shown as sudden increases in the halo mass.
+Mergers at very early times when the halo is signifcantly less massive than its $z=0$ mass are not shown, but one can see that no clear merger is associated with the gap in stellar ages.
+Two mergers occur later on at $t\sim9$ and $\sim12\,\Gyr$.}
+  \label{fig:history}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{fig/mgfe_vice.pdf}
+  \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one zone chemical evolution model, described in the text.
+The upper panel shows the evolution over $2\,\Gyr$ of \MgFe{} while the lower panel shows the negative of its time derivative.
+Decreasing the star formation timescale $\tau_{\star}=M_{\textrm{gas}/\textrm{SFR}}$ leads to a more rapid decline in \MgFe{}.
+At its steepest decline ($t\sim0.5\,\Gyr$), an order of magnitude decrease in $\tau_{\star}$ leads to a slope nearly a factor of $2$ larger.
+At later times ($t>1\,\Gyr$), the models with smaller $\tau_{\star}$ reach their steady-state \MgFe{} value more quickly.}
+  \label{fig:vice}
 \end{figure}

### 2024-08-28 paper/ms.tex
Update fig1 text

@@
 
+The main result of our paper is given in Figure~\ref{fig:fig1}.
+Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle and right columns).
+The colored vertical lines show 1D conditional histograms at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at $0.25\,\dex$ higher in the simulations.
+The \MgFe{} values in the lower panels are given offsets in order to reduce overlap.
+The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities.
+The Milky Way shows a clear bimodal population, with a high-$\alpha$ sequence most clearly distinct from the low-$\alpha$ sequence at low metallicity.
+The two sequences merge around solar metallicity.
+
+Our SOI, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column).
+There is some structure in the $\FeH=-0.75$ bin, but at higher metallicity there is only a weak hint at a second mode in the $\FeH=-0.25$ bin.
+
+The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with a post-processed declination in \MgFe{}.
+Star particles formed before $z=1.5$ are given an additive offset of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ and $t_{\textrm{form}}$ is the formation time of the star particle.
+Only stars formed before $z=1.5$ are shown.
+A multimodal structure emerges with three clear modes at $\MgFe\sim0.8$, $0.5$, and $0.2\,\dex$.
+The 1D histograms show that the modes are well-separated, and that the troughs between the modes nearly vanish.
+
 \begin{figure*}

### 2024-08-28 paper/ms.tex
Add alpha tform text

@@
 
+\subsection{Alpha Time Dependence}\label{ssec:alpha_time}
+
 \begin{figure*}
@@
 \end{figure*}
+
+The abundance distributions shown in Figure~\ref{fig:fig1} can be better understood by examining the evolution of \MgFe{} with time of the individual stars/star particles.
+In the upper panels of Figure~\ref{fig:alpha} we show the true distribution of \MgFe{} as a function of time for the fiducial SOI in the middle and for the post-processed, $\alpha$-enhanced subhalo to the right.
+We split  We use age instead of formation time in order to better facilitate comparisons to observations.
+There is a gap in the ages that occurs at an age of  $\sim10.75\,\Gyr$, which we mark with a vertical dashed line.
+Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
+In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly depressed \MgFe{} than stars which form a short time later.
+
+In the lower panels we plot to the left data from the Milky Way and to the middle and right from the fiducial and $\alpha$-enhanced SOI, respectively.
+For the simulations, we add $10\%$ age and $0.01\,\dex$ \MgFe{} errors.
+These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:errors} for plots of the observational errors).
+The error in \MgFe{} is not signficant, but the age error of $1\,\Gyr$ at $10\,\Gyr$ smears out the distribution before and after the dashed line.
+The $\alpha$-enhanced SOI still shows two separate populations in this plot, but they now significantly overlap in age.
+
+The Milky Way distribution (lower left panel) bears some resemblance to the $\alpha$-enhanced SOI.
+In particular, the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively) show what appears to be two populations overlapping in age but nonetheless separated in \MgFe{}.
 

### 2024-08-28 paper/ms.tex
Remove old text

@@
 
-The main result of our paper is given in Figure~\ref{fig:fig1}.
-Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle column).
-The colored vertical lines show 1D conditional histograms at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0$ \red{check}.
-The Milky Way shows a clear bimodal population, with a high-$\alpha$ sequence most clearly distinct from the low-$\alpha$ sequence at low metallicity.
-The two sequences merge around solar metallicity.
-
-Our subhalo of interest, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column).
-There is some structure in the $\FeH=-0.75$ and $\FeH=0$ bins, but the peaks are close together ($<0.1\dex$) and the trough-to-peak ratio is high ($\sim1/2$ and $1/5$, respectively).
-It is not obvious that this distribution would have any structure with observational errors.
-
-The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with an artificial declination in \MgFe{}.
-Star particles are given an additive offset of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ and $t_{\textrm{form}}$ is the formation time of the star particle.
-Only stars formed before $z=1.5$ are shown.
-Here, one can see a striking multimodal structure with three clear modes at $\MgFe\sim0.8$, $0.5$, and $0.2\,\dex$.
-These modes display more contrasted structure, with the distance between modes increasing (to $\sim0.2\,\dex$) as well as the trough-to-peak ratio decreasing to $\sim0.4$ between the $0.8$ and $0.5$ modes and practically vanishing between the $0.5$ and $0.2$ modes.
-
 \subsection{Time Dependence}\label{sec:timedep}

### 2024-08-29 paper/ms.tex
Add evol history results text

@@
 
+\subsection{Evolutionary History}\label{ssec:evol}
+
 \begin{figure}
@@
 \end{figure}
+
+In an effort towards understanding the events in our SOI's history that led to the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of some of its key quantities.
+In the upper panel of Figure~\ref{fig:history}, we show the SFH of our galaxy with the same dashed line as in Figure~\ref{fig:alpha} (at an age of $10.75\,\Gyr$ in that plot is at a time of $\sim3\,\Gyr$ here).
+This SFH is computed from the formation times of all star particles in the subhalo at $z=0$.
+This allows us to compute the SFH at fine time resolution, but also means contamination by accreted stellar debris.
+We see two peaks in the SFH at $t\sim2.5$ and $\sim4.5\,\Gyr$ of an amplitude of about $70$ and $60\,\Msunyr$.
+The dashed line corresponds to a relative drop in the SFR, down to about $10\,\Msunyr$ before quickly recovering.
+
+The middle panel shows the accretion rate of the central black hole as a fraction of the maximum (Eddington) accretion rate.
+Early in its history ($t<2\,\Gyr$), the subhalo experiences high accretion rates.
+The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it switches to the low accretion/radio mode.
+However, at the dashed line there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
+
+The lower panel shows the virial mass of the subhalo, as measured by $M_{200}$ -- the mass within the radius that encloses a region of density $200\times$ the mean density of the universe.
+Early on at $t<4\,\Gyr$ the virial mass grows roughly linearly up to $\sim2\times10^{12}\,\Msun$.
+After that, the virial mass remains roughly constant until sharp increases at $t\sim10$ and $\sim12\,\Gyr$.
+The transition in the virial mass from linear to constant at $t\sim4\,\Gyr$ is followed $1\,\Gyr$ later by a sudden drop in the SFR and BH accretion rate.
 

### 2024-08-29 paper/ms.tex
Add one zone model res text

@@
 
+\subsection{One-Zone Model}\label{ssec:onezone}
+
 \begin{figure}
@@
 
-\subsection{Time Dependence}\label{sec:timedep}
+We showed in Figure~\ref{fig:fig1} that a time-linear $\alpha$-enhancement of old stars (forming before $z=1.5$) led to the emergence of a strong chemical bimodality.
+This $\alpha$-enhancement is equivalent to saying that \alphaFe{} declines more rapdily with time at high-$z$.
+In Figure~\ref{fig:vice} we demonstrate an argument for why this steeper decline in \alphaFe{} might be absent in TNG.
+
+We show in the upper panel the evolution of \MgFe{} of three one zone chemical evolution models which vary the star formation timescale.
+This timescale, $\tau_{\star}$, is the inverse of the star formation efficiency.
+A shorter star formation timescale leads to a more rapid reduction in \MgFe{}.
+In the shortest timescale model, $\tau_{\star}=0.5\,\Gyr$, \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ in $2\,\Gyr$.
+In comparison, the longest timescale model, $\tau_{\star}=5\,\Gyr$ only drops to $\sim0.2\dex$ in the same time.
+
+The lower panel shows the negative of the time derivative of \MgFe{}.
+This panel shows the same behavior, with the slope of the $\tau_{\star}=0.5\,\Gyr$ model peaking at $-0.5\,\dex/\Gyr$ compared to the $5\,\Gyr$ model which peaks at $-0.25\,\dex/\Gyr$.
+After $1\,\Gyr$, the trend starts to reverse, with the longer star formation timescale models declining more rapidly, though at a much reduced rate ($\sim-0.1\,\dex/\Gyr$) than at the peak.
 

### 2024-08-30 paper/ms.tex
Update intro

@@
 Fe is produced in both Type Ia and Type II SNe whereas $\alpha$-elements are produced predominantly through Type II SNe.
-Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr for Type Ia), the ratio between $\alpha$-elements and Fe generally decreases with time.
+Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr for Type Ia), the ratio between $\alpha$-elements and Fe is expected to generally decrease with time.
 
-This decline of \alphaFe{} over time has long been recognized \citep{1979ApJ...229.1046T}.
+Because of their disparate formation channels, the two dimensional plane of \alphaFe{}-\FeH{} has received considerable interest.
+In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
+This bimodal distribution is shown in the upper left panel of Figure~\ref{fig:fig1}.
+
+A more extensive survey of the different proposed formation mechanisms of this bimodality is given in \citet{2024arXiv240707985B}.
+Here, we mention simply that there are two approaches.
+First, the bimodality is a result of internal secular processes that generate the bimodality through radial migration \citep{2009MNRAS.396..203S,2021MNRAS.507.5882S,2023MNRAS.523.3791C} or clump formation \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
+
+Second, the bimodality is generated through gas infall scenarios, either from specific gas accretion episodes from the intergalactic medium \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}, or through a more self-consistent collapse sequence of the circumgalactic medium driven through feedback \citep{2021MNRAS.501.5176K}.
+Third and finally, the bimodality is generated through a merger process, either by enhancing the SFR of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
+The fact that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N}.
+
+In \citet{2024arXiv240707985B} we argued for an alternate formation scenario of the bimodality, for which we provide further support in this work.
+In this scenario, the bimodality is formed through a brief quiescent period in the Galaxy's history.
+During this period, which lasts $\sim300\,\Myr$, two things happen.
+First, as the chemical evolution of the galaxy proceeds fewer stars form.
+Second, because the SFR is lower, $\alpha$-element production drops and so the \alphaFe{} of the gas drops as well.
+The combination of these two effects is what leads to the valley in between the high- and low-$\alpha$ sequences.
+
+In that work, we used idealized simulations of a galaxy merger that triggered a starburst which preceded the quiescent period.
+However, we argued that the merger aspect of that work was not necessary, but rather the quiescence.
+In this work, we study a subhalo from the Illustris TNG50 simulation which demonstrates this.
+This subhalo of interest (SoI) exhibits the sequence of events presented in \citet{2024arXiv240707985B} after a simple post-processing step which enhances the \alphaFe{} of old star particles.
+The SoI undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
+
+In Section~\ref{sec:methods} we discuss our selection technique which led to discovering the SoI, as well as a simple one zone chemical evolution model we use to justify our post-processing step.
+In Section~\ref{sec:results} we present the main results which we discuss and interpret in Section~\ref{sec:disc}.
+We conclude in Section~\ref{sec:conc}.
+
+% This decline of \alphaFe{} over time has long been recognized \citep{1979ApJ...229.1046T}.
 This trend is only generally true, though, with non-monotonic behavior observed in observations and even one-zone chemical models \citep[e.g.][]{2022arXiv220402989C}.
-
-Two types of supernovae (SNe) are responsible for most of the production of Fe and $\alpha$-elements: Type II and Type Ia \citep{2023A&ARv..31....1A}.
-Type II SNe originate from massive stars whose lifetimes are rather short (10s of Myr).
-Type Ia SNe, on the other hand, are thought to originate from white dwarfs whose masses have exceeded the Chandrasekar limit due to accretion from a donor star.
 

### 2024-08-30 paper/ms.tex
Title updates
Update abstract

@@
 
-\shorttitle{The Milky Way's Phoenix Phase}
+\shorttitle{Something Something}
 \shortauthors{Beane et al.}
@@
 
-\title{Something something}
+\title{Rising from the Ashes II.: something something}
 
@@
 However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality.
-We present a case study of a galaxy at $z=1.5$ in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase.
-In the fiducial simulation, this galaxy does not host any multimodality in its chemical abundance plane.
-However, when an artificial slope in \alphaFe{} as a function of time is added (older stars are given boosted \alphaFe{}), we show that the distribution becomes strikingly multimodal.
-This suggests that, for this creation avenue, multimodality can only be created at times when \alphaFe{} is rapidly declining, as expected at high-$z$.
-It also provides additional support that models must produce galaxies with this declination.
-We suggest that TNG50 fails in this respect because the resolved star formation efficiency at high densities is too low.
+We present a case study of a subhalo at $z=1.5$ in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase.
+After a minor post-processing step which boosts the \alphaFe{} of old star particles, we demonstrate that this galaxy hosts a strongly bimodal distribution in the \alphaFe{}-\FeH{} plane.
+The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
+The quiescent period in this galaxy is not associated with a merger but some unspecified internal process.
+We argue that the requisite $\alpha$-boosting, post-processing step can be understood as the TNG model underproducing SF in the densest regions at high-$z$.
   \end{abstract}

### 2024-09-02 paper/ms.tex
Add James placeholder to mets
Add obs to methods

@@
 \subsection{Observations}\label{ssec:obs}
+We make use of two observational data sets.
+First, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}.
+We make the same selection cuts as in \citet{2024arXiv240707985B}, described in their Section~2.4.
+These are meant to select only giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's.
+This results in a sample of 54,777 stars.
+We use Fe to track total metallicity and Mg alone as an $\alpha$-element \red{TODO: add any additional details}.
+
+We then further considered a dataset of stellar ages from the APOKASC2 catalog \citep{2018ApJS..239...32P}.
+This uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
+We cross-match this catalog to our larger sample from ASPCAP which results in a sample of 1868 stars.
+
+\subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
+James inserts his bullshit
 

### 2024-09-02 paper/ms.tex
Add disc section on cause of bimodal

@@
 \section{Discussion}\label{sec:disc}
-In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our subhalo of interest.
-The result is quite simple, and indicates a fairly straightforward conclusion: multimodality is enhanced when \alphaFe{} more strongly declines with time.
+In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SOI before and after the $\alpha$-enhancement.
+It is visibly obvious that the TNG SOI is unimodal before the $\alpha$-enhancement and bimodal afterwards (ignoring the minor mode at high-\MgFe{}).
+Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the SOI?, and (2) what justifies the $\alpha$-enhancement?
+We then briefly extend our comparison to the Milky Way data.
+
+\subsection{Cause of Bimodality}\label{ssec:bim_cause}
+An extensive analysis of our SOI is beyond the scope of this project, but here we argue that the evidence is consistent with the scenario presented in \citet{2024arXiv240707985B}.
+They presented an idealized simulation resembling the merger between the Milky Way and GSE.
+They varied the orbital parameters slightly in a grid of 27 simulations and found that simulations which had a brief quiescent period as a result of the merger led to a bimodal abundance distribution.
+They argued that AGN activity was responsible for this brief quenching.
+
+Once the $\alpha$-enhancement post-processing has been done, the SoI that we have studied in this work is consistent with this scenario.
+The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} denotes the transition between the high- and low-$\alpha$ sequences.
+We place it at an age of $10.75\,\Gyr$ or a formation time of $\sim3\,\Gyr$.
+The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} to avoid overlap).
+Stars which formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
+At the line, we see a gap in the $\FeH=-0.5$ and $-0.25$ bins.
+
+The gap in each \FeH{} bin of Figure~\ref{fig:alpha} is contemperaneous with a minimum in the global SFR.
+We can see in the upper panel of Figure~\ref{fig:history} that this dashed line lies almost exactly at the point of a local minimum in the SFH.
+This minimum, which is $\sim10\,\Msunyr$, is 6--7$\times$ smaller than the maxima before and after it.\footnote{A reasonable argument can be made that $10\,\Msunyr$ is hardly quiescent.
+However, for our purposes, it only matters that the SFR at the minimum is small relative to the SFR close in time before and after.
+And besides, this SFH is computed using the formation times of all star particles at $z=0$, which is likely contaminated by later mergers.}
+
+During this period of suppressed SF, we argue that the relative lack of enrichment of Type~II SNe which leads to a lower rate of Mg production.
+This leads to a rapid reduction in \MgFe{}.
+This, combined with a lack of SF in the first place, leads to a scarcity of star particles in the region intermediate between the high- and low-$\alpha$ sequences.
+A more in-depth explanation is given in Section~4.1 in \citet{2024arXiv240707985B}.
+
+In the fiducial TNG distribution shown in the upper middle panel of Figure~\ref{fig:alpha}, the same general behavior with respect to the dashed line is present.
+However, because the \MgFe{} decline before the dashed line is not as strong, star particles which formed before and after the dashed line overlap in the \MgFe{} distribution shown in Figure~\ref{fig:fig1}.
+
+It is also worth noting that in both the fiducial and $\alpha$-enhanced SOI, there is a sort of rebound effect in \MgFe{}.
+The star particles which form directly after the dashed line have a slightly lower \MgFe{} than stars which form after.
+This was seen in Figure~9 of \citet{2024arXiv240707985B}.
+In that work, it was argued that this occurs because during the period of suppressed star formation the \alphaFe{} of star forming gas plummets since there is no contribution from Type~II SNe.
+Later, the \alphaFe{} will recover when the SFR also recovers, but there is a brief window when old, low-$\alpha$ stars can form.
 

### 2024-09-02 paper/ms.tex
Add decrese in alpha plot

@@
 
-\subsection{Cause of $\alpha$ Decline}\label{ssec:sfe}
-As discussed in Section~\ref{sec:intro}, it has long been known that the \alphaFe{} ratio should decline with time \red{cite}.
-This declination is caused by the relative enrichment contribution between Type II and Type Ia SNe, with the former contributing the bulk of the $\alpha$-elements and both contributing to Fe.
-However, this picture is complicated by the details of galaxy evolution.
-Inflows and outflows, radial gas transfer, and unmixed local enrichment all have a strong effect on the \alphaFe{} ratio.
+\subsection{Steepening of $\alpha$ Decline}\label{ssec:sfe}
+As described in Section~\ref{X}, we applied a post-processing to the \MgFe{} of star particles in the TNG simulation.
+Specifically, to star particles formed before $z=1.5$, we added to their \MgFe{} a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time.
+This post-processed subhalo is presented alongside the fiducial subhalo in the right and middle columns, respectively, of Figures~\ref{fig:fig1} and \ref{fig:alpha}.
 
-A detailed accounting of all these processes is beyond the scope of this work, and much of it is impossible with the sparse snapshot spacing in TNG.
-However, we do offer one possible explanation for the relatively minor declination of \alphaFe{} in the simulation: the SFE at high surface densities in TNG is too low.
+The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, and, of course, enrichment models.
+Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy is hardly cause to firmly assert that the fiducial evolution is incorrect.} is not straightforward nor, in our opinion, even possible.
+However, we do offer one reasonable explanation -- the SFE at the high densities more present at high-$z$ is too low.
 
-First, we demonstrate the impact of the SFE on the \alphaFe{} ratio using a simple one-zone chemical evolution model with the publicly available code \texttt{VICE}.
+We demonstrate the impact of the SFE on the \alphaFe{} ratio using a simple one-zone chemical evolution model with the publicly available code \texttt{VICE}.
 The details of our setup is given in Section~\red{X}.
-We vary the star formation timescale, $\tau_{*}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio asa function of time.
-We find that shorter star formation timescales lead to a more rapid reduction in \MgFe{}.
-A close match to our subhalo of interest in TNG is not attempted.
+We vary the star formation timescale, $\tau_{\star}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio asa function of time.
+We find that shorter star formation timescales do lead to a more rapid reduction in \MgFe{}.
+We assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
+Such a difference in the rate occurs between the $\tau_{\star}=0.5$ and $1\,\Gyr$ models at their respective maximum slope magnitudes.
 
@@
 What is relevant for comparison to these models is the SF timescale averaged over some well-mixed region.
+Hassan et al.
+(in preparation) demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude, well within our needed factor of $2$ in $\tau_{\star}$.
+
+Therefore, we think our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified.
 

### 2024-09-02 paper/ms.tex
Add brief cause of qui section

@@
 
-\subsection{Full Sample}\label{ssec:fullsamp}
+\subsection{Cause of Quiescence}\label{ssec:cause_qui}
+It is natural to question why the minimum in the SFR occurs.
+In \citet{2024arXiv240707985B}, AGN activity from a merger was the suspected cause.
+Here, we can see that there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
+Establishing a causal relationship between the two is beyond the scope of the present work, though it is the same suspected cause as in \citet{2024arXiv240707985B}.
 
-A version of Figure~\ref{fig:fig1} for the rest of the subhalos in our original sample are given in the Appendix.
-They display a variety of morphologies, likely arising from a similar variety of processes.
-They are the subject of continuing work.
+% \subsection{Full Sample}\label{ssec:fullsamp}
 

### 2024-09-02 paper/ms.tex
another one

@@
 
-The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, and, of course, enrichment models.
+The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models.
 Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy is hardly cause to firmly assert that the fiducial evolution is incorrect.} is not straightforward nor, in our opinion, even possible.

### 2024-09-02 paper/ms.tex
more serious
Tiny abstract updates

@@
 
-\author{Vadim Semenov}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{Lars Hernquist}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
 \author{et al}
@@
 However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality.
-We present a case study of a subhalo at $z=1.5$ in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase.
+We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase.
 After a minor post-processing step which boosts the \alphaFe{} of old star particles, we demonstrate that this galaxy hosts a strongly bimodal distribution in the \alphaFe{}-\FeH{} plane.
 The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
-The quiescent period in this galaxy is not associated with a merger but some unspecified internal process.
-We argue that the requisite $\alpha$-boosting, post-processing step can be understood as the TNG model underproducing SF in the densest regions at high-$z$.
+The quiescent period in this galaxy is not associated with a merger but some unspecified internal process which leads to AGN activity.
+We argue that the post-processing step can be understood as the TNG model underproducing SF in the densest regions at high-$z$.
   \end{abstract}
@@
 \subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
-James inserts his bullshit
+James inserts his section
 

### 2024-09-02 paper/ms.tex
Add more about how SoI was selected

@@
 We did not want contamination by mergers at lower redshift which we know contribute very little to the Milky Way's disk stars \citep[e.g.][]{2016ARA&A..54..529B}.
+
+We examined the abundance distribution of this sample of subhalos by eye.
+Not many subhalos had multimodal structure, and any structure that was present was relatively weak compared to that observed in the Milky Way.
+We then applied a post-processing to the \MgFe{} of stars by adding to each star particle a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time of each star particle.
+With this post-processing, we found that much more structure was generally present and we selected subhalo 172175 (at snapshot 40) for its particular resemblance to the Milky Way.
+We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
+We refer to this subhalo as our subhalo of interest (SoI).
 
@@
 The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models.
-Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy is hardly cause to firmly assert that the fiducial evolution is incorrect.} is not straightforward nor, in our opinion, even possible.
+Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} is not straightforward nor, in our opinion, even possible.
 However, we do offer one reasonable explanation -- the SFE at the high densities more present at high-$z$ is too low.

### 2024-09-02 paper/ms.tex
More added to disc

@@
 Therefore, we think our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified.
+An intuitive understanding of the impact the decline in \alphaFe{} vs time has is that, when \alphaFe{} declines rapidly, it is a better estimator of age.
+When it is a better estimator of age, events separated temporally better separate in the abundance plane.
+
+\subsection{Comparison to Observations}\label{ssec:compare_obs}
+The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC2 catalog.
+In the bins where the bimodality is strongest (blue and orange, $\FeH=-0.5$ and $-0.25$, respectively), we see that there is a sort of two tiered distribution with significant overlap in age.
+In the SoI with age and abundance errors shown in the lower right panel, a very similar distribution can be seen in all \FeH{} bins.
+An examination of the true distribution in the SoI (upper right panel), we see that the two distributions are in fact very cleanly separated in age.
+Of course, we do not know the true underlying distribution in the Milky Way, but these panels show that the Milky Way is consistent with the general picture shown in our SoI.
 

### 2024-09-02 paper/ms.tex
Add conclusions

@@
 
+\section{Conclusions}\label{sec:conc}
+In this work, we examined a specific subhalo in Illustris TNG50.
+This subhalo is at a Milky Way-progenitor mass at high-$z$ ($z\sim2$).
+After applying a post-processing step that increased the \MgFe{} of star particles formed before $z=1.5$, this subhalo hosts a strong bimodality in the plane of \MgFe{} and \FeH{}, shown in Figure~\ref{fig:fig1}.
+This post-processing is justified by arguing that the SFE of dense gas is too low in TNG (Section~\ref{ssec:sfe}).
+
+This bimodality can be traced to an event that occurred at an age of $10.75\,\Gyr$, or formation time of $\sim3\,\Gyr$ ($z\sim2$).
+Shown as a vertical dashed line in Figure~\ref{fig:alpha}, star particles which form before this form at high-$\alpha$ while stars which form after form at lower $\alpha$.
+At the dashed line, there is a gap.
+We argue that the presence of this gap is responsible for the valley in the bimodality (Figure~\ref{fig:fig1}).
+It is accompanied by a global reduction in the SFR by about a factor of 6 (upper panel of Figure~\ref{fig:history}).
+
+The reduction in the SFR has two effects.
+First, a lower production of Mg is the natural result of a lack of Type~II SNe.
+Second, the lack of SF means that stars at \MgFe{} intermediate between the high- and low-$\alpha$ sequences never form.
+This is the same argument that was first presented in \citet{2024arXiv240707985B}.
+When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the Milky Way's distribution (Section~\ref{ssec:compare_obs}).
+
+This work adds further support that the argument made in \citet{2024arXiv240707985B} is a plausible explanation for the Milky Way's abundance bimodality.
+
 \begin{acknowledgements}

### 2024-09-03 paper/ms.tex
Add follow up sentence
Update title
First pass changes

@@
 
-\shorttitle{Something Something}
+\shorttitle{Abundance Bimodality in TNG}
 \shortauthors{Beane et al.}
@@
 
-\title{Rising from the Ashes II.: something something}
+\title{Rising from the Ashes II: A Hidden Abundance Bimodality in Illustris TNG}
 
@@
 \begin{abstract}
-    The Milky Way is known to host at least two modes in the present day distribution of chemical abundances.
+    The Milky Way is known to host at least two modes in the present day distribution of Fe and $\alpha$-elements.
 The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive sattelite (Gaia-Sausage-Enceladus) at $z\sim2$.
 However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality.
-We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase.
+We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a sequence of starburst, brief quiescence, and then rejuvenation.
 After a minor post-processing step which boosts the \alphaFe{} of old star particles, we demonstrate that this galaxy hosts a strongly bimodal distribution in the \alphaFe{}-\FeH{} plane.
@@
 The quiescent period in this galaxy is not associated with a merger but some unspecified internal process which leads to AGN activity.
-We argue that the post-processing step can be understood as the TNG model underproducing SF in the densest regions at high-$z$.
+We argue that the post-processing step can be understood as the TNG model underproducing star formation in the densest regions at high-$z$.
   \end{abstract}
@@
 \section{Introduction}\label{sec:intro}
-For most elements, their stellar surface abundances retain the composition of their natal gas cloud.
-Therefore, the present-day distribution of stellar surface abundances encodes the chemical history of a galaxy.
-Two elements have received particular interest in the Milky Way: Fe and $\alpha$-elements (elements produced through the $\alpha$-process).
+The stellar surface abundances of most elements retain the composition of their natal gas cloud.
+Therefore, the present-day distribution of stellar surface abundances encodes the chemical history of a galaxy's gas phase.
+Two elements have received particular interest in the Milky Way: Fe and $\alpha$-elements (elements produced through the $\alpha$-process, such as O and Mg).
 Fe is produced in both Type Ia and Type II SNe whereas $\alpha$-elements are produced predominantly through Type II SNe.
-Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr for Type Ia), the ratio between $\alpha$-elements and Fe is expected to generally decrease with time.
+Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr to Gyrs for Type Ia), the ratio between $\alpha$-elements and Fe is expected to generally decrease with time.
 
-Because of their disparate formation channels, the two dimensional plane of \alphaFe{}-\FeH{} has received considerable interest.
+Because of their separate formation channels, the two dimensional plane of \alphaFe{}-\FeH{} has received considerable interest.
 In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
@@
 In this scenario, the bimodality is formed through a brief quiescent period in the Galaxy's history.
-During this period, which lasts $\sim300\,\Myr$, two things happen.
-First, as the chemical evolution of the galaxy proceeds fewer stars form.
+During this period, which lasted $\sim300\,\Myr$ in that setup, two things happen.
+First, as the chemical evolution of the galaxy proceeds, fewer stars form.
 Second, because the SFR is lower, $\alpha$-element production drops and so the \alphaFe{} of the gas drops as well.
@@
 The SoI undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
+Therefore, this work serves as a verification that the scenario in \citet{2024arXiv240707985B} is possible in cosmological simulations and can occur in non-merger scenarios.
 
@@
 \subsection{IllustrisTNG Sample}\label{ssec:tng}
-We have made use of the Illustris TNG50 simulation \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$) It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG model \citep{2017MNRAS.465.3291W, 2018MNRAS.473.4077P}.
+We have made use of the Illustris TNG50 simulation \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$).
+It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG model \citep{2013MNRAS.436.3031V, 2017MNRAS.465.3291W, 2018MNRAS.473.4077P}.
 This model includes several subgrid processes: a wind generation model, chemical enrichment from supernovae and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.
@@
 We chose to make our selection of galaxies at $z=1.5$ instead of at lower redshift because we wished to capture the \textit{formation} of any multimodal structure.
-We did not want contamination by mergers at lower redshift which we know contribute very little to the Milky Way's disk stars \citep[e.g.][]{2016ARA&A..54..529B}.
+We did not want contamination by mergers at lower redshift which we know contribute very little to the Milky Way's disk stars \citep[e.g.,][]{2016ARA&A..54..529B}.
 
-We examined the abundance distribution of this sample of subhalos by eye.
+We examined the abundance distribution in the \MgFe{}-\FeH{} plane of this sample of subhalos by eye.
 Not many subhalos had multimodal structure, and any structure that was present was relatively weak compared to that observed in the Milky Way.
 We then applied a post-processing to the \MgFe{} of stars by adding to each star particle a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time of each star particle.
-With this post-processing, we found that much more structure was generally present and we selected subhalo 172175 (at snapshot 40) for its particular resemblance to the Milky Way.
+With this post-processing, we found that much more structure was generally present.
+We selected subhalo 172175 (at snapshot 40) for its particular resemblance to the Milky Way.
 We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
@@
 The middle column shows the same plots but for our TNG subhalo of interest (392276) and with the fixed \FeH{} values $0.25\,\dex$ lower.
-No clear bimodality is detected at any metallicity.
+Only faint structure is seen in the lowest bin (blue, $-0.75\,\dex$).
 The right column shows the same subhalo but after increasing the \MgFe{} value of star particles formed before $z=1.5$ linearly with formation time (specifically by incrementing \MgFe{} by $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ if $t_{\textrm{form}} < t_{1.5}$, where $t_{1.5}$ is the age of the universe at $z=1.5$).
@@
 Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle and right columns).
-The colored vertical lines show 1D conditional histograms at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at $0.25\,\dex$ higher in the simulations.
+The colored vertical lines show 1D conditional histograms at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations.
 The \MgFe{} values in the lower panels are given offsets in order to reduce overlap.
@@
 
-Our SOI, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column).
-There is some structure in the $\FeH=-0.75$ bin, but at higher metallicity there is only a weak hint at a second mode in the $\FeH=-0.25$ bin.
-
-The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with a post-processed declination in \MgFe{}.
+Our SoI, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column).
+There is some structure in the $\FeH=-0.75$ bin.
+The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with a post-processed declination in \MgFe{} described in Section~\ref{ssec:tng}.
 Star particles formed before $z=1.5$ are given an additive offset of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ and $t_{\textrm{form}}$ is the formation time of the star particle.
-Only stars formed before $z=1.5$ are shown.
 A multimodal structure emerges with three clear modes at $\MgFe\sim0.8$, $0.5$, and $0.2\,\dex$.
@@
 A gap in the relation occurs at an age of approximately $10.75\,\Gyr$, which we indicate with a vertical dashed line.
-The effect of the $\alpha$-enhancement is clear, as it more clearly separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$).
-The lower panels show on the left the Milky Way and on the center and right the data from TNG but with $10\%$ age errors and $0.01\,\dex$ errors in \MgFe{}.
+The effect of the $\alpha$-enhancement is clear, as it separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$).
+The lower panels show on the left the Milky Way and on the center and right the data from TNG but with $15\%$ age errors and $0.01\,\dex$ errors in \MgFe{}.
 When the simulations are given these errors, we see that the before and after star particles smear such that the two populations significantly overlap in ages.
+In the $\alpha$-enhanced SoI, two populations emerge in each bin which overlapped in the fiducial distribution.
 This feature more closely resembles the Milky Way, which displays such populations where the bimodality is strongest -- $\FeH=-0.5$ (blue) and $-0.25$ (orange).}
@@
 The abundance distributions shown in Figure~\ref{fig:fig1} can be better understood by examining the evolution of \MgFe{} with time of the individual stars/star particles.
-In the upper panels of Figure~\ref{fig:alpha} we show the true distribution of \MgFe{} as a function of time for the fiducial SOI in the middle and for the post-processed, $\alpha$-enhanced subhalo to the right.
-We split  We use age instead of formation time in order to better facilitate comparisons to observations.
-There is a gap in the ages that occurs at an age of  $\sim10.75\,\Gyr$, which we mark with a vertical dashed line.
+In the upper panels of Figure~\ref{fig:alpha} we show the true distribution of \MgFe{} as a function of time for the fiducial SoI in the middle and for the post-processed, $\alpha$-enhanced subhalo to the right.
+We use age instead of formation time in order to better facilitate comparisons to observations.
+There is a gap in the ages that occurs at an age of $10.75\,\Gyr$, which we mark with a vertical dashed line.
 Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
@@
 
-In the lower panels we plot to the left data from the Milky Way and to the middle and right from the fiducial and $\alpha$-enhanced SOI, respectively.
-For the simulations, we add $10\%$ age and $0.01\,\dex$ \MgFe{} errors.
+In the lower panels we plot to the left data from the Milky Way and to the middle and right from the fiducial and $\alpha$-enhanced SoI, respectively.
+For the simulations, we add $15\%$ age and $0.01\,\dex$ \MgFe{} Gaussian errors.
 These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:errors} for plots of the observational errors).
-The error in \MgFe{} is not signficant, but the age error of $1\,\Gyr$ at $10\,\Gyr$ smears out the distribution before and after the dashed line.
-The $\alpha$-enhanced SOI still shows two separate populations in this plot, but they now significantly overlap in age.
+The error in \MgFe{} is not signficant, but the age error, which is $1\,\Gyr$ at $10\,\Gyr$, smears out the distribution before and after the dashed line.
+The $\alpha$-enhanced SoI still shows two separate populations in this plot, but they now significantly overlap in age.
 
-The Milky Way distribution (lower left panel) bears some resemblance to the $\alpha$-enhanced SOI.
+The Milky Way distribution (lower left panel) bears some resemblance to the $\alpha$-enhanced SoI.
 In particular, the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively) show what appears to be two populations overlapping in age but nonetheless separated in \MgFe{}.
+These are the bins at which the bimodality is strongest (upper left panel of Figure~\ref{fig:fig1}).
 
@@
 This SFH is generated using the formation times of all star particles in the subhalo at $z=0$.
-In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha}, which delineates the separation between the high- and low-$\alpha$ sequences.
+In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha} ($\sim3\,\Gyr$), which delineates the separation between the high- and low-$\alpha$ sequences.
 The gap in ages is naturally associated with a gap in the SFH located at the dashed line.
 The middle panel shows the BH accretion rate as a fraction of the maximum (Eddington) accretion rate across time.
-At early times the accretion rate is high, but the gap in ages is also coincident with a local spike in the accretion rate.
+The accretion rate is high early on, but then drops.
+The gap in ages (dashed line) is coincident with a local peak in the BH accretion rate.
 In the lower panel we show the mass assembly of the halo, given as the mass within the radius that encloses $200\times$ the mean density of the universe.
-In this plot mergers are shown as sudden increases in the halo mass.
+In this plot mergers are shown as sudden increases in $M_{200}$.
 Mergers at very early times when the halo is signifcantly less massive than its $z=0$ mass are not shown, but one can see that no clear merger is associated with the gap in stellar ages.
-Two mergers occur later on at $t\sim9$ and $\sim12\,\Gyr$.}
+Two mergers occur later on at $t\sim10$ and $\sim12\,\Gyr$.}
   \label{fig:history}
@@
 
-In an effort towards understanding the events in our SOI's history that led to the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of some of its key quantities.
+In an effort towards understanding the events in our SoI's history that led to the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of some of its key quantities.
 In the upper panel of Figure~\ref{fig:history}, we show the SFH of our galaxy with the same dashed line as in Figure~\ref{fig:alpha} (at an age of $10.75\,\Gyr$ in that plot is at a time of $\sim3\,\Gyr$ here).
 This SFH is computed from the formation times of all star particles in the subhalo at $z=0$.
-This allows us to compute the SFH at fine time resolution, but also means contamination by accreted stellar debris.
+This allows us to compute the SFH at fine time resolution.
 We see two peaks in the SFH at $t\sim2.5$ and $\sim4.5\,\Gyr$ of an amplitude of about $70$ and $60\,\Msunyr$.
@@
 Early in its history ($t<2\,\Gyr$), the subhalo experiences high accretion rates.
-The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it switches to the low accretion/radio mode.
-However, at the dashed line there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
+The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it switches to the low accretion radio mode.
+However, at the dashed line ($\sim3\,\Gyr$) there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
 
@@
   \includegraphics[width=\columnwidth]{fig/mgfe_vice.pdf}
-  \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one zone chemical evolution model, described in the text.
-The upper panel shows the evolution over $2\,\Gyr$ of \MgFe{} while the lower panel shows the negative of its time derivative.
+  \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one zone chemical evolution model, described in Section~\ref{ssec:onezone_met}.
+The upper panel shows the evolution of \MgFe{} over $2\,\Gyr$ while the lower panel shows the negative of its time derivative.
 Decreasing the star formation timescale $\tau_{\star}=M_{\textrm{gas}/\textrm{SFR}}$ leads to a more rapid decline in \MgFe{}.
@@
 
-We show in the upper panel the evolution of \MgFe{} of three one zone chemical evolution models which vary the star formation timescale.
-This timescale, $\tau_{\star}$, is the inverse of the star formation efficiency.
-A shorter star formation timescale leads to a more rapid reduction in \MgFe{}.
+We show in the upper panel the evolution of \MgFe{} of three one zone chemical evolution models which vary the star formation (SF) timescale.
+This timescale, $\tau_{\star}$, is the inverse of the SF efficiency.
+A shorter SF timescale leads to a more rapid reduction in \MgFe{}.
 In the shortest timescale model, $\tau_{\star}=0.5\,\Gyr$, \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ in $2\,\Gyr$.
-In comparison, the longest timescale model, $\tau_{\star}=5\,\Gyr$ only drops to $\sim0.2\dex$ in the same time.
+In comparison, the longest timescale model, $\tau_{\star}=5\,\Gyr$ only drops to $\sim0.2\,\dex$ in the same time.
 
@@
 This panel shows the same behavior, with the slope of the $\tau_{\star}=0.5\,\Gyr$ model peaking at $-0.5\,\dex/\Gyr$ compared to the $5\,\Gyr$ model which peaks at $-0.25\,\dex/\Gyr$.
-After $1\,\Gyr$, the trend starts to reverse, with the longer star formation timescale models declining more rapidly, though at a much reduced rate ($\sim-0.1\,\dex/\Gyr$) than at the peak.
+After $1\,\Gyr$, the trend starts to reverse, with the longer SF timescale models declining more rapidly, though at a much reduced rate ($\sim-0.1\,\dex/\Gyr$) than at the peak.
 
 \section{Discussion}\label{sec:disc}
-In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SOI before and after the $\alpha$-enhancement.
-It is visibly obvious that the TNG SOI is unimodal before the $\alpha$-enhancement and bimodal afterwards (ignoring the minor mode at high-\MgFe{}).
-Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the SOI?, and (2) what justifies the $\alpha$-enhancement?
+In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SoI before and after the $\alpha$-enhancement.
+It is visibly obvious that the TNG SoI is unimodal before the $\alpha$-enhancement and bimodal afterwards (ignoring the minor mode at high-\MgFe{}).
+Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the SoI?, and (2) what justifies the $\alpha$-enhancement?
 We then briefly extend our comparison to the Milky Way data.
@@
 \subsection{Cause of Bimodality}\label{ssec:bim_cause}
-An extensive analysis of our SOI is beyond the scope of this project, but here we argue that the evidence is consistent with the scenario presented in \citet{2024arXiv240707985B}.
+An extensive analysis of our SoI is beyond the scope of this project, but here we argue that the evidence is consistent with the scenario presented in \citet{2024arXiv240707985B}.
 They presented an idealized simulation resembling the merger between the Milky Way and GSE.
@@
 
-The gap in each \FeH{} bin of Figure~\ref{fig:alpha} is contemperaneous with a minimum in the global SFR.
+The age gap in each \FeH{} bin of Figure~\ref{fig:alpha} is contemperaneous with a minimum in the global SFR.
 We can see in the upper panel of Figure~\ref{fig:history} that this dashed line lies almost exactly at the point of a local minimum in the SFH.
 This minimum, which is $\sim10\,\Msunyr$, is 6--7$\times$ smaller than the maxima before and after it.\footnote{A reasonable argument can be made that $10\,\Msunyr$ is hardly quiescent.
-However, for our purposes, it only matters that the SFR at the minimum is small relative to the SFR close in time before and after.
-And besides, this SFH is computed using the formation times of all star particles at $z=0$, which is likely contaminated by later mergers.}
+However, for our purposes, it only matters that the SFR at the minimum is small relative to the SFR close in time before and after.}
 
@@
 
-It is also worth noting that in both the fiducial and $\alpha$-enhanced SOI, there is a sort of rebound effect in \MgFe{}.
+It is also worth noting that in both the fiducial and $\alpha$-enhanced SoI, there is a sort of rebound effect in \MgFe{}.
 The star particles which form directly after the dashed line have a slightly lower \MgFe{} than stars which form after.
 This was seen in Figure~9 of \citet{2024arXiv240707985B}.
-In that work, it was argued that this occurs because during the period of suppressed star formation the \alphaFe{} of star forming gas plummets since there is no contribution from Type~II SNe.
-Later, the \alphaFe{} will recover when the SFR also recovers, but there is a brief window when old, low-$\alpha$ stars can form.
+In that work, it was argued that this occurs because, during the period of suppressed SF, the \alphaFe{} of star forming gas plummets since there is no contribution from Type~II SNe.
+Later, the \alphaFe{} of the gas will recover when the SFR also recovers, but there is a brief window when old, low-$\alpha$ stars can form.
 
@@
 As described in Section~\ref{X}, we applied a post-processing to the \MgFe{} of star particles in the TNG simulation.
-Specifically, to star particles formed before $z=1.5$, we added to their \MgFe{} a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time.
+Specifically, for star particles formed before $z=1.5$, we added to their \MgFe{} a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time.
 This post-processed subhalo is presented alongside the fiducial subhalo in the right and middle columns, respectively, of Figures~\ref{fig:fig1} and \ref{fig:alpha}.
@@
 The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models.
-Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} is not straightforward nor, in our opinion, even possible.
-However, we do offer one reasonable explanation -- the SFE at the high densities more present at high-$z$ is too low.
+Isolating the cause of the ``incorrect''\footnote{Our case study of a single galaxy, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} \MgFe{} vs time evolution at high-$z$ is not straightforward nor, in our opinion, even possible.
+However, we do offer one reasonable explanation -- the SFE at high densities, more present at high-$z$, is too low.
 
 We demonstrate the impact of the SFE on the \alphaFe{} ratio using a simple one-zone chemical evolution model with the publicly available code \texttt{VICE}.
-The details of our setup is given in Section~\red{X}.
-We vary the star formation timescale, $\tau_{\star}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio asa function of time.
-We find that shorter star formation timescales do lead to a more rapid reduction in \MgFe{}.
-We assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
-Such a difference in the rate occurs between the $\tau_{\star}=0.5$ and $1\,\Gyr$ models at their respective maximum slope magnitudes.
+The details of our setup is given in Section~\ref{ssec:onezone_met}.
+We vary the SF timescale, $\tau_{\star}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio as a function of time.
+We find that shorter SF timescales do lead to a more rapid reduction in \MgFe{}.
+The rate of decrease in \MgFe{}, at its maximum, varies from $\sim-0.25\,\dex/\Gyr$ in the $\tau_{\star}=5\,\Gyr$ model to $\sim-0.5\,\dex/\Gyr$ in the $\tau_{\star}=0.5\,\Gyr$ model.
+For our post-processing, assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
+Such a difference is well within the range of \MgFe{} decrease seen in our different $\tau_{\star}$ models.
 
-In TNG, the SF timescale is set to a fixed value of $2.2\,\Gyr$.
-However, this value is the SF timescale used to set the SFR of an individual cell.
-What is relevant for comparison to these models is the SF timescale averaged over some well-mixed region.
+S.
 Hassan et al.
-(in preparation) demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude, well within our needed factor of $2$ in $\tau_{\star}$.
-
-Therefore, we think our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified.
+(in preparation) demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude.
+This is well within our needed factor of $2$ in $\tau_{\star}$.
+Therefore, our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified.
 An intuitive understanding of the impact the decline in \alphaFe{} vs time has is that, when \alphaFe{} declines rapidly, it is a better estimator of age.
-When it is a better estimator of age, events separated temporally better separate in the abundance plane.
+When it is a better estimator of age, events which are separated temporally become better separated in the abundance plane.
 
@@
 An examination of the true distribution in the SoI (upper right panel), we see that the two distributions are in fact very cleanly separated in age.
-Of course, we do not know the true underlying distribution in the Milky Way, but these panels show that the Milky Way is consistent with the general picture shown in our SoI.
+We do not know the true underlying distribution in the Milky Way, but these panels show that the general picture shown in our SoI is consistent with the Milky Way.
 
@@
 This is the same argument that was first presented in \citet{2024arXiv240707985B}.
-When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the Milky Way's distribution (Section~\ref{ssec:compare_obs}).
+When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the Milky Way's abundance-age distribution (Section~\ref{ssec:compare_obs}).
 
@@
 % \input{src/app.tex}
-
 \end{document}

### 2024-09-03 paper/ms.tex
Bit more detail on plots

@@
 Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle and right columns).
-The colored vertical lines show 1D conditional histograms at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations.
-The \MgFe{} values in the lower panels are given offsets in order to reduce overlap.
+The upper panels show the 2D distribution in the space of \MgFe{}-\FeH{}.
+We have applied the standard \texttt{scipy} implementation of a gaussian kernel density estimator to a Cartesian grid of points.
+For each panel, we normalize so that the integral of the distribution is unity.
+Colors are plotted in a log scale ranging from $0.08$ to $15\,\dex^{-2}$.
+Contour lines are plotted at $0.1$, $1.5$, and $10\,\dex^{-2}$.
+
+The colored vertical lines are indicated at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations.
+The lower panels show 1D histograms of \MgFe{} in bins centered on these values.
+The bins for the Milky Way/simulations are $0.2$/$0.05\,\dex$.
+The \MgFe{} values are given offsets in order to reduce overlap.
 The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities.
@@
 We use age instead of formation time in order to better facilitate comparisons to observations.
+These panels are true 2D histograms, with a logarithmic colormap normalized to the maximum of the plot.
+The values of \MgFe{} are offset to avoid overlap.
+
 There is a gap in the ages that occurs at an age of $10.75\,\Gyr$, which we mark with a vertical dashed line.

### 2024-09-07 paper/ms.tex

@@
 This results in a sample of 54,777 stars.
-We use Fe to track total metallicity and Mg alone as an $\alpha$-element \red{TODO: add any additional details}.
+We use Fe to track total metallicity and Mg alone as an $\alpha$-element.
 
@@
 For the simulations, we add $15\%$ age and $0.01\,\dex$ \MgFe{} Gaussian errors.
-These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:errors} for plots of the observational errors).
+These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:obs_err} for plots of the observational errors).
 The error in \MgFe{} is not signficant, but the age error, which is $1\,\Gyr$ at $10\,\Gyr$, smears out the distribution before and after the dashed line.
@@
 
-% \input{src/app.tex}
+\appendix
+
+\section{Observational Errors}\label{app:obs_err}
+In Figure~\ref{fig:alpha}, we assumed observational errors of $15\%$ in age and $0.01\,\dex$ in \MgFe{}.
+In Figure~\ref{fig:obs_err}, we plot the quoted observational errors of the APOKASC2 (left) and ASPCAP (right) datasets, showing both \FeH{} and \MgFe{} (blue and orange, respectively).
+We show our $15\%$ age error and $0.01\,\dex$ abundance error assumptions as black lines.
+For the age error, we used the maximum of the upper and lower estimates from \citet{2018ApJS..239...32P}.
+Our assumed errors are generally consistent with the errors.
+Our error in \MgFe{} is a bit smaller than in ASPCAP, but the age estimates are by far the more constraining of the two.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\columnwidth]{fig/obs_error.pdf}
+  \caption{The observational errors of the APOKASC2 (left) and ASPCAP dataset (right).
+We show, on the left, a line indicating a $15\%$ error in observed age and on the right a vertical line indicating a $0.01\,\dex$ error.}
+  \label{fig:obs_err}
+\end{figure*}
+
 \end{document}

### 2024-09-07 paper/ms.tex
Update abstract
and change 10.75 to 10.6

@@
 
-\title{Rising from the Ashes II: A Hidden Abundance Bimodality in Illustris TNG}
+\title{Rising from the Ashes II: Did the Birth of the Milky Way's Bar Give Birth to the Birth of the Abundance Bimodality}
 
@@
 The colors indicate stellar populations at fixed values of \FeH{}, which are the same as in Figure~\ref{fig:fig1}.
-A gap in the relation occurs at an age of approximately $10.75\,\Gyr$, which we indicate with a vertical dashed line.
+A gap in the relation occurs at an age of approximately $10.6\,\Gyr$, which we indicate with a vertical dashed line.
 The effect of the $\alpha$-enhancement is clear, as it separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$).
@@
 
-There is a gap in the ages that occurs at an age of $10.75\,\Gyr$, which we mark with a vertical dashed line.
+There is a gap in the ages that occurs at an age of $10.6\,\Gyr$, which we mark with a vertical dashed line.
 Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
@@
 This SFH is generated using the formation times of all star particles in the subhalo at $z=0$.
-In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha} ($\sim3\,\Gyr$), which delineates the separation between the high- and low-$\alpha$ sequences.
+In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha} ($\sim3.2\,\Gyr$), which delineates the separation between the high- and low-$\alpha$ sequences.
 The gap in ages is naturally associated with a gap in the SFH located at the dashed line.
@@
 In an effort towards understanding the events in our SoI's history that led to the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of some of its key quantities.
-In the upper panel of Figure~\ref{fig:history}, we show the SFH of our galaxy with the same dashed line as in Figure~\ref{fig:alpha} (at an age of $10.75\,\Gyr$ in that plot is at a time of $\sim3\,\Gyr$ here).
+In the upper panel of Figure~\ref{fig:history}, we show the SFH of our galaxy with the same dashed line as in Figure~\ref{fig:alpha} (at an age of $10.6\,\Gyr$ in that plot is at a time of $\sim3.2\,\Gyr$ here).
 This SFH is computed from the formation times of all star particles in the subhalo at $z=0$.
@@
 The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it switches to the low accretion radio mode.
-However, at the dashed line ($\sim3\,\Gyr$) there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
+However, at the dashed line ($\sim3.2\,\Gyr$) there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
 
@@
 The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} denotes the transition between the high- and low-$\alpha$ sequences.
-We place it at an age of $10.75\,\Gyr$ or a formation time of $\sim3\,\Gyr$.
+We place it at an age of $10.6\,\Gyr$ or a formation time of $\sim3.2\,\Gyr$.
 The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} to avoid overlap).
@@
 
-This bimodality can be traced to an event that occurred at an age of $10.75\,\Gyr$, or formation time of $\sim3\,\Gyr$ ($z\sim2$).
+This bimodality can be traced to an event that occurred at an age of $10.6\,\Gyr$, or formation time of $\sim3.2\,\Gyr$ ($z\sim2$).
 Shown as a vertical dashed line in Figure~\ref{fig:alpha}, star particles which form before this form at high-$\alpha$ while stars which form after form at lower $\alpha$.

### 2024-09-07 paper/ms.tex
Add zoomed evol hist plot

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200_zoomed.pdf}
+  \caption{\textbf{At the transition from the high- to low-$\alpha$ sequence, a bar forms and strengthens, AGN activity is enhanced, and star formation is supressed.} The evolutionary history of our SoI near the transition between the high- and low-$\alpha$ sequence, which is indicated as a vertical dashed line at an age of $10.6\,\Gyr$ ($t\sim3.2\,\Gyr$).
+The blue line indicates the SFR, which drops from a peak of $\sim54\,\Msunyr$ to $\sim3.6\,\Msunyr$.
+The minimum is very close to the transition.
+The drop in SFR is coincident with a rise in the AGN accretion rate (orange) as well as a rise in the strength of the bar (red).}
+  \label{fig:history_zoom}
+\end{figure}
+
+We show the evolution of the SoI in greater detail at the transition between the high- and low-$\alpha$ sequences in Figure~\ref{fig:history_zoom}.
+As in Figure~\ref{fig:history} we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$, in red.
+From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54\,\Msunyr$ to $3.6\,\Gyr$.
+The minimum in the SFR is nearly coincident with the transition line.
+
+We can see more clearly here that the BH accretion rate (red), in units of the Eddington accretion rate, increases from a value of $\sim0.08$ at $\sim2.8\,\Gyr$ to a maximum of $\sim0.3$ at $\sim3.1\,\Gyr$, right before the transition.
+This rise in the AGN accretion rate is preceded by a strengthening of the bar, which rises from an $A_2$ of $\sim0.1$ at $t\sim2.4\,\Gyr$ to an $A_2$ of $\sim0.5$ at $\sim3.1\,\Gyr$, the time of the peak BH accretion rate.
+
 \subsection{One-Zone Model}\label{ssec:onezone}

### 2024-09-08 paper/ms.tex
Add images to results

@@
 \newcommand{\kpc}{\ensuremath{\textrm{kpc}}}
+\newcommand{\ckpc}{\ensuremath{\textrm{ckpc}}}
 \newcommand{\pc}{\ensuremath{\textrm{pc}}}
@@
 
+\subsection{Images}\label{ssec:images}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/images_star.pdf}
+  \caption{Surface density projections of star particles in our SoI at the transition between the high- and low-$\alpha$ sequences.
+Each panel indicates subsequent snapshots ranging from snapshot 23 ($z\sim3.5$) to snapshot 36 ($z\sim1.7$), as well as snapshot 99 ($z=0$) in the lower right.
+Several key numbers are shown in the corners of each panel, clockwise from the top left: SFR, time, bar strength ($A_{2,\textrm{max}}$), and BH accretion rate.
+A guide is given in the top left subpanel.
+At the center-bottom of each panel, we indicate panels which occur before the transition ($\sim3.2\,\Gyr$) as high-$\alpha$ and panels which occur after as low-$\alpha$.}
+  \label{fig:images_star}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/images_gas.pdf}
+  \caption{As in Figure~\ref{fig:images_star}, but showing the surface density projections of gas in our SoI at the transition between the high- and low-$\alpha$ sequences.
+Each panel indicates subsequent snapshots ranging from snapshot 23 ($z\sim3.5$) to snapshot 36 ($z\sim1.7$), as well as snapshot 99 ($z=0$) in the lower right.
+Several key numbers are shown in the corners of each panel, clockwise from the top left: SFR, time, gas fraction, and BH accretion rate.
+A guide is given in the top left subpanel.
+At the center-bottom of each panel, we indicate panels which occur before the transition ($\sim3.2\,\Gyr$) as high-$\alpha$ and panels which occur after as low-$\alpha$.}
+  \label{fig:images_gas}
+\end{figure*}
+
+In order to better conceptualize the evolution of the SoI at the high- to low-$\alpha$ transition, we show surface density projections of the stellar (Figure~\ref{fig:images_star}) and gaseous (Figure~\ref{fig:images_gas}) phases of the progenitors of our SoI at various redshifts.
+In addition to the final, $z=0$, snapshot in the lower right, we show panels for snapshots 23 to 36 in which $z$ ranges from $\sim3.5$ to $\sim1.7$ and the cosmic time from $\sim1.81$ to $\sim3.74\,\Gyr$.
+Projections are made on a $256\times256$ grid of a $25\,\kpc$ by $25\,\kpc$ square.
+All star particles/gas cells within ten times the stellar half-mass radius are used, and a simple nearest neighbor assignment of mass to each cell is used.
+Colors range logarithmically from $5\times10^{-4}$ to $0.5$ in native units ($10^{10} h M_{\odot} \ckpc^{-2}$).
+
+We also show four relevant statistics in each panel of Figures~\ref{fig:images_star} and \ref{fig:images_gas}.
+For Figure~\ref{fig:images_star}, these are, clockwise from the upper left, the SFR, cosmic time, bar strength, and BH accretion rate.
+They are the same for Figure~\ref{fig:images_gas}, but bar strength is replaced with gas fraction (within twice the stellar half-mass radius).
+
+A description of the events portrayed in each Figure is given in Section~\ref{ssec:cause_qui}.
+
 \subsection{One-Zone Model}\label{ssec:onezone}

### 2024-09-09 paper/ms.tex
Add discussion of images

@@
 \newcommand{\Msunyr}{\ensuremath{\Msun/\textrm{yr}}}
+\newcommand{\Atmax}{\ensuremath{A_{2,\textrm{max}}}}
 
@@
 As in Figure~\ref{fig:history} we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$, in red.
-From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54\,\Msunyr$ to $3.6\,\Gyr$.
+From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54$ to $3.6\,\Msunyr$.
 The minimum in the SFR is nearly coincident with the transition line.
@@
 They are the same for Figure~\ref{fig:images_gas}, but bar strength is replaced with gas fraction (within twice the stellar half-mass radius).
+The bar strength is missing from several snapshots.
+This is because the catalog we pull \Atmax{} from excludes certain galaxies from being considered barred if they do not pass certain quality cuts \citep{2022MNRAS.515.1524Z}.
+These can come from, e.g., flybys or violent buckling events.
 
@@
 \subsection{Cause of Quiescence}\label{ssec:cause_qui}
+% We show the evolution of the SoI in greater detail at the transition between the high- and low-$\alpha$ sequences in Figure~\ref{fig:history_zoom}.
+As in Figure~\ref{fig:history} we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$, in red.
+From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54\,\Msunyr$ to $3.6\,\Msunyr$.
+The minimum in the SFR is nearly coincident with the transition line.
+
+% We can see more clearly here that the BH accretion rate (red), in units of the Eddington accretion rate, increases from a value of $\sim0.08$ at $\sim2.8\,\Gyr$ to a maximum of $\sim0.3$ at $\sim3.1\,\Gyr$, right before the transition.
+This rise in the AGN accretion rate is preceded by a strengthening of the bar, which rises from an $A_2$ of $\sim0.1$ at $t\sim2.4\,\Gyr$ to an $A_2$ of $\sim0.5$ at $\sim3.1\,\Gyr$, the time of the peak BH accretion rate.
+
 It is natural to question why the minimum in the SFR occurs.
@@
 Here, we can see that there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
-Establishing a causal relationship between the two is beyond the scope of the present work, though it is the same suspected cause as in \citet{2024arXiv240707985B}.
+Based on this burst, it is reasonable to suspect that AGN activity is also responsible for the quiescent period in our SoI.
+However, we argue that the cause of the localized spike in the BH accretion rate is not due to a merger but instead due to the formation/strengthening of a bar.
+
+In Figure~\ref{fig:history_zoom}, we take a closer view of the evolution of our SoI at the transition between the high- and low-$\alpha$ sequence, which we denote with the same line at an age of $10.6\,\Gyr$ ($t\sim3.2\,\Gyr$) as before.
+Here, we see that indeed the drop in the SFR ( $\sim3.6\,\Msunyr$ at $t\sim3.3\,\Gyr$) reaches a minimum one snapshot after the maximum in the BH accretion rate ($\sim0.3\times\dot{M_{\textrm{edd}}}$ at $t\sim3.1\,\Gyr$).
+
+The gaseous surface density images in Figure~\ref{fig:images_gas} are helpful to understand this moment in the SoI's history.
+The third row, from $t=2.84$ to $3.28\,\Gyr$ shows this moment, with the rightmost $t=3.28\,\Gyr$ marking the transition from high- to low-$\alpha$ formation.
+The gas fraction (bottom right number) quickly drops from $25\%$ to $3\%$, accompanied by not only a high SFR ($54.3\,\Msunyr$ at maximum) but also an increasing BH accretion rate.
+
+This increasing BH accretion rate is also preceded by the formation of a stellar bar at the center of the galaxy as seen in Figure~\ref{fig:images_star}.\footnote{The bar is already at a strength of $\Atmax\sim0.1$ before, so it either forms or strengthens depending on one's interpretation.
+We choose the former.} Starting from $t=2.38\,\Gyr$, the bar strength grows from $\Atmax=0.1$ to $0.5$ at $t=3.13\,\Gyr$, the peak of the BH accretion rate.
+Note that the bar strength considers only the region where the phase of the second Fourier mode is constant, and so spiral structure as seen in, e.g., the $t=2.38\,\Gyr$ snapshot is not eligible for \Atmax{}.
 

### 2024-09-10 paper/ms.tex
Vedant edits

@@
     The Milky Way is known to host at least two modes in the present day distribution of Fe and $\alpha$-elements.
-The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive sattelite (Gaia-Sausage-Enceladus) at $z\sim2$.
+The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive satellite (Gaia-Sausage-Enceladus) at $z\sim2$.
 However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality.
@@
 The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
-The quiescent period in this galaxy is not associated with a merger but some unspecified internal process which leads to AGN activity.
-We argue that the post-processing step can be understood as the TNG model underproducing star formation in the densest regions at high-$z$.
+The quiescent period in this galaxy is not associated with a merger but by the formation of a bar which is followed by AGN activity.
+This galaxy indicates a novel scenario in which the $\alpha$-bimodality is caused by AGN-induced quenching induced by the formation of the Milky Way's bar.
+We argue that the post-processing step can be interpreted as the TNG model underproducing star formation in the densest regions at high-$z$.
   \end{abstract}
@@
 
-A more extensive survey of the different proposed formation mechanisms of this bimodality is given in \citet{2024arXiv240707985B}.
-Here, we mention simply that there are two approaches.
-First, the bimodality is a result of internal secular processes that generate the bimodality through radial migration \citep{2009MNRAS.396..203S,2021MNRAS.507.5882S,2023MNRAS.523.3791C} or clump formation \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
+There are essentially two approaches to explaining the bimodality.
+First, it is a result of internal secular processes that generate the bimodality through radial migration \citep{2009MNRAS.396..203S,2021MNRAS.507.5882S,2023MNRAS.523.3791C} or clump formation \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
 
@@
 Third and finally, the bimodality is generated through a merger process, either by enhancing the SFR of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
-The fact that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N}.
+The fact that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
 
@@
 Second, because the SFR is lower, $\alpha$-element production drops and so the \alphaFe{} of the gas drops as well.
+This is conceptually similar to some variants of the two-phase infall scenarios which allow for a brief halt in the star formation rate \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period is much shorter in \citet{2024arXiv240707985B}.
 The combination of these two effects is what leads to the valley in between the high- and low-$\alpha$ sequences.
@@
 
+One piece of the TNG model of note for this work is the BH accretion and feedback method \citep{2017MNRAS.465.3291W}.
+The black hole accretion rate ($\dot{M_{\textrm{BH}}}$) is computed using the local structure of the gas phase with the Bondi-Hoyle-Lyttleton formula \citep{1939PCPS...35..405H,1944MNRAS.104..273B,1952MNRAS.112..195B}, with a maximum of the Eddington accretion rate ($\dot{M_{\textrm{edd}}}$).
+The model allows the BH to be either in a kinetic radio-mode or a thermal quasar-mode.
+If the Eddington ratio ($\dot{M_{\textrm{BH}}}/\dot{M_{\textrm{edd}}}$) exceeds a threshold ($M_{\textrm{BH}}$-dependent, but $\sim0.001--0.1$), the BH is in the quasar mode and injects a large amount of thermal energy into its surroundings.
+
 Using the public catalog, we selected a sample of subhalos at $z=1.5$ (snapshot 40) according to the following criteria: (1) the subhalo is central (i.e., the most massive subhalo within its halo), and (2) the subhalo's stellar mass is between $10^{10}$ and $10^{10.5}\,\Msun/\textrm{h}$.
@@
 We did not want contamination by mergers at lower redshift which we know contribute very little to the Milky Way's disk stars \citep[e.g.,][]{2016ARA&A..54..529B}.
+We study the main descendant of our SoI at $z=0$
 
@@
 This uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
-We cross-match this catalog to our larger sample from ASPCAP which results in a sample of 1868 stars.
+Using only stars with $25\%$ age uncertainties (taken as the maximum of the upper and lower uncertainty), we cross-match this catalog to our larger sample from ASPCAP which results in a sample of 1201 stars.
 
@@
 The bins for the Milky Way/simulations are $0.2$/$0.05\,\dex$.
-The \MgFe{} values are given offsets in order to reduce overlap.
+The \MgFe{} values are given offsets so their medians are at zero.
 The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities.
@@
 These panels are true 2D histograms, with a logarithmic colormap normalized to the maximum of the plot.
-The values of \MgFe{} are offset to avoid overlap.
+The values of \MgFe{} are offset so their medians are at zero.
 
@@
 However, at the dashed line ($\sim3.2\,\Gyr$) there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
+This places the BH firmly in the thermal quasar-mode, and allows it to inject large amounts of thermal energy into the center of the galaxy.
 
@@
 We place it at an age of $10.6\,\Gyr$ or a formation time of $\sim3.2\,\Gyr$.
-The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} to avoid overlap).
+The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} so their medians are at zero).
 Stars which formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
@@
 
+The scenario implied by all the available evidence is that: 
+\begin{enumerate}
+  \item a bar forms through an internal instability, which
+  \item drives a large amount of gas to the center of the galaxy, which
+  \item triggers a high BH accretion rate and quasar-mode thermal feedback, which
+  \item clears gas out of the galaxy.
+\end{enumerate}
+This picture is supported by work showing that in simulations bars should be able to fuel AGN \citep{1990Natur.345..679S,2010MNRAS.407.1529H}, and that barred galaxies preferentially host AGN \citep{2022A&A...661A.105S}.
+At high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+
+A complicating factor for this picture comes from the high-SFR associated with the galaxy.
+The depletion time ($M_{\textrm{gas}}/\textrm{SFR}$) at the $t=2.84\,\Gyr$ snapshot is $204\,\Myr$, shorter than the time it takes for the SFR to reach its minimum.
+However, this perspective has to be balanced by the fact that the depletion time is already short at this redshift.
+The average depletion time in the preceding 5 snapshots is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its CGM.
+A definitive account, difficult with the current simulation because of its sparse snapshot spacing, requires further work.
+
 % \subsection{Full Sample}\label{ssec:fullsamp}
@@
 
+While a strong claim about the cause of the quiescent period is difficult to make, we showed that the formation/strengthening of a bar could be responsible for triggering an episode of AGN activity.
 This work adds further support that the argument made in \citet{2024arXiv240707985B} is a plausible explanation for the Milky Way's abundance bimodality.

### 2024-09-10 paper/ms.tex
Update based on image rhalf change

@@
 All star particles/gas cells within ten times the stellar half-mass radius are used, and a simple nearest neighbor assignment of mass to each cell is used.
-Colors range logarithmically from $5\times10^{-4}$ to $0.5$ in native units ($10^{10} h M_{\odot} \ckpc^{-2}$).
+Colors range logarithmically from $5\times10^{-4}$ to $0.5$ in native units ($10^{10} h M_{\odot} \ckpc^{-2}$), and only resolution elements within 10 times the stellar half-mass radius of the center of the subhalo are used.
 

### 2024-09-10 paper/ms.tex

@@
 \begin{abstract}
-    The Milky Way is known to host at least two modes in the present day distribution of Fe and $\alpha$-elements.
+    The Milky Way is known to host at least two modes in its present day distribution of Fe and $\alpha$-elements.
 The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive satellite (Gaia-Sausage-Enceladus) at $z\sim2$.
@@
 The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
-The quiescent period in this galaxy is not associated with a merger but by the formation of a bar which is followed by AGN activity.
-This galaxy indicates a novel scenario in which the $\alpha$-bimodality is caused by AGN-induced quenching induced by the formation of the Milky Way's bar.
+The quiescent period in this galaxy is not associated with a merger but by the formation of a bar followed by AGN activity.
+This galaxy indicates a novel scenario in which the $\alpha$-bimodality is caused by AGN-induced quenching triggered by the formation of the Milky Way's bar.
 We argue that the post-processing step can be interpreted as the TNG model underproducing star formation in the densest regions at high-$z$.
@@
 The SoI undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
+However, instead of being preceded by a merger, the quenching is preceded by apparent bar-induced AGN activity.
 Therefore, this work serves as a verification that the scenario in \citet{2024arXiv240707985B} is possible in cosmological simulations and can occur in non-merger scenarios.
 
-In Section~\ref{sec:methods} we discuss our selection technique which led to discovering the SoI, as well as a simple one zone chemical evolution model we use to justify our post-processing step.
+In Section~\ref{sec:methods} we discuss our selection technique which led to discovering the SoI, the observations we use for comparison, as well as a simple one zone chemical evolution model we use to justify our post-processing step.
 In Section~\ref{sec:results} we present the main results which we discuss and interpret in Section~\ref{sec:disc}.
@@
 We did not want contamination by mergers at lower redshift which we know contribute very little to the Milky Way's disk stars \citep[e.g.,][]{2016ARA&A..54..529B}.
-We study the main descendant of our SoI at $z=0$
 
@@
 We refer to this subhalo as our subhalo of interest (SoI).
+
+\subsection{Bar Catalog}\label{ssec:barcat}
+In order to study the evolution of the morphology of our SoI, we make use of the \citet{2022MNRAS.515.1524Z} catalog.
+They provide a decomposition of all galaxies with at least $10^4$ star particles, as well as an estimate of the bar strength.
+This taken to be the maximum of the second Fourier mode ($A_{2,\textrm{max}}$) within the bar region (not including spiral arms).
 
@@
 The lower panels show 1D histograms of \MgFe{} in bins centered on these values.
-The bins for the Milky Way/simulations are $0.2$/$0.05\,\dex$.
+The bins for the Milky Way/simulations have width $0.2$/$0.05\,\dex$.
 The \MgFe{} values are given offsets so their medians are at zero.
@@
 These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:obs_err} for plots of the observational errors).
-The error in \MgFe{} is not signficant, but the age error, which is $1\,\Gyr$ at $10\,\Gyr$, smears out the distribution before and after the dashed line.
+The error in \MgFe{} is not signficant, but the age error, which is $1.5\,\Gyr$ at $10\,\Gyr$, smears out the distribution before and after the dashed line.
 The $\alpha$-enhanced SoI still shows two separate populations in this plot, but they now significantly overlap in age.
@@
   \caption{\textbf{The evolutionary history of our subhalo of interest.} The upper panel shows the SFH of our subhalo.
-This SFH is generated using the formation times of all star particles in the subhalo at $z=0$.
+This SFH is computed using the SFR within twice the stellar half-mass radius in our SoI's main progenitors.
 In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha} ($\sim3.2\,\Gyr$), which delineates the separation between the high- and low-$\alpha$ sequences.
@@
 In the upper panel of Figure~\ref{fig:history}, we show the SFH of our galaxy with the same dashed line as in Figure~\ref{fig:alpha} (at an age of $10.6\,\Gyr$ in that plot is at a time of $\sim3.2\,\Gyr$ here).
-This SFH is computed from the formation times of all star particles in the subhalo at $z=0$.
-This allows us to compute the SFH at fine time resolution.
-We see two peaks in the SFH at $t\sim2.5$ and $\sim4.5\,\Gyr$ of an amplitude of about $70$ and $60\,\Msunyr$.
-The dashed line corresponds to a relative drop in the SFR, down to about $10\,\Msunyr$ before quickly recovering.
+This SFH is computed using the SFR within twice the stellar half-mass radius in our SoI's main progenitors.
+We see two peaks in the SFH at $t\sim2.5$ and $\sim4.5\,\Gyr$ of an amplitude of about $50$ and $30\,\Msunyr$.
+The dashed line corresponds to a relative drop in the SFR, down to about $3\,\Msunyr$ before quickly recovering.
 
@@
 Early in its history ($t<2\,\Gyr$), the subhalo experiences high accretion rates.
-The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it switches to the low accretion radio mode.
+The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it fails to show on this linear plot.
 However, at the dashed line ($\sim3.2\,\Gyr$) there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
@@
 We show the evolution of the SoI in greater detail at the transition between the high- and low-$\alpha$ sequences in Figure~\ref{fig:history_zoom}.
-As in Figure~\ref{fig:history} we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$, in red.
+As in Figure~\ref{fig:history}, we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$ in the bar region, in red.
 From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54$ to $3.6\,\Msunyr$.
@@
 They are the same for Figure~\ref{fig:images_gas}, but bar strength is replaced with gas fraction (within twice the stellar half-mass radius).
-The bar strength is missing from several snapshots.
-This is because the catalog we pull \Atmax{} from excludes certain galaxies from being considered barred if they do not pass certain quality cuts \citep{2022MNRAS.515.1524Z}.
+The bar strength is missing from several snapshots because the \citet{2022MNRAS.515.1524Z} catalog excludes certain galaxies from being considered barred if they do not pass certain quality cuts.
 These can come from, e.g., flybys or violent buckling events.
@@
 We can see in the upper panel of Figure~\ref{fig:history} that this dashed line lies almost exactly at the point of a local minimum in the SFH.
-This minimum, which is $\sim10\,\Msunyr$, is 6--7$\times$ smaller than the maxima before and after it.\footnote{A reasonable argument can be made that $10\,\Msunyr$ is hardly quiescent.
-However, for our purposes, it only matters that the SFR at the minimum is small relative to the SFR close in time before and after.}
+This minimum, which is $\sim3\,\Msunyr$, is 10--15$\times$ smaller than the maxima before and after it.
 
@@
 \subsection{Steepening of $\alpha$ Decline}\label{ssec:sfe}
-As described in Section~\ref{X}, we applied a post-processing to the \MgFe{} of star particles in the TNG simulation.
+As described in Section~\ref{ssec:tng}, we applied a post-processing to the \MgFe{} of star particles in the TNG simulation.
 Specifically, for star particles formed before $z=1.5$, we added to their \MgFe{} a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time.
@@
 
-A complicating factor for this picture comes from the high-SFR associated with the galaxy.
+A complicating factor for this picture comes from the high SFR associated with the galaxy.
 The depletion time ($M_{\textrm{gas}}/\textrm{SFR}$) at the $t=2.84\,\Gyr$ snapshot is $204\,\Myr$, shorter than the time it takes for the SFR to reach its minimum.
-However, this perspective has to be balanced by the fact that the depletion time is already short at this redshift.
+However, this has to be balanced by the fact that the depletion time is already short at this redshift.
 The average depletion time in the preceding 5 snapshots is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its CGM.

### 2024-09-10 paper/ms.tex
Add app fig

@@
 With this post-processing, we found that much more structure was generally present.
-We selected subhalo 172175 (at snapshot 40) for its particular resemblance to the Milky Way.
+
+We show the abundance distributions (replicating Figure~\ref{fig:fig1}) of 16 random subhalos from our catalog, and the subhalo we selected, in Appendix~\ref{app:rand_fig1}.
+Of these subhalos, some structure is present, but none have a strong bimodality as seen in the Milky Way.
+After the $\alpha$-enhancement, a few have strongly bimodal features (subject to interpretation): 172175, 178140, 193025.
+
+We selected subhalo 172175 (the ID at snapshot 40) for its particular resemblance to the Milky Way.
 We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
@@
 
+\section{Random Selection of Subhalos}\label{app:rand_fig1}
+In Figures~\ref{fig:app0} to \ref{fig:app16}, we show a version of Figure~\ref{fig:fig1} but for a random selection of subhalos from our broader sample of 168 Milky Way-progenitors at $z=1.5$ in TNG50.
+It is from this sample that we selected our SoI.
+We first show our SoI at $z=1.5$ in Figure~\ref{fig:app0}, and then show our random sample of 16.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_172175.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for our SoI at $z=1.5$.}
+  \label{fig:app0}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_163071.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app1}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_178140.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app2}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_179009.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app3}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_193025.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app4}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_196834.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app5}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_202467.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app6}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_208267.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app7}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_222555.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app8}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_235345.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app9}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_245661.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app10}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_254663.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app11}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_260347.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app12}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_265671.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app13}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_282632.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app14}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_287601.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app15}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/app_292983.pdf}
+  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
+  \label{fig:app16}
+\end{figure*}
+
 \end{document}

### 2024-09-11 paper/ms.tex
Update title/authors
one-zone model section text

@@
 \newcommand{\red}[1]{\textcolor{red}{#1}}
+% \linespread{1.8}
 
@@
 \subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
-James inserts his section
+One-zone galactic chemical evolution (GCE) models describe enrichment in an idealized gas reservoir in which newly synthesized metals mix instantaneously (see e.g.
+the reviews by \citealt{Tinsley1980} and \citealt{Matteucci2021}).
+Our parameter choices in this paper are based on the models in \citet{2022arXiv220402989C}.
+While they were interested in bursts of star formation at the transition between the stellar halo and thick disk formation epochs, we focus on smooth evolutionary histories in this paper.
+We integrate these models numerically using the publicly available {\tt Versatile Integrator for Chemical Evolution} ({\tt VICE}; \citealt{Johnson2020}).
+\par
+The quantity that is of particular importance to our results is the star formation efficiency (SFE) timescale $\tau_\star$:
+\begin{equation}
+\tau_\star \equiv \frac{M_g}{\dot{M}_\star},
+\end{equation}
+where $M_g$ and $\dot{M}_\star$ are the ISM mass and star formation rate, respectively.
+This timescale can be equivalently expressed as the ratio of the corresponding surface densities $\Sigma_g$ and $\dot{\Sigma}_\star$.
+$\tau_\star$ is the inverse of the SFE itself, describing the rate of star formation per unit mass in the ISM.
+In principle, $\tau_\star$ should vary with $M_g$ because the observed relation between $\dot{\Sigma}_\star$ and $\Sigma_g$ is non-linear; classically, $\dot{\Sigma}_\star \propto \Sigma_g^N$ where $N \approx 1.5$ (e.g.
+\citealt{Schmidt1959, Kennicutt1998}).
+For simplicity, we hold $\tau_\star$ constant in this paper, which corresponds to a linear relation.
+In section 3.5 below, we present models using $\tau_\star = 0.5$, $1$, and $5$ Gyr.
+\par
+Following \citet{2022arXiv220402989C}, our models assume that there is initially no gas present in the galaxy (i.e. $M_g = 0$ at $t = 0$).
+Zero metallicity gas accretes at a constant rate of $\dot{M}_\text{in} = 5$ M$_\odot$/yr.
+The efficiency with which feedback sweeps up ISM material and ejects it to the CGM in an outflow is described by the mass loading factor $\eta \equiv \dot{M}_\text{out} / \dot{M}_\star$.
+We use $\eta = 2$ throughout this paper (i.e. for every solar mass of stars formed, 2 M$_\odot$ of ISM gas is lost to an outflow).
+These parameter choices lead to an SFH that initially rises from zero and approaches a constant value of $\sim$1.9 M$_\odot$/yr.
+With these choices, the predicted abundance evolution is insensitive to the overall normalization of the accretion and star formation histories, since a larger accretion rate forms more stars and metals but simultaneously introduces more H into the ISM.
+\par
+We use the solar abundances of Fe and Mg from \citet{Magg2022} with an additional 0.04 dex to account for the effects of diffusion and gravitational settling (\citealt{Turcotte1998}; i.e.
+$\{Z_{\text{Fe},\odot}, Z_{\text{Mg},\odot}\} = \{13.7, 6.71\} \times 10^{-4}$).
+We adopt SN yields of Fe and Mg based on \citeauthor{Weinberg2023}'s \citeyearpar{Weinberg2023} recommendations for Type II SNe:
+\begin{itemize}
+
+	\item $y_\text{Fe}^\text{II} = 4.73 \times 10^{-4}$
+
+	\item $y_\text{Mg}^\text{II} = 6.52 \times 10^{-4}$
+
+	\item $y_\text{Fe}^\text{Ia} = 12 \times 10^{-4}$
+
+	\item $y_\text{Mg}^\text{Ia} = 0$,
+
+\end{itemize}
+where the subscripts and superscripts denote the element and SN type, respectively.
+We select this value of $y_\text{Fe}^\text{Ia}$ as it corresponds to $\sim$30\% ($\sim$70\%) of Fe arising from Type II (Ia) SNe at solar [Fe/H].
+These yields are population-averaged, meaning that they quantify the amount of metal production per unit mass of star formation under the given enrichment channel (e.g.
+a hypothetical $1000$ M$_\odot$ stellar population would produce a total of $0.652$ M$_\odot$ of Mg through Type II SNe).
+{\tt VICE} models Type II SNe as exploding instantaneously following an episode of star formation.
+For Type Ia SNe, we assume that metals are produced according to the empirically motivated $t^{-1.1}$ power-law based volumetric SN rates as a function of redshift and the cosmic SFH \citep[e.g.][]{Maoz2012}.
+\par
+We use the yields recommended by \citet{Weinberg2023} because they are based on an empirical determination of the mean $^{56}$Ni yield from Type II SNe by \citet{Rodriguez2021, Rodriguez2023} applied to multi-element abundance distributions in the Milky Way.
+Theoretically predicted SN yields \citep[e.g.][]{Seitenzahl2013, Sukhbold2016, Limongi2018, Gronow2021} are subject to substantial theoretical uncertainties.
+Empirical considerations regarding yields are often necessary for GCE models to make tenable predictions (see also discussion in \citealt{Palla2022}).
+\par
+With the exception of our SN yields, we find through experimentation that the decline in [Mg/Fe] with time is most significantly sensitive to the value of $\tau_\star$.
+We therefore expect its connection to the decline in [Mg/Fe] on which this paper is focused to be robust.
+We refer to \citet{Johnson2020} and \citet{2022arXiv220402989C} for further discussion of these GCE models.
 

### 2024-09-26 paper/ms.tex
Add new figure

--- 2024-09-10 paper/ms.tex
@@
-\documentclass[linenumbers, twocolumn]{aastex631}
+\documentclass[twocolumn]{aastex631}
 
@@
 
-\title{Rising from the Ashes II: Did the Birth of the Milky Way's Bar Give Birth to the Birth of the Abundance Bimodality}
+\title{Rising from the Ashes II: Can Bar Formation Lead to Abundance Bimodalities?}
 
@@
 
-\author{et al}
+\author{Vadim Semenov}
+\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
+
+\author{Lars Hernquist}
+\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
+
+\author{Vedant Chandra}
+\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
+
+\author{Charlie Conroy}
+\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200_zoomed.pdf}
-  \caption{\textbf{At the transition from the high- to low-$\alpha$ sequence, a bar forms and strengthens, AGN activity is enhanced, and star formation is supressed.} The evolutionary history of our SoI near the transition between the high- and low-$\alpha$ sequence, which is indicated as a vertical dashed line at an age of $10.6\,\Gyr$ ($t\sim3.2\,\Gyr$).
-The blue line indicates the SFR, which drops from a peak of $\sim54\,\Msunyr$ to $\sim3.6\,\Msunyr$.
-The minimum is very close to the transition.
-The drop in SFR is coincident with a rise in the AGN accretion rate (orange) as well as a rise in the strength of the bar (red).}
-  \label{fig:history_zoom}
-\end{figure}
-
-We show the evolution of the SoI in greater detail at the transition between the high- and low-$\alpha$ sequences in Figure~\ref{fig:history_zoom}.
-As in Figure~\ref{fig:history}, we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$ in the bar region, in red.
-From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54$ to $3.6\,\Msunyr$.
-The minimum in the SFR is nearly coincident with the transition line.
-
-We can see more clearly here that the BH accretion rate (red), in units of the Eddington accretion rate, increases from a value of $\sim0.08$ at $\sim2.8\,\Gyr$ to a maximum of $\sim0.3$ at $\sim3.1\,\Gyr$, right before the transition.
-This rise in the AGN accretion rate is preceded by a strengthening of the bar, which rises from an $A_2$ of $\sim0.1$ at $t\sim2.4\,\Gyr$ to an $A_2$ of $\sim0.5$ at $\sim3.1\,\Gyr$, the time of the peak BH accretion rate.
-
-\subsection{Images}\label{ssec:images}
+\subsection{Sequence of Events}\label{ssec:sequence_of_events}
 \begin{figure*}
   \centering
-  \includegraphics[width=\textwidth]{fig/images_star.pdf}
-  \caption{Surface density projections of star particles in our SoI at the transition between the high- and low-$\alpha$ sequences.
-Each panel indicates subsequent snapshots ranging from snapshot 23 ($z\sim3.5$) to snapshot 36 ($z\sim1.7$), as well as snapshot 99 ($z=0$) in the lower right.
-Several key numbers are shown in the corners of each panel, clockwise from the top left: SFR, time, bar strength ($A_{2,\textrm{max}}$), and BH accretion rate.
-A guide is given in the top left subpanel.
-At the center-bottom of each panel, we indicate panels which occur before the transition ($\sim3.2\,\Gyr$) as high-$\alpha$ and panels which occur after as low-$\alpha$.}
-  \label{fig:images_star}
+  \includegraphics[width=\textwidth]{fig/alyssa.pdf}
+  \caption{Surface density projections of gas (top row) and star particles (middle row) in our SoI across snapshots at different times during the high- to low-$\alpha$ transition.
+Below the projections is a plot showing the SFR, BH accretion rate (in units of $\dot{M_{\textrm{BH}}}/\dot{M_{\textrm{Edd}}}$), and bar strength ($A_2/A_0$ for $R<2$ kpc).
+Time ranges from $\sim2.4\,\textrm{Gyr}$ to $\sim3.6\,\textrm{Gyr}$, corresponding to redshifts from $z\sim2.7$ to $z\sim1.8$.
+A sequence of events in which the bar strengthens, BH accretion increases, and SFR declines is seen, and is described more fully in the text.}
+  \label{fig:seq}
 \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{fig/images_gas.pdf}
-  \caption{As in Figure~\ref{fig:images_star}, but showing the surface density projections of gas in our SoI at the transition between the high- and low-$\alpha$ sequences.
-Each panel indicates subsequent snapshots ranging from snapshot 23 ($z\sim3.5$) to snapshot 36 ($z\sim1.7$), as well as snapshot 99 ($z=0$) in the lower right.
-Several key numbers are shown in the corners of each panel, clockwise from the top left: SFR, time, gas fraction, and BH accretion rate.
-A guide is given in the top left subpanel.
-At the center-bottom of each panel, we indicate panels which occur before the transition ($\sim3.2\,\Gyr$) as high-$\alpha$ and panels which occur after as low-$\alpha$.}
-  \label{fig:images_gas}
-\end{figure*}
+Figure~\ref{fig:seq} presents surface density projections of gas and stars at different stages of the high- to low-$\alpha$ transition.
+The upper panels show gas density, while the middle panels display stellar density.
+Time progresses from $\sim2.4$ to $\sim3.6\,\textrm{Gyr}$, corresponding to redshifts ranging from $z\sim2.7$ to $z\sim1.8$.
 
-In order to better conceptualize the evolution of the SoI at the high- to low-$\alpha$ transition, we show surface density projections of the stellar (Figure~\ref{fig:images_star}) and gaseous (Figure~\ref{fig:images_gas}) phases of the progenitors of our SoI at various redshifts.
-In addition to the final, $z=0$, snapshot in the lower right, we show panels for snapshots 23 to 36 in which $z$ ranges from $\sim3.5$ to $\sim1.7$ and the cosmic time from $\sim1.81$ to $\sim3.74\,\Gyr$.
-Projections are made on a $256\times256$ grid of a $25\,\kpc$ by $25\,\kpc$ square.
-All star particles/gas cells within ten times the stellar half-mass radius are used, and a simple nearest neighbor assignment of mass to each cell is used.
-Colors range logarithmically from $5\times10^{-4}$ to $0.5$ in native units ($10^{10} h M_{\odot} \ckpc^{-2}$), and only resolution elements within 10 times the stellar half-mass radius of the center of the subhalo are used.
-
-We also show four relevant statistics in each panel of Figures~\ref{fig:images_star} and \ref{fig:images_gas}.
-For Figure~\ref{fig:images_star}, these are, clockwise from the upper left, the SFR, cosmic time, bar strength, and BH accretion rate.
-They are the same for Figure~\ref{fig:images_gas}, but bar strength is replaced with gas fraction (within twice the stellar half-mass radius).
-The bar strength is missing from several snapshots because the \citet{2022MNRAS.515.1524Z} catalog excludes certain galaxies from being considered barred if they do not pass certain quality cuts.
-These can come from, e.g., flybys or violent buckling events.
-
-A description of the events portrayed in each Figure is given in Section~\ref{ssec:cause_qui}.
+This Figure shows the following sequence of events:
+\begin{enumerate}
+    \item Bar forms: A steady increase in the bar strength, as indicated by $A_2/A_0$ for star particles with $R<2\,\kpc$, from $\sim0.05$ to $0.4$ starting around $2.8\,\textrm{Gyr}$.
+This rise is accompanied by the appearance of elongated features in the gas and stars consistent with a bar.
+    \item BH accretion increases: Following the increase in bar strength by about a snapshot ($\sim150\,\Myr$ here), the black hole accretion rate ($\dot{M_{\textrm{BH}}}/\dot{M_{\textrm{Edd}}}$) shows a significant spike, rising from a minimum of $\sim0.08$ at $t=2.84\,\Gyr$ to a maximum of $\sim0.29$ at $t=3.13\,\Gyr$.
+    \item SFR declines: After the increase in black hole accretion, the star formation rate (SFR) begins to decline.
+The decrease in SFR is gradual and continues as the black hole accretion rate remains elevated.
+By approximately $3.2\,\textrm{Gyr}$, the SFR reaches a more quiescent state, where it remains relatively low.
+\end{enumerate}
 

### 2024-10-01 paper/ms.tex
Edits based on James comments

@@
 \author{James W. Johnson}
-\affiliation{The Observatories of the Carnegie Institution for Science, Pasadena, CA, USA}
+\affiliation{Carnegie Science Observatories, Pasadena, CA, USA}
 
@@
 We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a sequence of starburst, brief quiescence, and then rejuvenation.
-After a minor post-processing step which boosts the \alphaFe{} of old star particles, we demonstrate that this galaxy hosts a strongly bimodal distribution in the \alphaFe{}-\FeH{} plane.
+Following a minor post-processing adjustment -— motivated by recent findings on the star formation efficiency in TNG -- which increases the \alphaFe{} values of older star particles, we demonstrate that this galaxy exhibits a pronounced bimodal distribution in the \alphaFe{}-\FeH{} plane.
 The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
@@
 The stellar surface abundances of most elements retain the composition of their natal gas cloud.
-Therefore, the present-day distribution of stellar surface abundances encodes the chemical history of a galaxy's gas phase.
-Two elements have received particular interest in the Milky Way: Fe and $\alpha$-elements (elements produced through the $\alpha$-process, such as O and Mg).
-Fe is produced in both Type Ia and Type II SNe whereas $\alpha$-elements are produced predominantly through Type II SNe.
-Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr to Gyrs for Type Ia), the ratio between $\alpha$-elements and Fe is expected to generally decrease with time.
+Therefore, the present-day distribution of their abundances encodes the chemical history of a galaxy's gas phase.
+Two classes elements have received particular attention in the Milky Way due to their disparate formation channels: iron-peak (such as Fe) and $\alpha$-elements (produced through the $\alpha$-process, such as O and Mg).
+Iron-peak elements are produced in both Type Ia and Type II supernovae (SNe) whereas $\alpha$-elements are produced predominantly through Type II SNe.
+In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences shown in Figure~\ref{fig:fig1} \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
 
-Because of their separate formation channels, the two dimensional plane of \alphaFe{}-\FeH{} has received considerable interest.
-In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
-This bimodal distribution is shown in the upper left panel of Figure~\ref{fig:fig1}.
+\red{where to put?} Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr to Gyrs for Type Ia), the ratio between $\alpha$-elements and Fe is expected to generally decrease with time.
 
-There are essentially two approaches to explaining the bimodality.
+Broadly speaking, there are three approaches to explaining the bimodality.
 First, it is a result of internal secular processes that generate the bimodality through radial migration \citep{2009MNRAS.396..203S,2021MNRAS.507.5882S,2023MNRAS.523.3791C} or clump formation \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
+Second, the bimodality is generated through gas infall scenarios, either from specific gas accretion episodes from the intergalactic medium \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}, or through a more self-consistent collapse sequence of the circumgalactic medium driven through feedback \citep{2021MNRAS.501.5176K}.
+Third and finally, the bimodality is generated through a merger process, either by enhancing the star formation rate (SFR) of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
+Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
 
-Second, the bimodality is generated through gas infall scenarios, either from specific gas accretion episodes from the intergalactic medium \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}, or through a more self-consistent collapse sequence of the circumgalactic medium driven through feedback \citep{2021MNRAS.501.5176K}.
-Third and finally, the bimodality is generated through a merger process, either by enhancing the SFR of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
-The fact that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
-
-In \citet{2024arXiv240707985B} we argued for an alternate formation scenario of the bimodality, for which we provide further support in this work.
+% In \citet{2024arXiv240707985B} (hereafter Paper~I) we argued for an alternate formation scenario of the bimodality.
 In this scenario, the bimodality is formed through a brief quiescent period in the Galaxy's history.
 During this period, which lasted $\sim300\,\Myr$ in that setup, two things happen.
-First, as the chemical evolution of the galaxy proceeds, fewer stars form.
-Second, because the SFR is lower, $\alpha$-element production drops and so the \alphaFe{} of the gas drops as well.
-This is conceptually similar to some variants of the two-phase infall scenarios which allow for a brief halt in the star formation rate \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period is much shorter in \citet{2024arXiv240707985B}.
+First, because the SFR is lower, the number of $\alpha$-producing Type~II relative to Type~Ia SNe becomes quite small.
+Iron-peak elements are produced in great amounts while $\alpha$-elements are not, leading to a sudden drop in the \alphaFe{} of star-forming gas.
+Second, the lower SFR means that any time the star-forming gas spends in the region between the high- and low-$\alpha$ sequences is deemphasized in the present-day star counts.
+This is conceptually similar to some variants of the two-phase infall scenarios which allow for a brief halt in the star formation rate \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period is much shorter in Paper~I.
 The combination of these two effects is what leads to the valley in between the high- and low-$\alpha$ sequences.
 
-In that work, we used idealized simulations of a galaxy merger that triggered a starburst which preceded the quiescent period.
-However, we argued that the merger aspect of that work was not necessary, but rather the quiescence.
-In this work, we study a subhalo from the Illustris TNG50 simulation which demonstrates this.
-This subhalo of interest (SoI) exhibits the sequence of events presented in \citet{2024arXiv240707985B} after a simple post-processing step which enhances the \alphaFe{} of old star particles.
+In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,Myr$) quiescent period in the Galaxy's history, which has two effects.
+First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
+Second, the lower SFR results in fewer stars forming in the region between the high- and low-$\alpha$ sequences, reducing the occurance of this transitional population in present-day observations.
+This mechanism resembles two-phase infall models that incorporate a temporary halt in star formation \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period in Paper~I is much shorter.
+The combination of these two effects creates the valley between the high- and low-$\alpha$ sequences.
+
+In Paper~I, we used idealized simulations of a galaxy merger that triggered the quiescent period.
+However, we argued that the merger aspect of that work was not necessary.
+In this work, we study a subhalo, or galaxy, from the Illustris TNG50 simulation demonstrating this.
+This subhalo of interest (SoI) exhibits the sequence of events presented in Paper~I after a simple post-processing step which increases the \alphaFe{} of old star particles.
+This post-processing is motivated by recent work demonstrating that the star formation efficiency (SFE) of the dense gas present at high-$z$ is too low \citep{2024arXiv240909121H}.
 The SoI undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
 However, instead of being preceded by a merger, the quenching is preceded by apparent bar-induced AGN activity.
-Therefore, this work serves as a verification that the scenario in \citet{2024arXiv240707985B} is possible in cosmological simulations and can occur in non-merger scenarios.
+Therefore, this work serves as a verification that the scenario in Paper~I is possible in cosmological simulations and does not require a merger.
 
@@
 \subsection{IllustrisTNG Sample}\label{ssec:tng}
-We have made use of the Illustris TNG50 simulation \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$).
+We use Illustris TNG50 \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$).
 It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG model \citep{2013MNRAS.436.3031V, 2017MNRAS.465.3291W, 2018MNRAS.473.4077P}.
-This model includes several subgrid processes: a wind generation model, chemical enrichment from supernovae and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.
+This model includes several subgrid processes: a wind generation model, chemical enrichment from SNe and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.
 
-One piece of the TNG model of note for this work is the BH accretion and feedback method \citep{2017MNRAS.465.3291W}.
-The black hole accretion rate ($\dot{M_{\textrm{BH}}}$) is computed using the local structure of the gas phase with the Bondi-Hoyle-Lyttleton formula \citep{1939PCPS...35..405H,1944MNRAS.104..273B,1952MNRAS.112..195B}, with a maximum of the Eddington accretion rate ($\dot{M_{\textrm{edd}}}$).
+One piece of the TNG model of note for this work is the black hole (BH) accretion and feedback method \citep{2017MNRAS.465.3291W}.
+The BH accretion rate ($\dot{M}_{\textrm{BH}}$) is computed using the local structure of the gas phase with the Bondi-Hoyle-Lyttleton formula \citep{1939PCPS...35..405H,1944MNRAS.104..273B,1952MNRAS.112..195B}, with a maximum of the Eddington accretion rate ($\dot{M}_{\textrm{edd}}$).
 The model allows the BH to be either in a kinetic radio-mode or a thermal quasar-mode.
-If the Eddington ratio ($\dot{M_{\textrm{BH}}}/\dot{M_{\textrm{edd}}}$) exceeds a threshold ($M_{\textrm{BH}}$-dependent, but $\sim0.001--0.1$), the BH is in the quasar mode and injects a large amount of thermal energy into its surroundings.
+If the Eddington ratio ($\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$) exceeds a threshold ($M_{\textrm{BH}}$-dependent, but $\sim0.001$--$0.1$), the BH is in the quasar mode and injects a large amount of thermal energy into its surroundings.
 
@@
 The chosen mass range is broadly consistent with the expected mass of the Milky Way at this redshift \citep{2013ApJ...771L..35V}.
-We chose to make our selection of galaxies at $z=1.5$ instead of at lower redshift because we wished to capture the \textit{formation} of any multimodal structure.
-We did not want contamination by mergers at lower redshift which we know contribute very little to the Milky Way's disk stars \citep[e.g.,][]{2016ARA&A..54..529B}.
+We choose to make our selection of galaxies at $z=1.5$ instead of at lower redshift because we wish to capture the \textit{formation} of multimodal structure.
+Mergers at lower redshift contribute very little to the Milky Way's disk stars \citep[e.g.,][]{2016ARA&A..54..529B}, and would act as a contaminant in our sample.
 
-We examined the abundance distribution in the \MgFe{}-\FeH{} plane of this sample of subhalos by eye.
-Not many subhalos had multimodal structure, and any structure that was present was relatively weak compared to that observed in the Milky Way.
-We then applied a post-processing to the \MgFe{} of stars by adding to each star particle a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time of each star particle.
-With this post-processing, we found that much more structure was generally present.
+We examine the abundance distribution in the \MgFe{}-\FeH{} plane for this sample of subhalos by visual inspection.
+Few subhalos display multimodal structure, and when present, it is much weaker compared to that observed in the Milky Way.
+We then apply a post-processing step to the \MgFe{} of the stars, adding a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ to each star particle, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$), and $t_{\textrm{form}}$ is the formation time of the star particle.
+After this adjustment, which we justify in Section~\ref{ssec:sfe} based on TNG underpredicting the SFE of dense gas, we observe that the abundance structure becomes significantly more pronounced.
 
@@
 
-We selected subhalo 172175 (the ID at snapshot 40) for its particular resemblance to the Milky Way.
+We select subhalo 172175 (the ID at snapshot 40) for its resemblance to the Milky Way.
 We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
 We refer to this subhalo as our subhalo of interest (SoI).
-
-\subsection{Bar Catalog}\label{ssec:barcat}
-In order to study the evolution of the morphology of our SoI, we make use of the \citet{2022MNRAS.515.1524Z} catalog.
-They provide a decomposition of all galaxies with at least $10^4$ star particles, as well as an estimate of the bar strength.
-This taken to be the maximum of the second Fourier mode ($A_{2,\textrm{max}}$) within the bar region (not including spiral arms).
+\red{Add some morphological details of gal here}
 
@@
 First, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}.
-We make the same selection cuts as in \citet{2024arXiv240707985B}, described in their Section~2.4.
-These are meant to select only giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's.
+We make the same selection cuts as in Section~2.4 of Paper I.
+These criteria are meant to select giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's.
 This results in a sample of 54,777 stars.
@@
 We then further considered a dataset of stellar ages from the APOKASC2 catalog \citep{2018ApJS..239...32P}.
-This uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
+This catalog uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
 Using only stars with $25\%$ age uncertainties (taken as the maximum of the upper and lower uncertainty), we cross-match this catalog to our larger sample from ASPCAP which results in a sample of 1201 stars.
@@
 Only faint structure is seen in the lowest bin (blue, $-0.75\,\dex$).
-The right column shows the same subhalo but after increasing the \MgFe{} value of star particles formed before $z=1.5$ linearly with formation time (specifically by incrementing \MgFe{} by $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ if $t_{\textrm{form}} < t_{1.5}$, where $t_{1.5}$ is the age of the universe at $z=1.5$).
+The right column shows the same subhalo but after increasing the \MgFe{} value of star particles formed before $z=1.5$ linearly with formation time (with a slope of $0.1\dex/\Gyr$).
 A clear bimodality is shown in these panels which, unlike in the Milky Way, is present at all metallicities.}
@@
 The main result of our paper is given in Figure~\ref{fig:fig1}.
-Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle and right columns).
+Here, we compare the abundance plane in the Milky Way (left column) to that of our subhalo of interest (middle and right columns).
 The upper panels show the 2D distribution in the space of \MgFe{}-\FeH{}.
@@
 
-The colored vertical lines are indicated at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations.
+The colored vertical regions are indicated at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations.
 The lower panels show 1D histograms of \MgFe{} in bins centered on these values.
 The bins for the Milky Way/simulations have width $0.2$/$0.05\,\dex$.
-The \MgFe{} values are given offsets so their medians are at zero.
 The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities.
@@
 We use age instead of formation time in order to better facilitate comparisons to observations.
-These panels are true 2D histograms, with a logarithmic colormap normalized to the maximum of the plot.
-The values of \MgFe{} are offset so their medians are at zero.
+These panels show 2D histograms, with a logarithmic colormap normalized to the maximum of the plot.
+To prevent overlap, the values of \MgFe{} are given offsets of $0$, $-0.5$, $-1$, and $-1.5$, in order of increasing \FeH{}.
 
-There is a gap in the ages that occurs at an age of $10.6\,\Gyr$, which we mark with a vertical dashed line.
+In the SoI, there is an age gap at $sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
 Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
-In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly depressed \MgFe{} than stars which form a short time later.
+In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly reduced \MgFe{} than stars which form a short time later.
 
-In the lower panels we plot to the left data from the Milky Way and to the middle and right from the fiducial and $\alpha$-enhanced SoI, respectively.
-For the simulations, we add $15\%$ age and $0.01\,\dex$ \MgFe{} Gaussian errors.
-These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:obs_err} for plots of the observational errors).
-The error in \MgFe{} is not signficant, but the age error, which is $1.5\,\Gyr$ at $10\,\Gyr$, smears out the distribution before and after the dashed line.
-The $\alpha$-enhanced SoI still shows two separate populations in this plot, but they now significantly overlap in age.
+In the lower row, the left panel shows data from the Milky Way, while the middle and right panels correspond to the fiducial and $\alpha$-enhanced SoI, respectively.
+For the simulations, we introduce Gaussian errors of $15\%$ in age and $0.01,\dex$ in \MgFe{}.
+These error values align with the observational uncertainties from the APOKASC2 and APOGEE datasets, which the Milky Way panel (lower left) is based on (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
+While the error in \MgFe{} is relatively minor, the age error ($1.5\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
+Despite this, the $\alpha$-enhanced SoI still shows two distinct populations, although their ages now overlap more significantly.
 
-The Milky Way distribution (lower left panel) bears some resemblance to the $\alpha$-enhanced SoI.
-In particular, the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively) show what appears to be two populations overlapping in age but nonetheless separated in \MgFe{}.
-These are the bins at which the bimodality is strongest (upper left panel of Figure~\ref{fig:fig1}).
+Interestingly, the Milky Way distribution (lower left panel) exhibits similarities to the $\alpha$-enhanced SoI.
+Specifically, in the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively), there appear to be two populations that overlap in age but remain distinct in \MgFe{}.
+These are the bins where the bimodality is most pronounced (as seen in the upper left panel of Figure~\ref{fig:fig1}).
 
 \subsection{Evolutionary History}\label{ssec:evol}
-
 \begin{figure}
@@
   \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200.pdf}
-  \caption{\textbf{The evolutionary history of our subhalo of interest.} The upper panel shows the SFH of our subhalo.
-This SFH is computed using the SFR within twice the stellar half-mass radius in our SoI's main progenitors.
-In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha} ($\sim3.2\,\Gyr$), which delineates the separation between the high- and low-$\alpha$ sequences.
-The gap in ages is naturally associated with a gap in the SFH located at the dashed line.
-The middle panel shows the BH accretion rate as a fraction of the maximum (Eddington) accretion rate across time.
-The accretion rate is high early on, but then drops.
-The gap in ages (dashed line) is coincident with a local peak in the BH accretion rate.
-In the lower panel we show the mass assembly of the halo, given as the mass within the radius that encloses $200\times$ the mean density of the universe.
-In this plot mergers are shown as sudden increases in $M_{200}$.
-Mergers at very early times when the halo is signifcantly less massive than its $z=0$ mass are not shown, but one can see that no clear merger is associated with the gap in stellar ages.
-Two mergers occur later on at $t\sim10$ and $\sim12\,\Gyr$.}
+  \caption{\textbf{The evolutionary history of our subhalo of interest.} The left column shows the SFH, BH accretion rate, and virial mass ($M_{200}$) over the entire time span, while the right column zooms in on the period from $t\sim2\,\Gyr$ to $t\sim5\,\Gyr$.
+The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$, corresponding to the separation between the high- and low-$\alpha$ sequences (as shown in Figure~\ref{fig:alpha}).
+The middle panel shows the BH accretion rate as a fraction of the Eddington limit, and the lower panel shows the virial mass, representing the mass enclosed within a radius where the density is $200\times$ the mean cosmic density.}
   \label{fig:history}
@@
 
-In an effort towards understanding the events in our SoI's history that led to the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of some of its key quantities.
-In the upper panel of Figure~\ref{fig:history}, we show the SFH of our galaxy with the same dashed line as in Figure~\ref{fig:alpha} (at an age of $10.6\,\Gyr$ in that plot is at a time of $\sim3.2\,\Gyr$ here).
-This SFH is computed using the SFR within twice the stellar half-mass radius in our SoI's main progenitors.
-We see two peaks in the SFH at $t\sim2.5$ and $\sim4.5\,\Gyr$ of an amplitude of about $50$ and $30\,\Msunyr$.
-The dashed line corresponds to a relative drop in the SFR, down to about $3\,\Msunyr$ before quickly recovering.
+To understand the key events driving the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of several properties of the subhalo in Figure~\ref{fig:history}.
+The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$ from the high- to low-$\alpha$ sequences, as in Figure~\ref{fig:alpha}.
+The upper panel in the left column shows the the SFR (computed for all gas cells in the subhalo).
+There are two peaks at $t\sim2.5\,\Gyr$ and $t\sim4.5\,\Gyr$ with maximum values of $50\,\Msun/\textrm{yr}$ and $30\,\Msun/\textrm{yr}$, respectively.
+Around the high- to low-$\alpha$ transition, there is a dip in the SFR, which drops by an order of magnitude to about $3\,\Msun/\textrm{yr}$.
+The right panel zooms in on the period between $t=2\,\Gyr$ and $5\,\Gyr$, where we observe a sharp recovery in the SFR following the quiescent phase.
+In a single snapshot (spanning roughly 150 Myr), the SFR increases from about $3\,\Msun/\textrm{yr}$ to $10\,\Msun/\textrm{yr}$.
 
-The middle panel shows the accretion rate of the central black hole as a fraction of the maximum (Eddington) accretion rate.
-Early in its history ($t<2\,\Gyr$), the subhalo experiences high accretion rates.
-The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it fails to show on this linear plot.
-However, at the dashed line ($\sim3.2\,\Gyr$) there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
-This places the BH firmly in the thermal quasar-mode, and allows it to inject large amounts of thermal energy into the center of the galaxy.
+The middle panels track the accretion rate of the central BH as a fraction of the Eddington rate.
+Early in the subhalo's history ($t<2\,\Gyr$), the BH experiences high accretion, which steadily declines until $t\sim5\,\Gyr$.
+Around $t\sim3.2\,\Gyr$, the BH accretion rate peaks again, reaching approximately $30\%$ of the Eddington limit, placing the BH in quasar mode and injecting significant thermal energy into the galaxy's center.
+The middle right panel shows the period between $t=2$ and $5\,\Gyr$.
 
-The lower panel shows the virial mass of the subhalo, as measured by $M_{200}$ -- the mass within the radius that encloses a region of density $200\times$ the mean density of the universe.
-Early on at $t<4\,\Gyr$ the virial mass grows roughly linearly up to $\sim2\times10^{12}\,\Msun$.
-After that, the virial mass remains roughly constant until sharp increases at $t\sim10$ and $\sim12\,\Gyr$.
-The transition in the virial mass from linear to constant at $t\sim4\,\Gyr$ is followed $1\,\Gyr$ later by a sudden drop in the SFR and BH accretion rate.
+The lower panel illustrates the growth of the subhalo's virial mass ($M_{200}$).
+Early on ($t<4\,\Gyr$), $M_{200}$ increases roughly linearly, reaching about $2 \times 10^{12}\,\Msun$.
+After this, the mass remains relatively stable until jumps occur around $t\sim10$ and $\sim12\,\Gyr$, indicative of mergers.
+There are no mergers related to the earlier quiescent period around $t\sim3.2\,\Gyr$, as no major mass jumps are observed during this time.
+The lower right panel shows the period between $t=2$ and $5\,\Gyr$.
 
@@
   \caption{Surface density projections of gas (top row) and star particles (middle row) in our SoI across snapshots at different times during the high- to low-$\alpha$ transition.
-Below the projections is a plot showing the SFR, BH accretion rate (in units of $\dot{M_{\textrm{BH}}}/\dot{M_{\textrm{Edd}}}$), and bar strength ($A_2/A_0$ for $R<2$ kpc).
+Below the projections is a plot showing the SFR, BH accretion rate (in units of $\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$), and bar strength ($A_2/A_0$ for $R<2$ kpc).
 Time ranges from $\sim2.4\,\textrm{Gyr}$ to $\sim3.6\,\textrm{Gyr}$, corresponding to redshifts from $z\sim2.7$ to $z\sim1.8$.
@@
 This rise is accompanied by the appearance of elongated features in the gas and stars consistent with a bar.
-    \item BH accretion increases: Following the increase in bar strength by about a snapshot ($\sim150\,\Myr$ here), the black hole accretion rate ($\dot{M_{\textrm{BH}}}/\dot{M_{\textrm{Edd}}}$) shows a significant spike, rising from a minimum of $\sim0.08$ at $t=2.84\,\Gyr$ to a maximum of $\sim0.29$ at $t=3.13\,\Gyr$.
-    \item SFR declines: After the increase in black hole accretion, the star formation rate (SFR) begins to decline.
-The decrease in SFR is gradual and continues as the black hole accretion rate remains elevated.
-By approximately $3.2\,\textrm{Gyr}$, the SFR reaches a more quiescent state, where it remains relatively low.
+    \item BH accretion increases: Following the increase in bar strength by about a snapshot ($\sim150\,\Myr$ here), the BH accretion rate ($\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$) shows a significant spike, rising from a minimum of $\sim0.08$ at $t=2.84\,\Gyr$ to a maximum of $\sim0.29$ at $t=3.13\,\Gyr$ for one snapshot.
+    \item SFR declines: The SFR declines starting from a maximum of $54.3\,\Msunyr$ at $t=2.84\,\Gyr$ down to $3.6\,\Msunyr$ at $t=3.28\,\Gyr$.
+In the next snapshot at $t=3.45\,\Gyr$ the SFR recovers to $12.2\,\Msunyr$ and remains above
+
+    After the increase in BH accretion, the star formation rate (SFR) begins to decline.
+The decrease in SFR steadily commences as the BH accretion rate remains elevated.
+By approximately $3.2\,\textrm{Gyr}$, the SFR reaches a more quiescent state at $\sim3\,\Msunyr$.
+After one snapshot, the SFR increases to
 \end{enumerate}
@@
   \includegraphics[width=\columnwidth]{fig/mgfe_vice.pdf}
-  \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one zone chemical evolution model, described in Section~\ref{ssec:onezone_met}.
-The upper panel shows the evolution of \MgFe{} over $2\,\Gyr$ while the lower panel shows the negative of its time derivative.
-Decreasing the star formation timescale $\tau_{\star}=M_{\textrm{gas}/\textrm{SFR}}$ leads to a more rapid decline in \MgFe{}.
-At its steepest decline ($t\sim0.5\,\Gyr$), an order of magnitude decrease in $\tau_{\star}$ leads to a slope nearly a factor of $2$ larger.
-At later times ($t>1\,\Gyr$), the models with smaller $\tau_{\star}$ reach their steady-state \MgFe{} value more quickly.}
+  \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one-zone chemical evolution model, described in Section~\ref{ssec:onezone_met}.
+The evolution for different SFE values of $2$, $1$, and $0.2\,\textrm{Gyr}^{-1}$ are shown in blue, orange, and red, respectively.
+The upper panel shows the evolution of \MgFe{} over $2\,\Gyr$, while the lower panel shows the negative of its time derivative.
+Increasing the SFE ($\dot{Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$) leads to a more rapid decline in \MgFe{}.
+At its steepest decline ($t\sim0.5\,\Gyr$), increasing the SFE by an order of magnitude results in a slope nearly twice as steep.
+At later times ($t > 1\,\Gyr$), models with higher SFE reach their steady-state \MgFe{} value more quickly.}
   \label{fig:vice}
@@
 
-We showed in Figure~\ref{fig:fig1} that a time-linear $\alpha$-enhancement of old stars (forming before $z=1.5$) led to the emergence of a strong chemical bimodality.
-This $\alpha$-enhancement is equivalent to saying that \alphaFe{} declines more rapdily with time at high-$z$.
-In Figure~\ref{fig:vice} we demonstrate an argument for why this steeper decline in \alphaFe{} might be absent in TNG.
+In Figure~\ref{fig:fig1}, we showed that a time-linear $\alpha$-enhancement of older stars (formed before $z=1.5$) leads to the emergence of a pronounced chemical bimodality.
+This $\alpha$-enhancement corresponds to a more rapid decline in \alphaFe{} over time at high redshifts.
+Figure~\ref{fig:vice} demonstrates that having too low SFE at high densities is a plausible explanation for why such a steep decline in \alphaFe{} might not be occuring in the fiducial TNG model.
 
-We show in the upper panel the evolution of \MgFe{} of three one zone chemical evolution models which vary the star formation (SF) timescale.
-This timescale, $\tau_{\star}$, is the inverse of the SF efficiency.
-A shorter SF timescale leads to a more rapid reduction in \MgFe{}.
-In the shortest timescale model, $\tau_{\star}=0.5\,\Gyr$, \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ in $2\,\Gyr$.
-In comparison, the longest timescale model, $\tau_{\star}=5\,\Gyr$ only drops to $\sim0.2\,\dex$ in the same time.
+The upper panel of Figure~\ref{fig:vice} presents the evolution of \MgFe{} in three one-zone chemical evolution models with varying star formation efficiencies (SFE).
+A higher SFE leads to a faster reduction in \MgFe{}.
+In the model with the highest SFE ($2\,\Gyr^{-1}$, blue, where SFE is $\dot{\Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ over $2\,\Gyr$.
+In contrast, the model with the lowest SFE ($0.2\,\Gyr^{-1}$) only reaches $\sim0.2\,\dex$ within the same period.
 
-The lower panel shows the negative of the time derivative of \MgFe{}.
-This panel shows the same behavior, with the slope of the $\tau_{\star}=0.5\,\Gyr$ model peaking at $-0.5\,\dex/\Gyr$ compared to the $5\,\Gyr$ model which peaks at $-0.25\,\dex/\Gyr$.
-After $1\,\Gyr$, the trend starts to reverse, with the longer SF timescale models declining more rapidly, though at a much reduced rate ($\sim-0.1\,\dex/\Gyr$) than at the peak.
+The lower panel shows the negative time derivative of \MgFe{} (i.e., the rate of decline).
+The model with the highest SFE ($2\,\Gyr^{-1}$, blue) has a peak decline rate of $-0.5\,\dex/\Gyr$, while the model with the lowest SFE ($0.2\,\Gyr^{-1}$) peaks at $-0.25\,\dex/\Gyr$.
+After $1\,\Gyr$, the trend begins to reverse, and the lower-SFE models catch up, though at a much slower rate ($\sim-0.1\,\dex/\Gyr$) compared to their peak.
+
+This analysis illustrates that a higher SFE at early times (high redshift) leads to a faster decrease in \MgFe{}.
+Recent work has suggested that the SFE in such dense regions in TNG may indeed be too low, as discussed in Section~\ref{ssec:sfe}.
 
 \section{Discussion}\label{sec:disc}
-In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SoI before and after the $\alpha$-enhancement.
-It is visibly obvious that the TNG SoI is unimodal before the $\alpha$-enhancement and bimodal afterwards (ignoring the minor mode at high-\MgFe{}).
+In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SoI before and after our $\alpha$-enhancement post-processing procedure.
+It is clear that the TNG SoI is unimodal before the $\alpha$-enhancement and multi-modal afterwards.
 Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the SoI?, and (2) what justifies the $\alpha$-enhancement?
@@
 \subsection{Cause of Bimodality}\label{ssec:bim_cause}
-An extensive analysis of our SoI is beyond the scope of this project, but here we argue that the evidence is consistent with the scenario presented in \citet{2024arXiv240707985B}.
+An extensive analysis of our SoI is beyond the scope of this work, but here we argue that the evidence is consistent with the scenario presented in Paper I.
 They presented an idealized simulation resembling the merger between the Milky Way and GSE.
@@
 The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} denotes the transition between the high- and low-$\alpha$ sequences.
-We place it at an age of $10.6\,\Gyr$ or a formation time of $\sim3.2\,\Gyr$.
+We place it at a lookback time of $10.6\,\Gyr$ or a formation time of $\sim3.2\,\Gyr$.
 The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} so their medians are at zero).
-Stars which formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
+Stars formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
 At the line, we see a gap in the $\FeH=-0.5$ and $-0.25$ bins.
@@
 
-During this period of suppressed SF, we argue that the relative lack of enrichment of Type~II SNe which leads to a lower rate of Mg production.
-This leads to a rapid reduction in \MgFe{}.
-This, combined with a lack of SF in the first place, leads to a scarcity of star particles in the region intermediate between the high- and low-$\alpha$ sequences.
-A more in-depth explanation is given in Section~4.1 in \citet{2024arXiv240707985B}.
+During this period of suppressed SF, we argue that the lack of enrichment of Type~II relative to Type~Ia SNe leads to a lower rate of Mg production.
+Therefore, \MgFe{} rapidly declines.
+This, combined with a lack of SF in the first place, leads to a scarcity of star particles in the intermediate region between the high- and low-$\alpha$ sequences.
+A more in-depth explanation is given in Section~4.1 in Paper~I.
 
-In the fiducial TNG distribution shown in the upper middle panel of Figure~\ref{fig:alpha}, the same general behavior with respect to the dashed line is present.
-However, because the \MgFe{} decline before the dashed line is not as strong, star particles which formed before and after the dashed line overlap in the \MgFe{} distribution shown in Figure~\ref{fig:fig1}.
+In the fiducial TNG distribution, shown in the upper middle panel of Figure~\ref{fig:alpha}, the same general behavior is present.
+However, because the \MgFe{} decline before the quiescent period is slower, star particles which formed before and after this period overlap in the \MgFe{} distribution shown in Figure~\ref{fig:fig1}.
 
-It is also worth noting that in both the fiducial and $\alpha$-enhanced SoI, there is a sort of rebound effect in \MgFe{}.
+It is also worth noting that in both the fiducial and $\alpha$-enhanced SoI show a slight rebound effect in \MgFe{}.
 The star particles which form directly after the dashed line have a slightly lower \MgFe{} than stars which form after.
-This was seen in Figure~9 of \citet{2024arXiv240707985B}.
-In that work, it was argued that this occurs because, during the period of suppressed SF, the \alphaFe{} of star forming gas plummets since there is no contribution from Type~II SNe.
+This was also predicted in Figure~9 of Paper~I, where it was argued that during the period of suppressed star formation, the \alphaFe{} ratio of the star-forming gas drops sharply due to the reduced contribution of Type~II relative to Type~Ia SNe.
 Later, the \alphaFe{} of the gas will recover when the SFR also recovers, but there is a brief window when old, low-$\alpha$ stars can form.
+A similar behavior was seen in the one-zone models with bursty SFHs in \citet{2020MNRAS.498.1364J}.
 
@@
 The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models.
-Isolating the cause of the ``incorrect''\footnote{Our case study of a single galaxy, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} \MgFe{} vs time evolution at high-$z$ is not straightforward nor, in our opinion, even possible.
-However, we do offer one reasonable explanation -- the SFE at high densities, more present at high-$z$, is too low.
+Isolating the cause of the ``incorrect''\footnote{Our case study of a single subhalo, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} \MgFe{} vs time evolution at high-$z$ is not straightforward nor, in our opinion, even possible.
+However, we do offer one reasonable explanation: the SFE at high densities, more present at high-$z$, is too low.
 
@@
 The details of our setup is given in Section~\ref{ssec:onezone_met}.
-We vary the SF timescale, $\tau_{\star}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio as a function of time.
+We vary the SFE of the model ($\dot{Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), and examine the impact on the \MgFe{} ratio as a function of time.
 We find that shorter SF timescales do lead to a more rapid reduction in \MgFe{}.
-The rate of decrease in \MgFe{}, at its maximum, varies from $\sim-0.25\,\dex/\Gyr$ in the $\tau_{\star}=5\,\Gyr$ model to $\sim-0.5\,\dex/\Gyr$ in the $\tau_{\star}=0.5\,\Gyr$ model.
-For our post-processing, assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
-Such a difference is well within the range of \MgFe{} decrease seen in our different $\tau_{\star}$ models.
+The rate of decrease in \MgFe{}, at its maximum, varies between $\sim-0.25$, $-0.35$, and $-0.5\,\dex/\Gyr$ in the $\textrm{SFE}=0.2$, $1$, and $2\,\Gyr^{-1}$ models, respectively.
+For our post-processing, we assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
+Such a difference is well within the range of \MgFe{} decrease seen in our different $\tau_{\star}$ models, implying a factor of only $\sim2$ in the SFE is needed to reach our post-processing slope.
 
-S.
-Hassan et al.
-(in preparation) demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude.
-This is well within our needed factor of $2$ in $\tau_{\star}$.
-Therefore, our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified.
+\citet{2024arXiv240909121H} demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude.
+This is well within our needed factor of $2$ in the SFE (see Figure~\ref{fig:vice}).
+Therefore, \MgFe{} should decline more rapidly with a different feedback model (or future iteration of the TNG model) that leads to a higher SFE at high densities.
+
 An intuitive understanding of the impact the decline in \alphaFe{} vs time has is that, when \alphaFe{} declines rapidly, it is a better estimator of age.
-When it is a better estimator of age, events which are separated temporally become better separated in the abundance plane.
+When \alphaFe{} is a better estimator of age, events which are separated temporally become better separated in the abundance plane.
 
-\subsection{Comparison to Observations}\label{ssec:compare_obs}
+\subsection{Direct Comparison to Observations}\label{ssec:compare_obs}
 The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC2 catalog.
@@
 \subsection{Cause of Quiescence}\label{ssec:cause_qui}
-% We show the evolution of the SoI in greater detail at the transition between the high- and low-$\alpha$ sequences in Figure~\ref{fig:history_zoom}.
-As in Figure~\ref{fig:history} we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$, in red.
-From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54\,\Msunyr$ to $3.6\,\Msunyr$.
-The minimum in the SFR is nearly coincident with the transition line.
-
-% We can see more clearly here that the BH accretion rate (red), in units of the Eddington accretion rate, increases from a value of $\sim0.08$ at $\sim2.8\,\Gyr$ to a maximum of $\sim0.3$ at $\sim3.1\,\Gyr$, right before the transition.
-This rise in the AGN accretion rate is preceded by a strengthening of the bar, which rises from an $A_2$ of $\sim0.1$ at $t\sim2.4\,\Gyr$ to an $A_2$ of $\sim0.5$ at $\sim3.1\,\Gyr$, the time of the peak BH accretion rate.
-
 It is natural to question why the minimum in the SFR occurs.
-In \citet{2024arXiv240707985B}, AGN activity from a merger was the suspected cause.
+In Paper~I, AGN activity from a merger was the suspected cause.
 Here, we can see that there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
@@
 
-In Figure~\ref{fig:history_zoom}, we take a closer view of the evolution of our SoI at the transition between the high- and low-$\alpha$ sequence, which we denote with the same line at an age of $10.6\,\Gyr$ ($t\sim3.2\,\Gyr$) as before.
-Here, we see that indeed the drop in the SFR ( $\sim3.6\,\Msunyr$ at $t\sim3.3\,\Gyr$) reaches a minimum one snapshot after the maximum in the BH accretion rate ($\sim0.3\times\dot{M_{\textrm{edd}}}$ at $t\sim3.1\,\Gyr$).
+In Figure~\ref{fig:seq}, we combine a visual inspection of the gas (upper row) and stellar (middle row) surface densities with the evolution of three key quantites (lower plot): SFR, BH accretion rate, and bar strength in blue, orange, and red, respectively.
+These are shown for nine snapshots, from snapshot 27 to 35, corresponding to redshift $2.73$ to $1.82$ or cosmic time from $2.38\,\Gyr$ to $3.59\,\Gyr$.
+A vertical dashed line is included in the lower panel separating the formation of the low- and high-$\alpha$ sequence at an age of $10.6\,\Gyr$ (cosmic time $\sim3.2\,\Gyr$), as in Figures~\ref{fig:alpha} and \ref{fig:history}.
 
-The gaseous surface density images in Figure~\ref{fig:images_gas} are helpful to understand this moment in the SoI's history.
-The third row, from $t=2.84$ to $3.28\,\Gyr$ shows this moment, with the rightmost $t=3.28\,\Gyr$ marking the transition from high- to low-$\alpha$ formation.
-The gas fraction (bottom right number) quickly drops from $25\%$ to $3\%$, accompanied by not only a high SFR ($54.3\,\Msunyr$ at maximum) but also an increasing BH accretion rate.
-
-This increasing BH accretion rate is also preceded by the formation of a stellar bar at the center of the galaxy as seen in Figure~\ref{fig:images_star}.\footnote{The bar is already at a strength of $\Atmax\sim0.1$ before, so it either forms or strengthens depending on one's interpretation.
-We choose the former.} Starting from $t=2.38\,\Gyr$, the bar strength grows from $\Atmax=0.1$ to $0.5$ at $t=3.13\,\Gyr$, the peak of the BH accretion rate.
-Note that the bar strength considers only the region where the phase of the second Fourier mode is constant, and so spiral structure as seen in, e.g., the $t=2.38\,\Gyr$ snapshot is not eligible for \Atmax{}.
-
-The scenario implied by all the available evidence is that: 
+As described in Section~\ref{ssec:sequence_of_events}, the following sequence of events occurs: the bar strengthens and then the BH accretion rate spikes, all while the SFR of the galaxy declines.
+This is suggestive of the following causal sequence:
 \begin{enumerate}
@@
   \item triggers a high BH accretion rate and quasar-mode thermal feedback, which
-  \item clears gas out of the galaxy.
+  \item clears gas out of the galaxy leading to quiescence.
 \end{enumerate}
-This picture is supported by work showing that in simulations bars should be able to fuel AGN \citep{1990Natur.345..679S,2010MNRAS.407.1529H}, and that barred galaxies preferentially host AGN \citep{2022A&A...661A.105S}.
-At high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+This quiescent period then leads to the bimodality, as discussed in Section~\ref{ssec:bim_cause}.
+It is not possible to prove the causality of this sequence of events because of the sparse snapshot spacing in TNG50, and so this is left to future work.
+
+However, there is a significant body of theoretical and observational work in support of this picture.
+Bars and other non-axisymmetric features have long been argued to funnel gas into the centers of galaxies on theoretical grounds \citep{1989Natur.338...45S,2010MNRAS.407.1529H}.In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.
+Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+
+Since barred galaxies preferentially host AGN, we therefore predict that barred galaxies would preferentially host $\alpha$-bimodalities.
+The GECKOS survey, which aims to constrain the $\alpha$-bimodality of edge-on galaxies using integral field spectroscopy at different altitudes, could test this \citep{2024IAUS..377...27V}.
+On the other hand, the strength of a bar is not associated with the strength of the host AGN \citep[e.g.]{2022A&A...661A.105S}.
+So, it is not clear that bimodalities would be associated with bar strength.
 
@@
 The depletion time ($M_{\textrm{gas}}/\textrm{SFR}$) at the $t=2.84\,\Gyr$ snapshot is $204\,\Myr$, shorter than the time it takes for the SFR to reach its minimum.
-However, this has to be balanced by the fact that the depletion time is already short at this redshift.
-The average depletion time in the preceding 5 snapshots is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its CGM.
-A definitive account, difficult with the current simulation because of its sparse snapshot spacing, requires further work.
-
-% \subsection{Full Sample}\label{ssec:fullsamp}
+This implies the possibility of starvation as a quenching mechanism.
+However, the average depletion time in the preceding 5 snapshots (which are each $\sim150\,\Myr$ apart) is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its CGM.
+A definitive account, difficult with the current simulation outputs because of its sparse snapshot spacing, requires further work.
 
@@
 After applying a post-processing step that increased the \MgFe{} of star particles formed before $z=1.5$, this subhalo hosts a strong bimodality in the plane of \MgFe{} and \FeH{}, shown in Figure~\ref{fig:fig1}.
-This post-processing is justified by arguing that the SFE of dense gas is too low in TNG (Section~\ref{ssec:sfe}).
+This post-processing is justified by arguing that the SFE of dense gas is too low in TNG \citep[][see discussion in Section~\ref{ssec:sfe}]{2024arXiv240909121H}.
 
@@
 
-The reduction in the SFR has two effects.
-First, a lower production of Mg is the natural result of a lack of Type~II SNe.
+This bimodality can be traced to an event that occurred at an age of $10.6\,\Gyr$, or formation time of $\sim3.2\,\Gyr$ ($z\sim2$).
+Shown as a vertical dashed line in Figure~\ref{fig:alpha}, star particles that form before this time are at high-\MgFe{}, while star particles that form after are at low-\MgFe{}.
+This time is associated with a global reduction in the SFR (Figure~\ref{fig:history}), which appears to be related to AGN activity induced by the formation of a bar (Figure~\ref{fig:seq}).
+
+We argue that the reduction in the SFR has two effects which lead to the $\alpha$-bimodality.
+First, a lower production of Mg relative to Fe is the natural result of a lack of Type~II relative to Type~Ia SNe.
+The latter remain high due to their longer timescales, expediting a drop in \MgFe{}.
 Second, the lack of SF means that stars at \MgFe{} intermediate between the high- and low-$\alpha$ sequences never form.
-This is the same argument that was first presented in \citet{2024arXiv240707985B}.
-When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the Milky Way's abundance-age distribution (Section~\ref{ssec:compare_obs}).
+This argument is the same as presented in Paper~I and is consistent with the one-zone chemical evolution models of \citet{2020MNRAS.498.1364J}.
+When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the distribution observed in the Milky Way (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).
 
-While a strong claim about the cause of the quiescent period is difficult to make, we showed that the formation/strengthening of a bar could be responsible for triggering an episode of AGN activity.
-This work adds further support that the argument made in \citet{2024arXiv240707985B} is a plausible explanation for the Milky Way's abundance bimodality.
+This work adds further support to a scenario in which a quiescent period in the Milky Way's past is a plausible explanation for the Milky Way's abundance bimodality.
+We argued in Paper~I that the GSE merger could trigger this period.
+In this work we have argued that the formation of the Milky Way's bar could be responsible.
+In external galaxies, we predict that the presence of a bar is correlated with the presence of an $\alpha$-bimodality.
 

### 2024-10-07 paper/ms.tex
Move SNe timescales

@@
 Two classes elements have received particular attention in the Milky Way due to their disparate formation channels: iron-peak (such as Fe) and $\alpha$-elements (produced through the $\alpha$-process, such as O and Mg).
-Iron-peak elements are produced in both Type Ia and Type II supernovae (SNe) whereas $\alpha$-elements are produced predominantly through Type II SNe.
+Iron-peak elements are produced in both Type~Ia and Type~II supernovae (SNe) whereas $\alpha$-elements are produced predominantly through Type~II SNe.
 In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences shown in Figure~\ref{fig:fig1} \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
-
-\red{where to put?} Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr to Gyrs for Type Ia), the ratio between $\alpha$-elements and Fe is expected to generally decrease with time.
 
@@
 
-% In \citet{2024arXiv240707985B} (hereafter Paper~I) we argued for an alternate formation scenario of the bimodality.
-In this scenario, the bimodality is formed through a brief quiescent period in the Galaxy's history.
-During this period, which lasted $\sim300\,\Myr$ in that setup, two things happen.
-First, because the SFR is lower, the number of $\alpha$-producing Type~II relative to Type~Ia SNe becomes quite small.
-Iron-peak elements are produced in great amounts while $\alpha$-elements are not, leading to a sudden drop in the \alphaFe{} of star-forming gas.
-Second, the lower SFR means that any time the star-forming gas spends in the region between the high- and low-$\alpha$ sequences is deemphasized in the present-day star counts.
-This is conceptually similar to some variants of the two-phase infall scenarios which allow for a brief halt in the star formation rate \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period is much shorter in Paper~I.
-The combination of these two effects is what leads to the valley in between the high- and low-$\alpha$ sequences.
-
 In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,Myr$) quiescent period in the Galaxy's history, which has two effects.
-First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
+First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia\footnote{These SNe occur on different timescales (10s of Myr after star formation for Type~II, as compared to 100s of Myr to Gyrs for Type~Ia), so if the SFR drops, the number of Type~II SNe drops faster than Type~Ia.}, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
 Second, the lower SFR results in fewer stars forming in the region between the high- and low-$\alpha$ sequences, reducing the occurance of this transitional population in present-day observations.

### 2024-10-07 paper/ms.tex
Add summary table

@@
 \newcommand{\Atmax}{\ensuremath{A_{2,\textrm{max}}}}
+
+\newcommand{\rhalf}{\ensuremath{r_{\star,\textrm{half}}}}
 
@@
 
+\begin{table}[]
+  \centering
+  \begin{tabular}{ll}
+  \multicolumn{2}{c}{dark matter}                                                                  \\ \hline
+  \multicolumn{1}{l|}{$M_{200}$}                                      & $4.97\times10^{12}\,\Msun$ \\
+  \multicolumn{1}{l|}{$R_{200}$}                                      & $532\,\kpc$                \\
+                                                                      &                            \\
+  \multicolumn{2}{c}{baryons}                                                                      \\ \hline
+  \multicolumn{1}{l|}{$\rhalf$}                                       & $2\,\kpc$                  \\
+  \multicolumn{1}{l|}{$M_{\textrm{star}}(r<4\rhalf)$}                 & $7.6\times10^{12}\,\Msun$  \\
+  \multicolumn{1}{l|}{$M_{\textrm{gas}}(r<4\rhalf)$}                  & $2.6\times10^{11}\,\Msun$  \\
+  \multicolumn{1}{l|}{$\textrm{SFR}$}                                 & $0.56\,\Msunyr$            \\
+  \multicolumn{1}{l|}{$M_{\textrm{BH}}$}                              & $2.9\times10^{8}\,\Msun$   \\
+  \multicolumn{1}{l|}{$\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{Edd}}$} & $4.5\times10^{-5}$        
+  \end{tabular}
+  \caption{Summary statistics of our subhalo of interest at $z=0$.
+$M_{200}$ and $R_{200}$ are relative to the mean density of the universe, the SFR is for all gas bound to the subhalo, and the BH refers to the central BH.}
+  \label{tab:summ}
+\end{table}
+
 We select subhalo 172175 (the ID at snapshot 40) for its resemblance to the Milky Way.
 We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
+A summary of its key properties is given in Table~\ref{tab:summ}.
 We refer to this subhalo as our subhalo of interest (SoI).
-\red{Add some morphological details of gal here}
 

### 2024-10-07 paper/ms.tex
Update to match style of rest of text

--- 2024-10-07 paper/ms.tex
@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[linenumbers, twocolumn]{aastex631}
 
@@
 
-\title{Rising from the Ashes II: Can Bar Formation Lead to Abundance Bimodalities?}
+\title{Rising from the Ashes II: Did the Birth of the Milky Way's Bar Give Birth to the Birth of the Abundance Bimodality}
 
@@
 \author{James W. Johnson}
-\affiliation{Carnegie Science Observatories, Pasadena, CA, USA}
+\affiliation{The Observatories of the Carnegie Institution for Science, Pasadena, CA, USA}
 
-\author{Vadim Semenov}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{Lars Hernquist}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{Vedant Chandra}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
-
-\author{Charlie Conroy}
-\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
+\author{et al}
 
@@
 We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a sequence of starburst, brief quiescence, and then rejuvenation.
-Following a minor post-processing adjustment -— motivated by recent findings on the star formation efficiency in TNG -- which increases the \alphaFe{} values of older star particles, we demonstrate that this galaxy exhibits a pronounced bimodal distribution in the \alphaFe{}-\FeH{} plane.
+After a minor post-processing step which boosts the \alphaFe{} of old star particles, we demonstrate that this galaxy hosts a strongly bimodal distribution in the \alphaFe{}-\FeH{} plane.
 The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
@@
 The stellar surface abundances of most elements retain the composition of their natal gas cloud.
-Therefore, the present-day distribution of their abundances encodes the chemical history of a galaxy's gas phase.
-Two classes elements have received particular attention in the Milky Way due to their disparate formation channels: iron-peak (such as Fe) and $\alpha$-elements (produced through the $\alpha$-process, such as O and Mg).
-Iron-peak elements are produced in both Type~Ia and Type~II supernovae (SNe) whereas $\alpha$-elements are produced predominantly through Type~II SNe.
-In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences shown in Figure~\ref{fig:fig1} \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
+Therefore, the present-day distribution of stellar surface abundances encodes the chemical history of a galaxy's gas phase.
+Two elements have received particular interest in the Milky Way: Fe and $\alpha$-elements (elements produced through the $\alpha$-process, such as O and Mg).
+Fe is produced in both Type~Ia and Type~II SNe whereas $\alpha$-elements are produced predominantly through Type~II SNe.
+Because these SNe occur on different timescales (10s of Myr after star formation for Type~II, as compared to 100s of Myr to Gyrs for Type~Ia), the ratio between $\alpha$-elements and Fe is expected to generally decrease with time.
 
-Broadly speaking, there are three approaches to explaining the bimodality.
+Because of their separate formation channels, the two dimensional plane of \alphaFe{}-\FeH{} has received considerable interest.
+In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
+This bimodal distribution is shown in the upper left panel of Figure~\ref{fig:fig1}.
+
+There are essentially two approaches to explaining the bimodality.
 First, it is a result of internal secular processes that generate the bimodality through radial migration \citep{2009MNRAS.396..203S,2021MNRAS.507.5882S,2023MNRAS.523.3791C} or clump formation \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
+
 Second, the bimodality is generated through gas infall scenarios, either from specific gas accretion episodes from the intergalactic medium \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}, or through a more self-consistent collapse sequence of the circumgalactic medium driven through feedback \citep{2021MNRAS.501.5176K}.
-Third and finally, the bimodality is generated through a merger process, either by enhancing the star formation rate (SFR) of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
-Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
+Third and finally, the bimodality is generated through a merger process, either by enhancing the SFR of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
+The fact that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
 
-In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,Myr$) quiescent period in the Galaxy's history, which has two effects.
-First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia\footnote{These SNe occur on different timescales (10s of Myr after star formation for Type~II, as compared to 100s of Myr to Gyrs for Type~Ia), so if the SFR drops, the number of Type~II SNe drops faster than Type~Ia.}, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
-Second, the lower SFR results in fewer stars forming in the region between the high- and low-$\alpha$ sequences, reducing the occurance of this transitional population in present-day observations.
-This mechanism resembles two-phase infall models that incorporate a temporary halt in star formation \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period in Paper~I is much shorter.
-The combination of these two effects creates the valley between the high- and low-$\alpha$ sequences.
+In \citet{2024arXiv240707985B} we argued for an alternate formation scenario of the bimodality, for which we provide further support in this work.
+In this scenario, the bimodality is formed through a brief quiescent period in the Galaxy's history.
+During this period, which lasted $\sim300\,\Myr$ in that setup, two things happen.
+First, as the chemical evolution of the galaxy proceeds, fewer stars form.
+Second, because the SFR is lower, $\alpha$-element production drops and so the \alphaFe{} of the gas drops as well.
+This is conceptually similar to some variants of the two-phase infall scenarios which allow for a brief halt in the star formation rate \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period is much shorter in \citet{2024arXiv240707985B}.
+The combination of these two effects is what leads to the valley in between the high- and low-$\alpha$ sequences.
 
-In Paper~I, we used idealized simulations of a galaxy merger that triggered the quiescent period.
-However, we argued that the merger aspect of that work was not necessary.
-In this work, we study a subhalo, or galaxy, from the Illustris TNG50 simulation demonstrating this.
-This subhalo of interest (SoI) exhibits the sequence of events presented in Paper~I after a simple post-processing step which increases the \alphaFe{} of old star particles.
-This post-processing is motivated by recent work demonstrating that the star formation efficiency (SFE) of the dense gas present at high-$z$ is too low \citep{2024arXiv240909121H}.
+In that work, we used idealized simulations of a galaxy merger that triggered a starburst which preceded the quiescent period.
+However, we argued that the merger aspect of that work was not necessary, but rather the quiescence.
+In this work, we study a subhalo from the Illustris TNG50 simulation which demonstrates this.
+This subhalo of interest (SoI) exhibits the sequence of events presented in \citet{2024arXiv240707985B} after a simple post-processing step which enhances the \alphaFe{} of old star particles.
 The SoI undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
 However, instead of being preceded by a merger, the quenching is preceded by apparent bar-induced AGN activity.
-Therefore, this work serves as a verification that the scenario in Paper~I is possible in cosmological simulations and does not require a merger.
+Therefore, this work serves as a verification that the scenario in \citet{2024arXiv240707985B} is possible in cosmological simulations and can occur in non-merger scenarios.
 
@@
 \subsection{IllustrisTNG Sample}\label{ssec:tng}
-We use Illustris TNG50 \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$).
+We have made use of the Illustris TNG50 simulation \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$).
 It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG model \citep{2013MNRAS.436.3031V, 2017MNRAS.465.3291W, 2018MNRAS.473.4077P}.
-This model includes several subgrid processes: a wind generation model, chemical enrichment from SNe and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.
+This model includes several subgrid processes: a wind generation model, chemical enrichment from supernovae and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.
 
-One piece of the TNG model of note for this work is the black hole (BH) accretion and feedback method \citep{2017MNRAS.465.3291W}.
-The BH accretion rate ($\dot{M}_{\textrm{BH}}$) is computed using the local structure of the gas phase with the Bondi-Hoyle-Lyttleton formula \citep{1939PCPS...35..405H,1944MNRAS.104..273B,1952MNRAS.112..195B}, with a maximum of the Eddington accretion rate ($\dot{M}_{\textrm{edd}}$).
+One piece of the TNG model of note for this work is the BH accretion and feedback method \citep{2017MNRAS.465.3291W}.
+The black hole accretion rate ($\dot{M_{\textrm{BH}}}$) is computed using the local structure of the gas phase with the Bondi-Hoyle-Lyttleton formula \citep{1939PCPS...35..405H,1944MNRAS.104..273B,1952MNRAS.112..195B}, with a maximum of the Eddington accretion rate ($\dot{M_{\textrm{edd}}}$).
 The model allows the BH to be either in a kinetic radio-mode or a thermal quasar-mode.
-If the Eddington ratio ($\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$) exceeds a threshold ($M_{\textrm{BH}}$-dependent, but $\sim0.001$--$0.1$), the BH is in the quasar mode and injects a large amount of thermal energy into its surroundings.
+If the Eddington ratio ($\dot{M_{\textrm{BH}}}/\dot{M_{\textrm{edd}}}$) exceeds a threshold ($M_{\textrm{BH}}$-dependent, but $\sim0.001--0.1$), the BH is in the quasar mode and injects a large amount of thermal energy into its surroundings.
 
@@
 The chosen mass range is broadly consistent with the expected mass of the Milky Way at this redshift \citep{2013ApJ...771L..35V}.
-We choose to make our selection of galaxies at $z=1.5$ instead of at lower redshift because we wish to capture the \textit{formation} of multimodal structure.
-Mergers at lower redshift contribute very little to the Milky Way's disk stars \citep[e.g.,][]{2016ARA&A..54..529B}, and would act as a contaminant in our sample.
+We chose to make our selection of galaxies at $z=1.5$ instead of at lower redshift because we wished to capture the \textit{formation} of any multimodal structure.
+We did not want contamination by mergers at lower redshift which we know contribute very little to the Milky Way's disk stars \citep[e.g.,][]{2016ARA&A..54..529B}.
 
-We examine the abundance distribution in the \MgFe{}-\FeH{} plane for this sample of subhalos by visual inspection.
-Few subhalos display multimodal structure, and when present, it is much weaker compared to that observed in the Milky Way.
-We then apply a post-processing step to the \MgFe{} of the stars, adding a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ to each star particle, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$), and $t_{\textrm{form}}$ is the formation time of the star particle.
-After this adjustment, which we justify in Section~\ref{ssec:sfe} based on TNG underpredicting the SFE of dense gas, we observe that the abundance structure becomes significantly more pronounced.
+We examined the abundance distribution in the \MgFe{}-\FeH{} plane of this sample of subhalos by eye.
+Not many subhalos had multimodal structure, and any structure that was present was relatively weak compared to that observed in the Milky Way.
+We then applied a post-processing to the \MgFe{} of stars by adding to each star particle a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time of each star particle.
+With this post-processing, we found that much more structure was generally present.
 
@@
 
-We select subhalo 172175 (the ID at snapshot 40) for its resemblance to the Milky Way.
+We selected subhalo 172175 (the ID at snapshot 40) for its particular resemblance to the Milky Way.
 We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
 We refer to this subhalo as our subhalo of interest (SoI).
-\red{Add some morphological details of gal here}
+
+\subsection{Bar Catalog}\label{ssec:barcat}
+In order to study the evolution of the morphology of our SoI, we make use of the \citet{2022MNRAS.515.1524Z} catalog.
+They provide a decomposition of all galaxies with at least $10^4$ star particles, as well as an estimate of the bar strength.
+This taken to be the maximum of the second Fourier mode ($A_{2,\textrm{max}}$) within the bar region (not including spiral arms).
 
@@
 First, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}.
-We make the same selection cuts as in Section~2.4 of Paper I.
-These criteria are meant to select giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's.
+We make the same selection cuts as in \citet{2024arXiv240707985B}, described in their Section~2.4.
+These are meant to select only giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's.
 This results in a sample of 54,777 stars.
@@
 We then further considered a dataset of stellar ages from the APOKASC2 catalog \citep{2018ApJS..239...32P}.
-This catalog uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
+This uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
 Using only stars with $25\%$ age uncertainties (taken as the maximum of the upper and lower uncertainty), we cross-match this catalog to our larger sample from ASPCAP which results in a sample of 1201 stars.
@@
 \subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
-James inserts his section
+One-zone galactic chemical evolution (GCE) models describe enrichment in an idealized gas reservoir in which newly synthesized metals mix instantaneously (see e.g.
+the reviews by \citealt{Tinsley1980} and \citealt{Matteucci2021}).
+Our parameter choices in this paper are based on the models in \citet{2022arXiv220402989C}.
+While they were interested in bursts of star formation at the transition between the stellar halo and thick disk formation epochs, we focus on smooth evolutionary histories in this paper.
+We integrate these models numerically using the publicly available {\tt Versatile Integrator for Chemical Evolution} ({\tt VICE}; \citealt{Johnson2020}).
+
+The quantity that is of particular importance to our results is the star formation efficiency (SFE) timescale $\tau_\star$:
+\begin{equation}
+\tau_\star \equiv \frac{M_{\textrm{gas}}}{\dot{M}_{\textrm{star}}},
+\end{equation}
+where $M_{\textrm{gas}}$ and $\dot{M}_{\textrm{star}}$ are the ISM mass and star formation rate, respectively.
+This timescale can be equivalently expressed as the ratio of the corresponding surface densities $\Sigma_{\textrm{gas}}$ and $\dot{\Sigma}_{\textrm{star}}$.
+$\tau_\star$ is the inverse of the SFE itself, describing the rate of star formation per unit mass in the ISM.
+In principle, $\tau_\star$ should vary with $M_{\textrm{gas}}$ because the observed relation between $\dot{\Sigma}_{\textrm{star}}$ and $\Sigma_{\textrm{gas}}$ is non-linear; classically, $\dot{\Sigma}_{\textrm{star}} \propto \Sigma_{\textrm{gas}}^N$ where $N \approx 1.5$ (e.g.
+\citealt{Schmidt1959, Kennicutt1998}).
+For simplicity, we hold $\tau_\star$ constant in this paper, which corresponds to a linear relation.
+In section 3.5 below, we present models using $\tau_\star = 0.5$, $1$, and $5$ Gyr.
+
+Following \citet{2022arXiv220402989C}, our models assume that there is initially no gas present in the galaxy (i.e.
+$M_{\textrm{gas}} = 0$ at $t = 0$).
+Zero metallicity gas accretes at a constant rate of $\dot{M}_\text{in} = 5\,\Msunyr$.
+The efficiency with which feedback sweeps up ISM material and ejects it to the CGM in an outflow is described by the mass loading factor $\eta \equiv \dot{M}_\text{out} / \dot{M}_\star$.
+We use $\eta = 2$ throughout this paper (i.e.
+for every solar mass of stars formed, $2\,\Msun$ of ISM gas is lost to an outflow).
+These parameter choices lead to an SFH that initially rises from zero and approaches a constant value of $\sim1.9\,\Msunyr$.
+With these choices, the predicted abundance evolution is insensitive to the overall normalization of the accretion and star formation histories, since a larger accretion rate forms more stars and metals but simultaneously introduces more H into the ISM.
+
+We use the solar abundances of Fe and Mg from \citet{Magg2022} with an additional 0.04 dex to account for the effects of diffusion and gravitational settling (\citealt{Turcotte1998}; i.e.
+$\{Z_{\text{Fe},\odot}, Z_{\text{Mg},\odot}\} = \{13.7, 6.71\} \times 10^{-4}$).
+We adopt SN yields of Fe and Mg based on \citeauthor{Weinberg2023}'s \citeyearpar{Weinberg2023} recommendations for Type~II SNe:
+\begin{itemize}
+
+	\item $y_\text{Fe}^\text{II} = 4.73 \times 10^{-4}$
+
+	\item $y_\text{Mg}^\text{II} = 6.52 \times 10^{-4}$
+
+	\item $y_\text{Fe}^\text{Ia} = 12 \times 10^{-4}$
+
+	\item $y_\text{Mg}^\text{Ia} = 0$,
+
+\end{itemize}
+where the subscripts and superscripts denote the element and SN type, respectively.
+We select this value of $y_\text{Fe}^\text{Ia}$ as it corresponds to $\sim30\%$ ($\sim70\%$) of Fe arising from Type~II (Ia) SNe at solar \FeH{}.
+These yields are population-averaged, meaning that they quantify the amount of metal production per unit mass of star formation under the given enrichment channel (e.g.
+a hypothetical $1000\,\Msun$ stellar population would produce a total of $0.652\,\Msun$ of Mg through Type~II SNe).
+{\tt VICE} models Type~II SNe as exploding instantaneously following an episode of star formation.
+For Type~Ia SNe, we assume that metals are produced according to the empirically motivated $t^{-1.1}$ power-law based volumetric SN rates as a function of redshift and the cosmic SFH \citep[e.g.][]{Maoz2012}.
+
+We use the yields recommended by \citet{Weinberg2023} because they are based on an empirical determination of the mean $^{56}$Ni yield from Type~II SNe by \citet{Rodriguez2021, Rodriguez2023} applied to multi-element abundance distributions in the Milky Way.
+Theoretically predicted SN yields \citep[e.g.][]{Seitenzahl2013, Sukhbold2016, Limongi2018, Gronow2021} are subject to substantial theoretical uncertainties.
+Empirical considerations regarding yields are often necessary for GCE models to make tenable predictions (see also discussion in \citealt{Palla2022}).
+
+With the exception of our SN yields, we find through experimentation that the decline in \MgFe{} with time is most significantly sensitive to the value of $\tau_\star$.
+We therefore expect its connection to the decline in \MgFe{} on which this paper is focused to be robust.
+We refer to \citet{Johnson2020} and \citet{2022arXiv220402989C} for further discussion of these GCE models.
 
@@
 Only faint structure is seen in the lowest bin (blue, $-0.75\,\dex$).
-The right column shows the same subhalo but after increasing the \MgFe{} value of star particles formed before $z=1.5$ linearly with formation time (with a slope of $0.1\dex/\Gyr$).
+The right column shows the same subhalo but after increasing the \MgFe{} value of star particles formed before $z=1.5$ linearly with formation time (specifically by incrementing \MgFe{} by $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ if $t_{\textrm{form}} < t_{1.5}$, where $t_{1.5}$ is the age of the universe at $z=1.5$).
 A clear bimodality is shown in these panels which, unlike in the Milky Way, is present at all metallicities.}
@@
 The main result of our paper is given in Figure~\ref{fig:fig1}.
-Here, we compare the abundance plane in the Milky Way (left column) to that of our subhalo of interest (middle and right columns).
+Here, we compare the abundance plane in the Milky Way (left column) to that in our subhalo of interest (middle and right columns).
 The upper panels show the 2D distribution in the space of \MgFe{}-\FeH{}.
@@
 
-The colored vertical regions are indicated at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations.
+The colored vertical lines are indicated at $\FeH=-0.75$, $-0.5$, $-0.25$, and $0\,\dex$ in the Milky Way, and at bins $0.25\,\dex$ higher in the simulations.
 The lower panels show 1D histograms of \MgFe{} in bins centered on these values.
 The bins for the Milky Way/simulations have width $0.2$/$0.05\,\dex$.
+The \MgFe{} values are given offsets so their medians are at zero.
 The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities.
@@
 We use age instead of formation time in order to better facilitate comparisons to observations.
-These panels show 2D histograms, with a logarithmic colormap normalized to the maximum of the plot.
-To prevent overlap, the values of \MgFe{} are given offsets of $0$, $-0.5$, $-1$, and $-1.5$, in order of increasing \FeH{}.
+These panels are true 2D histograms, with a logarithmic colormap normalized to the maximum of the plot.
+The values of \MgFe{} are offset so their medians are at zero.
 
-In the SoI, there is an age gap at $sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
+There is a gap in the ages that occurs at an age of $10.6\,\Gyr$, which we mark with a vertical dashed line.
 Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
-In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly reduced \MgFe{} than stars which form a short time later.
+In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly depressed \MgFe{} than stars which form a short time later.
 
-In the lower row, the left panel shows data from the Milky Way, while the middle and right panels correspond to the fiducial and $\alpha$-enhanced SoI, respectively.
-For the simulations, we introduce Gaussian errors of $15\%$ in age and $0.01,\dex$ in \MgFe{}.
-These error values align with the observational uncertainties from the APOKASC2 and APOGEE datasets, which the Milky Way panel (lower left) is based on (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
-While the error in \MgFe{} is relatively minor, the age error ($1.5\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
-Despite this, the $\alpha$-enhanced SoI still shows two distinct populations, although their ages now overlap more significantly.
+In the lower panels we plot to the left data from the Milky Way and to the middle and right from the fiducial and $\alpha$-enhanced SoI, respectively.
+For the simulations, we add $15\%$ age and $0.01\,\dex$ \MgFe{} Gaussian errors.
+These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:obs_err} for plots of the observational errors).
+The error in \MgFe{} is not signficant, but the age error, which is $1.5\,\Gyr$ at $10\,\Gyr$, smears out the distribution before and after the dashed line.
+The $\alpha$-enhanced SoI still shows two separate populations in this plot, but they now significantly overlap in age.
 
-Interestingly, the Milky Way distribution (lower left panel) exhibits similarities to the $\alpha$-enhanced SoI.
-Specifically, in the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively), there appear to be two populations that overlap in age but remain distinct in \MgFe{}.
-These are the bins where the bimodality is most pronounced (as seen in the upper left panel of Figure~\ref{fig:fig1}).
+The Milky Way distribution (lower left panel) bears some resemblance to the $\alpha$-enhanced SoI.
+In particular, the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively) show what appears to be two populations overlapping in age but nonetheless separated in \MgFe{}.
+These are the bins at which the bimodality is strongest (upper left panel of Figure~\ref{fig:fig1}).
 
 \subsection{Evolutionary History}\label{ssec:evol}
+
 \begin{figure}
@@
   \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200.pdf}
-  \caption{\textbf{The evolutionary history of our subhalo of interest.} The left column shows the SFH, BH accretion rate, and virial mass ($M_{200}$) over the entire time span, while the right column zooms in on the period from $t\sim2\,\Gyr$ to $t\sim5\,\Gyr$.
-The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$, corresponding to the separation between the high- and low-$\alpha$ sequences (as shown in Figure~\ref{fig:alpha}).
-The middle panel shows the BH accretion rate as a fraction of the Eddington limit, and the lower panel shows the virial mass, representing the mass enclosed within a radius where the density is $200\times$ the mean cosmic density.}
+  \caption{\textbf{The evolutionary history of our subhalo of interest.} The upper panel shows the SFH of our subhalo.
+This SFH is computed using the SFR within twice the stellar half-mass radius in our SoI's main progenitors.
+In this and all subsequent panels we show a vertical dashed line at the same position as in Figure~\ref{fig:alpha} ($\sim3.2\,\Gyr$), which delineates the separation between the high- and low-$\alpha$ sequences.
+The gap in ages is naturally associated with a gap in the SFH located at the dashed line.
+The middle panel shows the BH accretion rate as a fraction of the maximum (Eddington) accretion rate across time.
+The accretion rate is high early on, but then drops.
+The gap in ages (dashed line) is coincident with a local peak in the BH accretion rate.
+In the lower panel we show the mass assembly of the halo, given as the mass within the radius that encloses $200\times$ the mean density of the universe.
+In this plot mergers are shown as sudden increases in $M_{200}$.
+Mergers at very early times when the halo is signifcantly less massive than its $z=0$ mass are not shown, but one can see that no clear merger is associated with the gap in stellar ages.
+Two mergers occur later on at $t\sim10$ and $\sim12\,\Gyr$.}
   \label{fig:history}
@@
 
-To understand the key events driving the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of several properties of the subhalo in Figure~\ref{fig:history}.
-The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$ from the high- to low-$\alpha$ sequences, as in Figure~\ref{fig:alpha}.
-The upper panel in the left column shows the the SFR (computed for all gas cells in the subhalo).
-There are two peaks at $t\sim2.5\,\Gyr$ and $t\sim4.5\,\Gyr$ with maximum values of $50\,\Msun/\textrm{yr}$ and $30\,\Msun/\textrm{yr}$, respectively.
-Around the high- to low-$\alpha$ transition, there is a dip in the SFR, which drops by an order of magnitude to about $3\,\Msun/\textrm{yr}$.
-The right panel zooms in on the period between $t=2\,\Gyr$ and $5\,\Gyr$, where we observe a sharp recovery in the SFR following the quiescent phase.
-In a single snapshot (spanning roughly 150 Myr), the SFR increases from about $3\,\Msun/\textrm{yr}$ to $10\,\Msun/\textrm{yr}$.
+In an effort towards understanding the events in our SoI's history that led to the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of some of its key quantities.
+In the upper panel of Figure~\ref{fig:history}, we show the SFH of our galaxy with the same dashed line as in Figure~\ref{fig:alpha} (at an age of $10.6\,\Gyr$ in that plot is at a time of $\sim3.2\,\Gyr$ here).
+This SFH is computed using the SFR within twice the stellar half-mass radius in our SoI's main progenitors.
+We see two peaks in the SFH at $t\sim2.5$ and $\sim4.5\,\Gyr$ of an amplitude of about $50$ and $30\,\Msunyr$.
+The dashed line corresponds to a relative drop in the SFR, down to about $3\,\Msunyr$ before quickly recovering.
 
-The middle panels track the accretion rate of the central BH as a fraction of the Eddington rate.
-Early in the subhalo's history ($t<2\,\Gyr$), the BH experiences high accretion, which steadily declines until $t\sim5\,\Gyr$.
-Around $t\sim3.2\,\Gyr$, the BH accretion rate peaks again, reaching approximately $30\%$ of the Eddington limit, placing the BH in quasar mode and injecting significant thermal energy into the galaxy's center.
-The middle right panel shows the period between $t=2$ and $5\,\Gyr$.
+The middle panel shows the accretion rate of the central black hole as a fraction of the maximum (Eddington) accretion rate.
+Early in its history ($t<2\,\Gyr$), the subhalo experiences high accretion rates.
+The accretion rate then steadily declines until $t\sim5\,\Gyr$ at which point it fails to show on this linear plot.
+However, at the dashed line ($\sim3.2\,\Gyr$) there is a localized peak in the accretion rate, maxing out at about $30\%$ Eddington.
+This places the BH firmly in the thermal quasar-mode, and allows it to inject large amounts of thermal energy into the center of the galaxy.
 
-The lower panel illustrates the growth of the subhalo's virial mass ($M_{200}$).
-Early on ($t<4\,\Gyr$), $M_{200}$ increases roughly linearly, reaching about $2 \times 10^{12}\,\Msun$.
-After this, the mass remains relatively stable until jumps occur around $t\sim10$ and $\sim12\,\Gyr$, indicative of mergers.
-There are no mergers related to the earlier quiescent period around $t\sim3.2\,\Gyr$, as no major mass jumps are observed during this time.
-The lower right panel shows the period between $t=2$ and $5\,\Gyr$.
+The lower panel shows the virial mass of the subhalo, as measured by $M_{200}$ -- the mass within the radius that encloses a region of density $200\times$ the mean density of the universe.
+Early on at $t<4\,\Gyr$ the virial mass grows roughly linearly up to $\sim2\times10^{12}\,\Msun$.
+After that, the virial mass remains roughly constant until sharp increases at $t\sim10$ and $\sim12\,\Gyr$.
+The transition in the virial mass from linear to constant at $t\sim4\,\Gyr$ is followed $1\,\Gyr$ later by a sudden drop in the SFR and BH accretion rate.
 
-\subsection{Sequence of Events}\label{ssec:sequence_of_events}
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200_zoomed.pdf}
+  \caption{\textbf{At the transition from the high- to low-$\alpha$ sequence, a bar forms and strengthens, AGN activity is enhanced, and star formation is supressed.} The evolutionary history of our SoI near the transition between the high- and low-$\alpha$ sequence, which is indicated as a vertical dashed line at an age of $10.6\,\Gyr$ ($t\sim3.2\,\Gyr$).
+The blue line indicates the SFR, which drops from a peak of $\sim54\,\Msunyr$ to $\sim3.6\,\Msunyr$.
+The minimum is very close to the transition.
+The drop in SFR is coincident with a rise in the AGN accretion rate (orange) as well as a rise in the strength of the bar (red).}
+  \label{fig:history_zoom}
+\end{figure}
+
+We show the evolution of the SoI in greater detail at the transition between the high- and low-$\alpha$ sequences in Figure~\ref{fig:history_zoom}.
+As in Figure~\ref{fig:history}, we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$ in the bar region, in red.
+From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54$ to $3.6\,\Msunyr$.
+The minimum in the SFR is nearly coincident with the transition line.
+
+We can see more clearly here that the BH accretion rate (red), in units of the Eddington accretion rate, increases from a value of $\sim0.08$ at $\sim2.8\,\Gyr$ to a maximum of $\sim0.3$ at $\sim3.1\,\Gyr$, right before the transition.
+This rise in the AGN accretion rate is preceded by a strengthening of the bar, which rises from an $A_2$ of $\sim0.1$ at $t\sim2.4\,\Gyr$ to an $A_2$ of $\sim0.5$ at $\sim3.1\,\Gyr$, the time of the peak BH accretion rate.
+
+\subsection{Images}\label{ssec:images}
 \begin{figure*}
   \centering
-  \includegraphics[width=\textwidth]{fig/alyssa.pdf}
-  \caption{Surface density projections of gas (top row) and star particles (middle row) in our SoI across snapshots at different times during the high- to low-$\alpha$ transition.
-Below the projections is a plot showing the SFR, BH accretion rate (in units of $\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$), and bar strength ($A_2/A_0$ for $R<2$ kpc).
-Time ranges from $\sim2.4\,\textrm{Gyr}$ to $\sim3.6\,\textrm{Gyr}$, corresponding to redshifts from $z\sim2.7$ to $z\sim1.8$.
-A sequence of events in which the bar strengthens, BH accretion increases, and SFR declines is seen, and is described more fully in the text.}
-  \label{fig:seq}
+  \includegraphics[width=\textwidth]{fig/images_star.pdf}
+  \caption{Surface density projections of star particles in our SoI at the transition between the high- and low-$\alpha$ sequences.
+Each panel indicates subsequent snapshots ranging from snapshot 23 ($z\sim3.5$) to snapshot 36 ($z\sim1.7$), as well as snapshot 99 ($z=0$) in the lower right.
+Several key numbers are shown in the corners of each panel, clockwise from the top left: SFR, time, bar strength ($A_{2,\textrm{max}}$), and BH accretion rate.
+A guide is given in the top left subpanel.
+At the center-bottom of each panel, we indicate panels which occur before the transition ($\sim3.2\,\Gyr$) as high-$\alpha$ and panels which occur after as low-$\alpha$.}
+  \label{fig:images_star}
 \end{figure*}
 
-Figure~\ref{fig:seq} presents surface density projections of gas and stars at different stages of the high- to low-$\alpha$ transition.
-The upper panels show gas density, while the middle panels display stellar density.
-Time progresses from $\sim2.4$ to $\sim3.6\,\textrm{Gyr}$, corresponding to redshifts ranging from $z\sim2.7$ to $z\sim1.8$.
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{fig/images_gas.pdf}
+  \caption{As in Figure~\ref{fig:images_star}, but showing the surface density projections of gas in our SoI at the transition between the high- and low-$\alpha$ sequences.
+Each panel indicates subsequent snapshots ranging from snapshot 23 ($z\sim3.5$) to snapshot 36 ($z\sim1.7$), as well as snapshot 99 ($z=0$) in the lower right.
+Several key numbers are shown in the corners of each panel, clockwise from the top left: SFR, time, gas fraction, and BH accretion rate.
+A guide is given in the top left subpanel.
+At the center-bottom of each panel, we indicate panels which occur before the transition ($\sim3.2\,\Gyr$) as high-$\alpha$ and panels which occur after as low-$\alpha$.}
+  \label{fig:images_gas}
+\end{figure*}
 
-This Figure shows the following sequence of events:
-\begin{enumerate}
-    \item Bar forms: A steady increase in the bar strength, as indicated by $A_2/A_0$ for star particles with $R<2\,\kpc$, from $\sim0.05$ to $0.4$ starting around $2.8\,\textrm{Gyr}$.
-This rise is accompanied by the appearance of elongated features in the gas and stars consistent with a bar.
-    \item BH accretion increases: Following the increase in bar strength by about a snapshot ($\sim150\,\Myr$ here), the BH accretion rate ($\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$) shows a significant spike, rising from a minimum of $\sim0.08$ at $t=2.84\,\Gyr$ to a maximum of $\sim0.29$ at $t=3.13\,\Gyr$ for one snapshot.
-    \item SFR declines: The SFR declines starting from a maximum of $54.3\,\Msunyr$ at $t=2.84\,\Gyr$ down to $3.6\,\Msunyr$ at $t=3.28\,\Gyr$.
-In the next snapshot at $t=3.45\,\Gyr$ the SFR recovers to $12.2\,\Msunyr$ and remains above
+In order to better conceptualize the evolution of the SoI at the high- to low-$\alpha$ transition, we show surface density projections of the stellar (Figure~\ref{fig:images_star}) and gaseous (Figure~\ref{fig:images_gas}) phases of the progenitors of our SoI at various redshifts.
+In addition to the final, $z=0$, snapshot in the lower right, we show panels for snapshots 23 to 36 in which $z$ ranges from $\sim3.5$ to $\sim1.7$ and the cosmic time from $\sim1.81$ to $\sim3.74\,\Gyr$.
+Projections are made on a $256\times256$ grid of a $25\,\kpc$ by $25\,\kpc$ square.
+All star particles/gas cells within ten times the stellar half-mass radius are used, and a simple nearest neighbor assignment of mass to each cell is used.
+Colors range logarithmically from $5\times10^{-4}$ to $0.5$ in native units ($10^{10} h M_{\odot} \ckpc^{-2}$), and only resolution elements within 10 times the stellar half-mass radius of the center of the subhalo are used.
 
-    After the increase in BH accretion, the star formation rate (SFR) begins to decline.
-The decrease in SFR steadily commences as the BH accretion rate remains elevated.
-By approximately $3.2\,\textrm{Gyr}$, the SFR reaches a more quiescent state at $\sim3\,\Msunyr$.
-After one snapshot, the SFR increases to
-\end{enumerate}
+We also show four relevant statistics in each panel of Figures~\ref{fig:images_star} and \ref{fig:images_gas}.
+For Figure~\ref{fig:images_star}, these are, clockwise from the upper left, the SFR, cosmic time, bar strength, and BH accretion rate.
+They are the same for Figure~\ref{fig:images_gas}, but bar strength is replaced with gas fraction (within twice the stellar half-mass radius).
+The bar strength is missing from several snapshots because the \citet{2022MNRAS.515.1524Z} catalog excludes certain galaxies from being considered barred if they do not pass certain quality cuts.
+These can come from, e.g., flybys or violent buckling events.
+
+A description of the events portrayed in each Figure is given in Section~\ref{ssec:cause_qui}.
 
@@
   \includegraphics[width=\columnwidth]{fig/mgfe_vice.pdf}
-  \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one-zone chemical evolution model, described in Section~\ref{ssec:onezone_met}.
-The evolution for different SFE values of $2$, $1$, and $0.2\,\textrm{Gyr}^{-1}$ are shown in blue, orange, and red, respectively.
-The upper panel shows the evolution of \MgFe{} over $2\,\Gyr$, while the lower panel shows the negative of its time derivative.
-Increasing the SFE ($\dot{Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$) leads to a more rapid decline in \MgFe{}.
-At its steepest decline ($t\sim0.5\,\Gyr$), increasing the SFE by an order of magnitude results in a slope nearly twice as steep.
-At later times ($t > 1\,\Gyr$), models with higher SFE reach their steady-state \MgFe{} value more quickly.}
+  \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one zone chemical evolution model, described in Section~\ref{ssec:onezone_met}.
+The upper panel shows the evolution of \MgFe{} over $2\,\Gyr$ while the lower panel shows the negative of its time derivative.
+Decreasing the star formation timescale $\tau_{\star}=M_{\textrm{gas}/\textrm{SFR}}$ leads to a more rapid decline in \MgFe{}.
+At its steepest decline ($t\sim0.5\,\Gyr$), an order of magnitude decrease in $\tau_{\star}$ leads to a slope nearly a factor of $2$ larger.
+At later times ($t>1\,\Gyr$), the models with smaller $\tau_{\star}$ reach their steady-state \MgFe{} value more quickly.}
   \label{fig:vice}
@@
 
-In Figure~\ref{fig:fig1}, we showed that a time-linear $\alpha$-enhancement of older stars (formed before $z=1.5$) leads to the emergence of a pronounced chemical bimodality.
-This $\alpha$-enhancement corresponds to a more rapid decline in \alphaFe{} over time at high redshifts.
-Figure~\ref{fig:vice} demonstrates that having too low SFE at high densities is a plausible explanation for why such a steep decline in \alphaFe{} might not be occuring in the fiducial TNG model.
+We showed in Figure~\ref{fig:fig1} that a time-linear $\alpha$-enhancement of old stars (forming before $z=1.5$) led to the emergence of a strong chemical bimodality.
+This $\alpha$-enhancement is equivalent to saying that \alphaFe{} declines more rapdily with time at high-$z$.
+In Figure~\ref{fig:vice} we demonstrate an argument for why this steeper decline in \alphaFe{} might be absent in TNG.
 
-The upper panel of Figure~\ref{fig:vice} presents the evolution of \MgFe{} in three one-zone chemical evolution models with varying star formation efficiencies (SFE).
-A higher SFE leads to a faster reduction in \MgFe{}.
-In the model with the highest SFE ($2\,\Gyr^{-1}$, blue, where SFE is $\dot{\Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ over $2\,\Gyr$.
-In contrast, the model with the lowest SFE ($0.2\,\Gyr^{-1}$) only reaches $\sim0.2\,\dex$ within the same period.
+We show in the upper panel the evolution of \MgFe{} of three one zone chemical evolution models which vary the star formation (SF) timescale.
+This timescale, $\tau_{\star}$, is the inverse of the SF efficiency.
+A shorter SF timescale leads to a more rapid reduction in \MgFe{}.
+In the shortest timescale model, $\tau_{\star}=0.5\,\Gyr$, \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ in $2\,\Gyr$.
+In comparison, the longest timescale model, $\tau_{\star}=5\,\Gyr$ only drops to $\sim0.2\,\dex$ in the same time.
 
-The lower panel shows the negative time derivative of \MgFe{} (i.e., the rate of decline).
-The model with the highest SFE ($2\,\Gyr^{-1}$, blue) has a peak decline rate of $-0.5\,\dex/\Gyr$, while the model with the lowest SFE ($0.2\,\Gyr^{-1}$) peaks at $-0.25\,\dex/\Gyr$.
-After $1\,\Gyr$, the trend begins to reverse, and the lower-SFE models catch up, though at a much slower rate ($\sim-0.1\,\dex/\Gyr$) compared to their peak.
-
-This analysis illustrates that a higher SFE at early times (high redshift) leads to a faster decrease in \MgFe{}.
-Recent work has suggested that the SFE in such dense regions in TNG may indeed be too low, as discussed in Section~\ref{ssec:sfe}.
+The lower panel shows the negative of the time derivative of \MgFe{}.
+This panel shows the same behavior, with the slope of the $\tau_{\star}=0.5\,\Gyr$ model peaking at $-0.5\,\dex/\Gyr$ compared to the $5\,\Gyr$ model which peaks at $-0.25\,\dex/\Gyr$.
+After $1\,\Gyr$, the trend starts to reverse, with the longer SF timescale models declining more rapidly, though at a much reduced rate ($\sim-0.1\,\dex/\Gyr$) than at the peak.
 
 \section{Discussion}\label{sec:disc}
-In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SoI before and after our $\alpha$-enhancement post-processing procedure.
-It is clear that the TNG SoI is unimodal before the $\alpha$-enhancement and multi-modal afterwards.
+In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SoI before and after the $\alpha$-enhancement.
+It is visibly obvious that the TNG SoI is unimodal before the $\alpha$-enhancement and bimodal afterwards (ignoring the minor mode at high-\MgFe{}).
 Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the SoI?, and (2) what justifies the $\alpha$-enhancement?
@@
 \subsection{Cause of Bimodality}\label{ssec:bim_cause}
-An extensive analysis of our SoI is beyond the scope of this work, but here we argue that the evidence is consistent with the scenario presented in Paper I.
+An extensive analysis of our SoI is beyond the scope of this project, but here we argue that the evidence is consistent with the scenario presented in \citet{2024arXiv240707985B}.
 They presented an idealized simulation resembling the merger between the Milky Way and GSE.
@@
 The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} denotes the transition between the high- and low-$\alpha$ sequences.
-We place it at a lookback time of $10.6\,\Gyr$ or a formation time of $\sim3.2\,\Gyr$.
+We place it at an age of $10.6\,\Gyr$ or a formation time of $\sim3.2\,\Gyr$.
 The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} so their medians are at zero).
-Stars formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
+Stars which formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
 At the line, we see a gap in the $\FeH=-0.5$ and $-0.25$ bins.
@@
 
-During this period of suppressed SF, we argue that the lack of enrichment of Type~II relative to Type~Ia SNe leads to a lower rate of Mg production.
-Therefore, \MgFe{} rapidly declines.
-This, combined with a lack of SF in the first place, leads to a scarcity of star particles in the intermediate region between the high- and low-$\alpha$ sequences.
-A more in-depth explanation is given in Section~4.1 in Paper~I.
+During this period of suppressed SF, we argue that the relative lack of enrichment of Type~II SNe which leads to a lower rate of Mg production.
+This leads to a rapid reduction in \MgFe{}.
+This, combined with a lack of SF in the first place, leads to a scarcity of star particles in the region intermediate between the high- and low-$\alpha$ sequences.
+A more in-depth explanation is given in Section~4.1 in \citet{2024arXiv240707985B}.
 
-In the fiducial TNG distribution, shown in the upper middle panel of Figure~\ref{fig:alpha}, the same general behavior is present.
-However, because the \MgFe{} decline before the quiescent period is slower, star particles which formed before and after this period overlap in the \MgFe{} distribution shown in Figure~\ref{fig:fig1}.
+In the fiducial TNG distribution shown in the upper middle panel of Figure~\ref{fig:alpha}, the same general behavior with respect to the dashed line is present.
+However, because the \MgFe{} decline before the dashed line is not as strong, star particles which formed before and after the dashed line overlap in the \MgFe{} distribution shown in Figure~\ref{fig:fig1}.
 
-It is also worth noting that in both the fiducial and $\alpha$-enhanced SoI show a slight rebound effect in \MgFe{}.
+It is also worth noting that in both the fiducial and $\alpha$-enhanced SoI, there is a sort of rebound effect in \MgFe{}.
 The star particles which form directly after the dashed line have a slightly lower \MgFe{} than stars which form after.
-This was also predicted in Figure~9 of Paper~I, where it was argued that during the period of suppressed star formation, the \alphaFe{} ratio of the star-forming gas drops sharply due to the reduced contribution of Type~II relative to Type~Ia SNe.
+This was seen in Figure~9 of \citet{2024arXiv240707985B}.
+In that work, it was argued that this occurs because, during the period of suppressed SF, the \alphaFe{} of star forming gas plummets since there is no contribution from Type~II SNe.
 Later, the \alphaFe{} of the gas will recover when the SFR also recovers, but there is a brief window when old, low-$\alpha$ stars can form.
-A similar behavior was seen in the one-zone models with bursty SFHs in \citet{2020MNRAS.498.1364J}.
 
@@
 The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models.
-Isolating the cause of the ``incorrect''\footnote{Our case study of a single subhalo, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} \MgFe{} vs time evolution at high-$z$ is not straightforward nor, in our opinion, even possible.
-However, we do offer one reasonable explanation: the SFE at high densities, more present at high-$z$, is too low.
+Isolating the cause of the ``incorrect''\footnote{Our case study of a single galaxy, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} \MgFe{} vs time evolution at high-$z$ is not straightforward nor, in our opinion, even possible.
+However, we do offer one reasonable explanation -- the SFE at high densities, more present at high-$z$, is too low.
 
@@
 The details of our setup is given in Section~\ref{ssec:onezone_met}.
-We vary the SFE of the model ($\dot{Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), and examine the impact on the \MgFe{} ratio as a function of time.
+We vary the SF timescale, $\tau_{\star}=M_{\textrm{gas}}/\textrm{SFR}$, and examine the impact on the \MgFe{} ratio as a function of time.
 We find that shorter SF timescales do lead to a more rapid reduction in \MgFe{}.
-The rate of decrease in \MgFe{}, at its maximum, varies between $\sim-0.25$, $-0.35$, and $-0.5\,\dex/\Gyr$ in the $\textrm{SFE}=0.2$, $1$, and $2\,\Gyr^{-1}$ models, respectively.
-For our post-processing, we assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
-Such a difference is well within the range of \MgFe{} decrease seen in our different $\tau_{\star}$ models, implying a factor of only $\sim2$ in the SFE is needed to reach our post-processing slope.
+The rate of decrease in \MgFe{}, at its maximum, varies from $\sim-0.25\,\dex/\Gyr$ in the $\tau_{\star}=5\,\Gyr$ model to $\sim-0.5\,\dex/\Gyr$ in the $\tau_{\star}=0.5\,\Gyr$ model.
+For our post-processing, assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
+Such a difference is well within the range of \MgFe{} decrease seen in our different $\tau_{\star}$ models.
 
-\citet{2024arXiv240909121H} demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude.
-This is well within our needed factor of $2$ in the SFE (see Figure~\ref{fig:vice}).
-Therefore, \MgFe{} should decline more rapidly with a different feedback model (or future iteration of the TNG model) that leads to a higher SFE at high densities.
+S.
+Hassan et al.
+(in preparation) demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude.
+This is well within our needed factor of $2$ in $\tau_{\star}$.
+Therefore, our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified.
+An intuitive understanding of the impact the decline in \alphaFe{} vs time has is that, when \alphaFe{} declines rapidly, it is a better estimator of age.
+When it is a better estimator of age, events which are separated temporally become better separated in the abundance plane.
 
-An intuitive understanding of the impact the decline in \alphaFe{} vs time has is that, when \alphaFe{} declines rapidly, it is a better estimator of age.
-When \alphaFe{} is a better estimator of age, events which are separated temporally become better separated in the abundance plane.
-
-\subsection{Direct Comparison to Observations}\label{ssec:compare_obs}
+\subsection{Comparison to Observations}\label{ssec:compare_obs}
 The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC2 catalog.
@@
 \subsection{Cause of Quiescence}\label{ssec:cause_qui}
+% We show the evolution of the SoI in greater detail at the transition between the high- and low-$\alpha$ sequences in Figure~\ref{fig:history_zoom}.
+As in Figure~\ref{fig:history} we indicate the SFR (blue) and black hole accretion rate (orange), but we also include the strength of the bar, taken to be the maximum value of $A_2$, in red.
+From $\sim2.8\,\Gyr$ to $\sim3.2\,\Gyr$, the SFR drops from $\sim54\,\Msunyr$ to $3.6\,\Msunyr$.
+The minimum in the SFR is nearly coincident with the transition line.
+
+% We can see more clearly here that the BH accretion rate (red), in units of the Eddington accretion rate, increases from a value of $\sim0.08$ at $\sim2.8\,\Gyr$ to a maximum of $\sim0.3$ at $\sim3.1\,\Gyr$, right before the transition.
+This rise in the AGN accretion rate is preceded by a strengthening of the bar, which rises from an $A_2$ of $\sim0.1$ at $t\sim2.4\,\Gyr$ to an $A_2$ of $\sim0.5$ at $\sim3.1\,\Gyr$, the time of the peak BH accretion rate.
+
 It is natural to question why the minimum in the SFR occurs.
-In Paper~I, AGN activity from a merger was the suspected cause.
+In \citet{2024arXiv240707985B}, AGN activity from a merger was the suspected cause.
 Here, we can see that there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
@@
 
-In Figure~\ref{fig:seq}, we combine a visual inspection of the gas (upper row) and stellar (middle row) surface densities with the evolution of three key quantites (lower plot): SFR, BH accretion rate, and bar strength in blue, orange, and red, respectively.
-These are shown for nine snapshots, from snapshot 27 to 35, corresponding to redshift $2.73$ to $1.82$ or cosmic time from $2.38\,\Gyr$ to $3.59\,\Gyr$.
-A vertical dashed line is included in the lower panel separating the formation of the low- and high-$\alpha$ sequence at an age of $10.6\,\Gyr$ (cosmic time $\sim3.2\,\Gyr$), as in Figures~\ref{fig:alpha} and \ref{fig:history}.
+In Figure~\ref{fig:history_zoom}, we take a closer view of the evolution of our SoI at the transition between the high- and low-$\alpha$ sequence, which we denote with the same line at an age of $10.6\,\Gyr$ ($t\sim3.2\,\Gyr$) as before.
+Here, we see that indeed the drop in the SFR ( $\sim3.6\,\Msunyr$ at $t\sim3.3\,\Gyr$) reaches a minimum one snapshot after the maximum in the BH accretion rate ($\sim0.3\times\dot{M_{\textrm{edd}}}$ at $t\sim3.1\,\Gyr$).
 
-As described in Section~\ref{ssec:sequence_of_events}, the following sequence of events occurs: the bar strengthens and then the BH accretion rate spikes, all while the SFR of the galaxy declines.
-This is suggestive of the following causal sequence:
+The gaseous surface density images in Figure~\ref{fig:images_gas} are helpful to understand this moment in the SoI's history.
+The third row, from $t=2.84$ to $3.28\,\Gyr$ shows this moment, with the rightmost $t=3.28\,\Gyr$ marking the transition from high- to low-$\alpha$ formation.
+The gas fraction (bottom right number) quickly drops from $25\%$ to $3\%$, accompanied by not only a high SFR ($54.3\,\Msunyr$ at maximum) but also an increasing BH accretion rate.
+
+This increasing BH accretion rate is also preceded by the formation of a stellar bar at the center of the galaxy as seen in Figure~\ref{fig:images_star}.\footnote{The bar is already at a strength of $\Atmax\sim0.1$ before, so it either forms or strengthens depending on one's interpretation.
+We choose the former.} Starting from $t=2.38\,\Gyr$, the bar strength grows from $\Atmax=0.1$ to $0.5$ at $t=3.13\,\Gyr$, the peak of the BH accretion rate.
+Note that the bar strength considers only the region where the phase of the second Fourier mode is constant, and so spiral structure as seen in, e.g., the $t=2.38\,\Gyr$ snapshot is not eligible for \Atmax{}.
+
+The scenario implied by all the available evidence is that: 
 \begin{enumerate}
@@
   \item triggers a high BH accretion rate and quasar-mode thermal feedback, which
-  \item clears gas out of the galaxy leading to quiescence.
+  \item clears gas out of the galaxy.
 \end{enumerate}
-This quiescent period then leads to the bimodality, as discussed in Section~\ref{ssec:bim_cause}.
-It is not possible to prove the causality of this sequence of events because of the sparse snapshot spacing in TNG50, and so this is left to future work.
-
-However, there is a significant body of theoretical and observational work in support of this picture.
-Bars and other non-axisymmetric features have long been argued to funnel gas into the centers of galaxies on theoretical grounds \citep{1989Natur.338...45S,2010MNRAS.407.1529H}.In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.
-Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
-
-Since barred galaxies preferentially host AGN, we therefore predict that barred galaxies would preferentially host $\alpha$-bimodalities.
-The GECKOS survey, which aims to constrain the $\alpha$-bimodality of edge-on galaxies using integral field spectroscopy at different altitudes, could test this \citep{2024IAUS..377...27V}.
-On the other hand, the strength of a bar is not associated with the strength of the host AGN \citep[e.g.]{2022A&A...661A.105S}.
-So, it is not clear that bimodalities would be associated with bar strength.
+This picture is supported by work showing that in simulations bars should be able to fuel AGN \citep{1990Natur.345..679S,2010MNRAS.407.1529H}, and that barred galaxies preferentially host AGN \citep{2022A&A...661A.105S}.
+At high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
 
@@
 The depletion time ($M_{\textrm{gas}}/\textrm{SFR}$) at the $t=2.84\,\Gyr$ snapshot is $204\,\Myr$, shorter than the time it takes for the SFR to reach its minimum.
-This implies the possibility of starvation as a quenching mechanism.
-However, the average depletion time in the preceding 5 snapshots (which are each $\sim150\,\Myr$ apart) is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its CGM.
-A definitive account, difficult with the current simulation outputs because of its sparse snapshot spacing, requires further work.
+However, this has to be balanced by the fact that the depletion time is already short at this redshift.
+The average depletion time in the preceding 5 snapshots is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its CGM.
+A definitive account, difficult with the current simulation because of its sparse snapshot spacing, requires further work.
+
+% \subsection{Full Sample}\label{ssec:fullsamp}
 
@@
 After applying a post-processing step that increased the \MgFe{} of star particles formed before $z=1.5$, this subhalo hosts a strong bimodality in the plane of \MgFe{} and \FeH{}, shown in Figure~\ref{fig:fig1}.
-This post-processing is justified by arguing that the SFE of dense gas is too low in TNG \citep[][see discussion in Section~\ref{ssec:sfe}]{2024arXiv240909121H}.
+This post-processing is justified by arguing that the SFE of dense gas is too low in TNG (Section~\ref{ssec:sfe}).
 
@@
 
-This bimodality can be traced to an event that occurred at an age of $10.6\,\Gyr$, or formation time of $\sim3.2\,\Gyr$ ($z\sim2$).
-Shown as a vertical dashed line in Figure~\ref{fig:alpha}, star particles that form before this time are at high-\MgFe{}, while star particles that form after are at low-\MgFe{}.
-This time is associated with a global reduction in the SFR (Figure~\ref{fig:history}), which appears to be related to AGN activity induced by the formation of a bar (Figure~\ref{fig:seq}).
+The reduction in the SFR has two effects.
+First, a lower production of Mg is the natural result of a lack of Type~II SNe.
+Second, the lack of SF means that stars at \MgFe{} intermediate between the high- and low-$\alpha$ sequences never form.
+This is the same argument that was first presented in \citet{2024arXiv240707985B}.
+When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the Milky Way's abundance-age distribution (Section~\ref{ssec:compare_obs}).
 
-We argue that the reduction in the SFR has two effects which lead to the $\alpha$-bimodality.
-First, a lower production of Mg relative to Fe is the natural result of a lack of Type~II relative to Type~Ia SNe.
-The latter remain high due to their longer timescales, expediting a drop in \MgFe{}.
-Second, the lack of SF means that stars at \MgFe{} intermediate between the high- and low-$\alpha$ sequences never form.
-This argument is the same as presented in Paper~I and is consistent with the one-zone chemical evolution models of \citet{2020MNRAS.498.1364J}.
-When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the distribution observed in the Milky Way (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).
-
-This work adds further support to a scenario in which a quiescent period in the Milky Way's past is a plausible explanation for the Milky Way's abundance bimodality.
-We argued in Paper~I that the GSE merger could trigger this period.
-In this work we have argued that the formation of the Milky Way's bar could be responsible.
-In external galaxies, we predict that the presence of a bar is correlated with the presence of an $\alpha$-bimodality.
+While a strong claim about the cause of the quiescent period is difficult to make, we showed that the formation/strengthening of a bar could be responsible for triggering an episode of AGN activity.
+This work adds further support that the argument made in \citet{2024arXiv240707985B} is a plausible explanation for the Milky Way's abundance bimodality.
 

### 2024-10-07 paper/ms.tex

--- 2024-10-07 paper/ms.tex
@@
 \subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
-James inserts his section
+One-zone galactic chemical evolution (GCE) models describe enrichment in an idealized gas reservoir in which newly synthesized metals mix instantaneously (see e.g.
+the reviews by \citealt{Tinsley1980} and \citealt{Matteucci2021}).
+Our parameter choices in this paper are based on the models in \citet{2022arXiv220402989C}.
+While they were interested in bursts of star formation at the transition between the stellar halo and thick disk formation epochs, we focus on smooth evolutionary histories in this paper.
+We integrate these models numerically using the publicly available {\tt Versatile Integrator for Chemical Evolution} ({\tt VICE}; \citealt{2020MNRAS.498.1364J}).
+
+The quantity that is of particular importance to our results is the star formation efficiency (SFE) timescale $\tau_\star$:
+\begin{equation}
+\tau_\star \equiv \frac{M_{\textrm{gas}}}{\dot{M}_{\textrm{star}}},
+\end{equation}
+where $M_{\textrm{gas}}$ and $\dot{M}_{\textrm{star}}$ are the ISM mass and star formation rate, respectively.
+This timescale can be equivalently expressed as the ratio of the corresponding surface densities $\Sigma_{\textrm{gas}}$ and $\dot{\Sigma}_{\textrm{star}}$.
+$\tau_\star$ is the inverse of the SFE itself, describing the rate of star formation per unit mass in the ISM.
+In principle, $\tau_\star$ should vary with $M_{\textrm{gas}}$ because the observed relation between $\dot{\Sigma}_{\textrm{star}}$ and $\Sigma_{\textrm{gas}}$ is non-linear; classically, $\dot{\Sigma}_{\textrm{star}} \propto \Sigma_{\textrm{gas}}^N$ where $N \approx 1.5$ (e.g.
+\citealt{Schmidt1959, Kennicutt1998}).
+For simplicity, we hold $\tau_\star$ constant in this paper, which corresponds to a linear relation.
+In section 3.5 below, we present models using $\tau_\star = 0.5$, $1$, and $5$ Gyr.
+
+Following \citet{2022arXiv220402989C}, our models assume that there is initially no gas present in the galaxy (i.e.
+$M_{\textrm{gas}} = 0$ at $t = 0$).
+Zero metallicity gas accretes at a constant rate of $\dot{M}_\text{in} = 5\,\Msunyr$.
+The efficiency with which feedback sweeps up ISM material and ejects it to the CGM in an outflow is described by the mass loading factor $\eta \equiv \dot{M}_\text{out} / \dot{M}_\star$.
+We use $\eta = 2$ throughout this paper (i.e.
+for every solar mass of stars formed, $2\,\Msun$ of ISM gas is lost to an outflow).
+These parameter choices lead to an SFH that initially rises from zero and approaches a constant value of $\sim1.9\,\Msunyr$.
+With these choices, the predicted abundance evolution is insensitive to the overall normalization of the accretion and star formation histories, since a larger accretion rate forms more stars and metals but simultaneously introduces more H into the ISM.
+
+We use the solar abundances of Fe and Mg from \citet{Magg2022} with an additional 0.04 dex to account for the effects of diffusion and gravitational settling (\citealt{Turcotte1998}; i.e.
+$\{Z_{\text{Fe},\odot}, Z_{\text{Mg},\odot}\} = \{13.7, 6.71\} \times 10^{-4}$).
+We adopt SN yields of Fe and Mg based on \citeauthor{Weinberg2023}'s \citeyearpar{Weinberg2023} recommendations for Type~II SNe:
+\begin{itemize}
+
+	\item $y_\text{Fe}^\text{II} = 4.73 \times 10^{-4}$
+
+	\item $y_\text{Mg}^\text{II} = 6.52 \times 10^{-4}$
+
+	\item $y_\text{Fe}^\text{Ia} = 12 \times 10^{-4}$
+
+	\item $y_\text{Mg}^\text{Ia} = 0$,
+
+\end{itemize}
+where the subscripts and superscripts denote the element and SN type, respectively.
+We select this value of $y_\text{Fe}^\text{Ia}$ as it corresponds to $\sim30\%$ ($\sim70\%$) of Fe arising from Type~II (Ia) SNe at solar \FeH{}.
+These yields are population-averaged, meaning that they quantify the amount of metal production per unit mass of star formation under the given enrichment channel (e.g.
+a hypothetical $1000\,\Msun$ stellar population would produce a total of $0.652\,\Msun$ of Mg through Type~II SNe).
+{\tt VICE} models Type~II SNe as exploding instantaneously following an episode of star formation.
+For Type~Ia SNe, we assume that metals are produced according to the empirically motivated $t^{-1.1}$ power-law based volumetric SN rates as a function of redshift and the cosmic SFH \citep[e.g.][]{Maoz2012}.
+
+We use the yields recommended by \citet{Weinberg2023} because they are based on an empirical determination of the mean $^{56}$Ni yield from Type~II SNe by \citet{Rodriguez2021, Rodriguez2023} applied to multi-element abundance distributions in the Milky Way.
+Theoretically predicted SN yields \citep[e.g.][]{Seitenzahl2013, Sukhbold2016, Limongi2018, Gronow2021} are subject to substantial theoretical uncertainties.
+Empirical considerations regarding yields are often necessary for GCE models to make tenable predictions (see also discussion in \citealt{Palla2022}).
+
+With the exception of our SN yields, we find through experimentation that the decline in \MgFe{} with time is most significantly sensitive to the value of $\tau_\star$.
+We therefore expect its connection to the decline in \MgFe{} on which this paper is focused to be robust.
+We refer to \citet{2020MNRAS.498.1364J} and \citet{2022arXiv220402989C} for further discussion of these GCE models.
 

### 2024-10-09 paper/ms.tex
Fix for another read through

@@
 \newcommand{\rhalf}{\ensuremath{r_{\star,\textrm{half}}}}
+\newcommand{\SFR}{\ensuremath{\textrm{SFR}}}
 
 \newcommand{\red}[1]{\textcolor{red}{#1}}
-% \linespread{1.8}
-
-% \received{March 1, 2021}
-% \revised{April 1, 2021}
-%\accepted{\today}
-
-\shorttitle{Abundance Bimodality in TNG}
-\shortauthors{Beane et al.}
-
-\graphicspath{{./}{fig/}}
 
@@
 \begin{abstract}
-    The Milky Way is known to host at least two modes in its present day distribution of Fe and $\alpha$-elements.
+    The Milky Way hosts at least two modes in its present day distribution of Fe and $\alpha$-elements.
 The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive satellite (Gaia-Sausage-Enceladus) at $z\sim2$.
@@
 The quiescent period in this galaxy is not associated with a merger but by the formation of a bar followed by AGN activity.
-This galaxy indicates a novel scenario in which the $\alpha$-bimodality is caused by AGN-induced quenching triggered by the formation of the Milky Way's bar.
-We argue that the post-processing step can be interpreted as the TNG model underproducing star formation in the densest regions at high-$z$.
+This galaxy indicates a novel scenario in which the $\alpha$-bimodality in the Milky Way is caused by AGN-induced quenching triggered by the formation of its bar.
+We predict that abundance bimodalities should be more common in barred as opposed to unbarred galaxies.
   \end{abstract}
@@
 Therefore, the present-day distribution of their abundances encodes the chemical history of a galaxy's gas phase.
-Two classes elements have received particular attention in the Milky Way due to their disparate formation channels: iron-peak (such as Fe) and $\alpha$-elements (produced through the $\alpha$-process, such as O and Mg).
+Two classes of elements have received particular attention in the Milky Way due to their disparate formation channels: iron-peak (such as Fe) and $\alpha$-elements (produced through the $\alpha$-process, such as O and Mg).
 Iron-peak elements are produced in both Type~Ia and Type~II supernovae (SNe) whereas $\alpha$-elements are produced predominantly through Type~II SNe.
@@
 
-In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,Myr$) quiescent period in the Galaxy's history, which has two effects.
+In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history, which has two effects.
 First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia\footnote{These SNe occur on different timescales (10s of Myr after star formation for Type~II, as compared to 100s of Myr to Gyrs for Type~Ia), so if the SFR drops, the number of Type~II SNe drops faster than Type~Ia.}, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
@@
 In Paper~I, we used idealized simulations of a galaxy merger that triggered the quiescent period.
-However, we argued that the merger aspect of that work was not necessary.
+However, in that work we argued the merger was unnecessary.
 In this work, we study a subhalo, or galaxy, from the Illustris TNG50 simulation demonstrating this.
 This subhalo of interest (SoI) exhibits the sequence of events presented in Paper~I after a simple post-processing step which increases the \alphaFe{} of old star particles.
-This post-processing is motivated by recent work demonstrating that the star formation efficiency (SFE) of the dense gas present at high-$z$ is too low \citep{2024arXiv240909121H}.
+This post-processing is motivated by recent work demonstrating that the star formation efficiency (SFE) of the dense gas present at high-$z$ is too low in the TNG model \citep{2024arXiv240909121H}.
 The SoI undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
@@
 
-In Section~\ref{sec:methods} we discuss our selection technique which led to discovering the SoI, the observations we use for comparison, as well as a simple one zone chemical evolution model we use to justify our post-processing step.
-In Section~\ref{sec:results} we present the main results which we discuss and interpret in Section~\ref{sec:disc}.
+In Section~\ref{sec:methods}, we discuss our selection technique which led to discovering the SoI, the observations we use for comparison, as well as a simple one zone chemical evolution model we use to justify our post-processing step.
+In Section~\ref{sec:results}, we present the main results which we discuss and interpret in Section~\ref{sec:disc}.
 We conclude in Section~\ref{sec:conc}.
-
-% This decline of \alphaFe{} over time has long been recognized \citep{1979ApJ...229.1046T}.
-This trend is only generally true, though, with non-monotonic behavior observed in observations and even one-zone chemical models \citep[e.g.][]{2022arXiv220402989C}.
 
@@
 It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG model \citep{2013MNRAS.436.3031V, 2017MNRAS.465.3291W, 2018MNRAS.473.4077P}.
-This model includes several subgrid processes: a wind generation model, chemical enrichment from SNe and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.
+This model includes several subgrid processes, including a wind generation model, chemical enrichment from SNe and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.
 
@@
 
-Using the public catalog, we selected a sample of subhalos at $z=1.5$ (snapshot 40) according to the following criteria: (1) the subhalo is central (i.e., the most massive subhalo within its halo), and (2) the subhalo's stellar mass is between $10^{10}$ and $10^{10.5}\,\Msun/\textrm{h}$.
+Using the public catalog, we select a sample of subhalos at $z=1.5$ (snapshot 40) according to the following criteria: (1) the subhalo is central (i.e., the most massive subhalo within its halo), and (2) the subhalo's stellar mass is between $10^{10}$ and $10^{10.5}\,\Msun/\textrm{h}$.
 There were a total of 168 subhalos that met both criteria.
-The chosen mass range is broadly consistent with the expected mass of the Milky Way at this redshift \citep{2013ApJ...771L..35V}.
+The chosen mass range is broadly consistent with the expected mass of the Milky Way from abundance matching at this redshift \citep{2013ApJ...771L..35V}.
 We choose to make our selection of galaxies at $z=1.5$ instead of at lower redshift because we wish to capture the \textit{formation} of multimodal structure.
@@
 We examine the abundance distribution in the \MgFe{}-\FeH{} plane for this sample of subhalos by visual inspection.
-Few subhalos display multimodal structure, and when present, it is much weaker compared to that observed in the Milky Way.
+Few subhalos display multimodal structure and, when present, is much weaker compared to that observed in the Milky Way.
 We then apply a post-processing step to the \MgFe{} of the stars, adding a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ to each star particle, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$), and $t_{\textrm{form}}$ is the formation time of the star particle.
@@
 Of these subhalos, some structure is present, but none have a strong bimodality as seen in the Milky Way.
-After the $\alpha$-enhancement, a few have strongly bimodal features (subject to interpretation): 172175, 178140, 193025.
+After the $\alpha$-enhancement, a few have strongly bimodal features: 172175, 178140, 193025.
 
-\begin{table}[]
+\begin{table}[htb]
   \centering
@@
   \end{tabular}
-  \caption{Summary statistics of our subhalo of interest at $z=0$.
+  \caption{Summary statistics of our subhalo of interest at $z=0$ (392276).
 $M_{200}$ and $R_{200}$ are relative to the mean density of the universe, the SFR is for all gas bound to the subhalo, and the BH refers to the central BH.}
@@
 We make the same selection cuts as in Section~2.4 of Paper I.
-These criteria are meant to select giants with high quality abundance measurements as well as restricting the sample to only stars in the disk with angular momenta similar to the Sun's.
+These criteria select giants with high quality abundance measurements and angular momenta similar to the Sun's.
 This results in a sample of 54,777 stars.
@@
 
-We then further considered a dataset of stellar ages from the APOKASC2 catalog \citep{2018ApJS..239...32P}.
+We then further considered a dataset of stellar ages from the APOKASC-3 catalog \citep{2024arXiv241000102P}.
 This catalog uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
@@
 \subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
-One-zone galactic chemical evolution (GCE) models describe enrichment in an idealized gas reservoir in which newly synthesized metals mix instantaneously (see e.g.
-the reviews by \citealt{Tinsley1980} and \citealt{Matteucci2021}).
+One-zone galactic chemical evolution (GCE) models describe enrichment in an idealized gas reservoir in which newly synthesized metals mix instantaneously (see, e.g., the reviews by \citealt{Tinsley1980} and \citealt{Matteucci2021}).
 Our parameter choices in this paper are based on the models in \citet{2022arXiv220402989C}.
@@
 
-The quantity that is of particular importance to our results is the star formation efficiency (SFE) timescale $\tau_\star$:
+The quantity of particular importance to our results is the star formation efficiency (SFE) timescale $\tau_\star$:
 \begin{equation}
-\tau_\star \equiv \frac{M_{\textrm{gas}}}{\dot{M}_{\textrm{star}}},
+\tau_\star \equiv \frac{M_{\textrm{gas}}}{\SFR},
 \end{equation}
-where $M_{\textrm{gas}}$ and $\dot{M}_{\textrm{star}}$ are the ISM mass and star formation rate, respectively.
+where $M_{\textrm{gas}}$ is the mass of the gas reservoir.
 This timescale can be equivalently expressed as the ratio of the corresponding surface densities $\Sigma_{\textrm{gas}}$ and $\dot{\Sigma}_{\textrm{star}}$.
-$\tau_\star$ is the inverse of the SFE itself, describing the rate of star formation per unit mass in the ISM.
+$\tau_\star$ is the inverse of the SFE itself, describing the rate of star formation per unit gas mass.
 In principle, $\tau_\star$ should vary with $M_{\textrm{gas}}$ because the observed relation between $\dot{\Sigma}_{\textrm{star}}$ and $\Sigma_{\textrm{gas}}$ is non-linear; classically, $\dot{\Sigma}_{\textrm{star}} \propto \Sigma_{\textrm{gas}}^N$ where $N \approx 1.5$ (e.g.
@@
 For simplicity, we hold $\tau_\star$ constant in this paper, which corresponds to a linear relation.
-In section 3.5 below, we present models using $\tau_\star = 0.5$, $1$, and $5$ Gyr.
+In Section~\ref{ssec:onezone} below, we present models using $\tau_\star = 0.5$, $1$, and $5\,\Gyr$.
 
@@
 Zero metallicity gas accretes at a constant rate of $\dot{M}_\text{in} = 5\,\Msunyr$.
-The efficiency with which feedback sweeps up ISM material and ejects it to the CGM in an outflow is described by the mass loading factor $\eta \equiv \dot{M}_\text{out} / \dot{M}_\star$.
+The efficiency with which feedback sweeps up interstellar material and ejects it to the circumgalactic medium in an outflow is described by the mass loading factor $\eta \equiv \dot{M}_\text{out} / \SFR$.
 We use $\eta = 2$ throughout this paper (i.e.
-for every solar mass of stars formed, $2\,\Msun$ of ISM gas is lost to an outflow).
+for every solar mass of stars formed, $2\,\Msun$ of interstellar gas is lost to an outflow).
 These parameter choices lead to an SFH that initially rises from zero and approaches a constant value of $\sim1.9\,\Msunyr$.
-With these choices, the predicted abundance evolution is insensitive to the overall normalization of the accretion and star formation histories, since a larger accretion rate forms more stars and metals but simultaneously introduces more H into the ISM.
+With these choices, the predicted abundance evolution is insensitive to the overall normalization of the accretion and star formation histories, since a larger accretion rate forms more stars and metals but simultaneously introduces more H into the interstellar medium.
 
-We use the solar abundances of Fe and Mg from \citet{Magg2022} with an additional 0.04 dex to account for the effects of diffusion and gravitational settling (\citealt{Turcotte1998}; i.e.
+We use the solar abundances of Fe and Mg from \citet{Magg2022} with an additional $0.04\,\dex$ to account for the effects of diffusion and gravitational settling (\citealt{Turcotte1998}; i.e.
 $\{Z_{\text{Fe},\odot}, Z_{\text{Mg},\odot}\} = \{13.7, 6.71\} \times 10^{-4}$).
@@
 These yields are population-averaged, meaning that they quantify the amount of metal production per unit mass of star formation under the given enrichment channel (e.g.
-a hypothetical $1000\,\Msun$ stellar population would produce a total of $0.652\,\Msun$ of Mg through Type~II SNe).
+a hypothetical $10^3\,\Msun$ stellar population would produce a total of $0.652\,\Msun$ of Mg through Type~II SNe).
 {\tt VICE} models Type~II SNe as exploding instantaneously following an episode of star formation.
@@
 Colors are plotted in a log scale ranging from $0.08$ to $15\,\dex^{-2}$.
-Contour lines are plotted at $0.1$, $1.5$, and $10\,\dex^{-2}$.
+Dashed contour lines are plotted at $0.1$, $1.5$, and $10\,\dex^{-2}$.
 
@@
 The lower panels show 1D histograms of \MgFe{} in bins centered on these values.
-The bins for the Milky Way/simulations have width $0.2$/$0.05\,\dex$.
-The rationale for the higher plotted \FeH{} in the simulations comes just from the empirical location of the bimodalities.
+The bins have width $0.2$/$0.05\,\dex$, which is reflected in the width of the colored, shaded regions in the upper panels.
+The rationale for the higher plotted \FeH{} in the simulations reflects the empirical location of the bimodalities.
 The Milky Way shows a clear bimodal population, with a high-$\alpha$ sequence most clearly distinct from the low-$\alpha$ sequence at low metallicity.
@@
 
-Our SoI, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column).
+The SoI, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column).
 There is some structure in the $\FeH=-0.75$ bin.
-The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with a post-processed declination in \MgFe{} described in Section~\ref{ssec:tng}.
-Star particles formed before $z=1.5$ are given an additive offset of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ and $t_{\textrm{form}}$ is the formation time of the star particle.
+The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with a modification to increase \MgFe{} values of older stars formed before $z=1.5$ (see Sections~\ref{ssec:tng} and \ref{ssec:onezone}).
 A multimodal structure emerges with three clear modes at $\MgFe\sim0.8$, $0.5$, and $0.2\,\dex$.
@@
 These error values align with the observational uncertainties from the APOKASC2 and APOGEE datasets, which the Milky Way panel (lower left) is based on (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
-While the error in \MgFe{} is relatively minor, the age error ($1.5\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
+While the error in \MgFe{} is insignificant, the age error ($1.5\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
 Despite this, the $\alpha$-enhanced SoI still shows two distinct populations, although their ages now overlap more significantly.
@@
   \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200.pdf}
-  \caption{\textbf{The evolutionary history of our subhalo of interest.} The left column shows the SFH, BH accretion rate, and virial mass ($M_{200}$) over the entire time span, while the right column zooms in on the period from $t\sim2\,\Gyr$ to $t\sim5\,\Gyr$.
+  \caption{\textbf{The evolutionary history of our subhalo of interest.} The left column shows the SFH, BH accretion rate, and virial mass ($M_{200}$) over the entire time span, while the right column zooms in on the period from $t=2\,\Gyr$ to $t=5\,\Gyr$.
 The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$, corresponding to the separation between the high- and low-$\alpha$ sequences (as shown in Figure~\ref{fig:alpha}).
-The middle panel shows the BH accretion rate as a fraction of the Eddington limit, and the lower panel shows the virial mass, representing the mass enclosed within a radius where the density is $200\times$ the mean cosmic density.}
+The upper panel shows the SFH, the middle panel shows the BH accretion rate as a fraction of the Eddington limit, and the lower panel shows the virial mass, representing the mass enclosed within a radius where the density is $200\times$ the mean cosmic density.}
   \label{fig:history}
@@
 
-To understand the key events driving the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of several properties of the subhalo in Figure~\ref{fig:history}.
+To understand the key events driving the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of several properties of the SoI in Figure~\ref{fig:history}.
 The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$ from the high- to low-$\alpha$ sequences, as in Figure~\ref{fig:alpha}.
-The upper panel in the left column shows the the SFR (computed for all gas cells in the subhalo).
+The upper panel in the left column shows the the SFR (computed for all gas cells in the SoI).
 There are two peaks at $t\sim2.5\,\Gyr$ and $t\sim4.5\,\Gyr$ with maximum values of $50\,\Msun/\textrm{yr}$ and $30\,\Msun/\textrm{yr}$, respectively.
@@
 The right panel zooms in on the period between $t=2\,\Gyr$ and $5\,\Gyr$, where we observe a sharp recovery in the SFR following the quiescent phase.
-In a single snapshot (spanning roughly 150 Myr), the SFR increases from about $3\,\Msun/\textrm{yr}$ to $10\,\Msun/\textrm{yr}$.
+In the span of a single snapshot (roughly $150\,\Myr$), the SFR increases from about $3\,\Msun/\textrm{yr}$ to $10\,\Msun/\textrm{yr}$.
 
 The middle panels track the accretion rate of the central BH as a fraction of the Eddington rate.
-Early in the subhalo's history ($t<2\,\Gyr$), the BH experiences high accretion, which steadily declines until $t\sim5\,\Gyr$.
+Early in the SoI's history ($t<2\,\Gyr$), the BH experiences high accretion, which steadily declines until $t\sim5\,\Gyr$.
 Around $t\sim3.2\,\Gyr$, the BH accretion rate peaks again, reaching approximately $30\%$ of the Eddington limit, placing the BH in quasar mode and injecting significant thermal energy into the galaxy's center.
@@
 
-The lower panel illustrates the growth of the subhalo's virial mass ($M_{200}$).
+The lower panel illustrates the growth of the SoI's virial mass ($M_{200}$).
 Early on ($t<4\,\Gyr$), $M_{200}$ increases roughly linearly, reaching about $2 \times 10^{12}\,\Msun$.
@@
     \item SFR declines: The SFR declines starting from a maximum of $54.3\,\Msunyr$ at $t=2.84\,\Gyr$ down to $3.6\,\Msunyr$ at $t=3.28\,\Gyr$.
-In the next snapshot at $t=3.45\,\Gyr$ the SFR recovers to $12.2\,\Msunyr$ and remains above
-
-    After the increase in BH accretion, the star formation rate (SFR) begins to decline.
-The decrease in SFR steadily commences as the BH accretion rate remains elevated.
-By approximately $3.2\,\textrm{Gyr}$, the SFR reaches a more quiescent state at $\sim3\,\Msunyr$.
-After one snapshot, the SFR increases to
+In the next snapshot at $t=3.45\,\Gyr$ the SFR recovers to $12.2\,\Msunyr$.
+Figure~\ref{fig:history} shows that it reaches its second maximum of $30.9\,\Msunyr$ at $4.5\,\Gyr$.
 \end{enumerate}
@@
 The upper panel shows the evolution of \MgFe{} over $2\,\Gyr$, while the lower panel shows the negative of its time derivative.
-Increasing the SFE ($\dot{Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$) leads to a more rapid decline in \MgFe{}.
+Increasing the SFE (decreasing $\tau_\star$) leads to a more rapid decline in \MgFe{}.
 At its steepest decline ($t\sim0.5\,\Gyr$), increasing the SFE by an order of magnitude results in a slope nearly twice as steep.
@@
 This $\alpha$-enhancement corresponds to a more rapid decline in \alphaFe{} over time at high redshifts.
-Figure~\ref{fig:vice} demonstrates that having too low SFE at high densities is a plausible explanation for why such a steep decline in \alphaFe{} might not be occuring in the fiducial TNG model.
+Figure~\ref{fig:vice} suggests that a low SFE at high densities may plausibly explain the absence of a steep decline in \alphaFe{} in the fiducial TNG model.
 
-The upper panel of Figure~\ref{fig:vice} presents the evolution of \MgFe{} in three one-zone chemical evolution models with varying star formation efficiencies (SFE).
-A higher SFE leads to a faster reduction in \MgFe{}.
-In the model with the highest SFE ($2\,\Gyr^{-1}$, blue, where SFE is $\dot{\Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ over $2\,\Gyr$.
-In contrast, the model with the lowest SFE ($0.2\,\Gyr^{-1}$) only reaches $\sim0.2\,\dex$ within the same period.
+The evolution of \MgFe{} in three one-zone GCE models with varying SFEs is shown in the upper panel of Figure~\ref{fig:vice} (models described in Section~\ref{ssec:onezone_met}).
+A higher SFE (lower $\tau_\star$) leads to a faster reduction in \MgFe{}.
+In the model with the highest SFE ($2\,\Gyr^{-1}$, $\tau_\star=0.5\,\Gyr$, blue), \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ over $2\,\Gyr$.
+In contrast, the model with the lowest SFE ($0.2\,\Gyr^{-1}$, $\tau_\star=5\,\Gyr$, red) only reaches $\sim0.2\,\dex$ within the same period.
 
@@
 Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the SoI?, and (2) what justifies the $\alpha$-enhancement?
-We then briefly extend our comparison to the Milky Way data.
+We then extend our comparison to data and argue the quiescent period is driven by a bar-induced AGN episode.
 
 \subsection{Cause of Bimodality}\label{ssec:bim_cause}
-An extensive analysis of our SoI is beyond the scope of this work, but here we argue that the evidence is consistent with the scenario presented in Paper I.
+Here we argue that the available evidence for the cause of the bimodality is consistent with the scenario presented in Paper~I.
 They presented an idealized simulation resembling the merger between the Milky Way and GSE.
@@
 The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} denotes the transition between the high- and low-$\alpha$ sequences.
-We place it at a lookback time of $10.6\,\Gyr$ or a formation time of $\sim3.2\,\Gyr$.
-The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} so their medians are at zero).
+We place it at a lookback time of $10.6\,\Gyr$ or a cosmic time of $\sim3.2\,\Gyr$ or $z\sim2.05$.\footnote{The transition between the high- and low-$\alpha$ sequences occurs approximately $1\,\Gyr$ before $z=1.5$, where the $\alpha$-enhancement begins.
+This, combined with the fact that not all of the subhalos in our sample display bimodalities (Appendix~\ref{app:rand_fig1}), shows that the $\alpha$-enhancement is not the direct cause of the bimodality.} The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} to prevent overlap).
 Stars formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
-At the line, we see a gap in the $\FeH=-0.5$ and $-0.25$ bins.
+At the $\alpha$-transition, we see a gap in the $\FeH=-0.5$ and $-0.25$ bins.
 
@@
 We vary the SFE of the model ($\dot{Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), and examine the impact on the \MgFe{} ratio as a function of time.
-We find that shorter SF timescales do lead to a more rapid reduction in \MgFe{}.
+We find that a higher SFE does lead to a more rapid reduction in \MgFe{}.
 The rate of decrease in \MgFe{}, at its maximum, varies between $\sim-0.25$, $-0.35$, and $-0.5\,\dex/\Gyr$ in the $\textrm{SFE}=0.2$, $1$, and $2\,\Gyr^{-1}$ models, respectively.
 For our post-processing, we assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
-Such a difference is well within the range of \MgFe{} decrease seen in our different $\tau_{\star}$ models, implying a factor of only $\sim2$ in the SFE is needed to reach our post-processing slope.
+Such a difference is well within the range of \MgFe{} slopes seen in our different $\tau_{\star}$ models, implying a factor of only $\sim2$ to $5$ in the SFE is needed to reach our post-processing slope.
 
 \citet{2024arXiv240909121H} demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude.
-This is well within our needed factor of $2$ in the SFE (see Figure~\ref{fig:vice}).
+This is well within our needed factor of $\sim2$ to $5$ in the SFE (see Figure~\ref{fig:vice}).
 Therefore, \MgFe{} should decline more rapidly with a different feedback model (or future iteration of the TNG model) that leads to a higher SFE at high densities.
@@
 \subsection{Direct Comparison to Observations}\label{ssec:compare_obs}
-The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC2 catalog.
+The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC-3 catalog.
 In the bins where the bimodality is strongest (blue and orange, $\FeH=-0.5$ and $-0.25$, respectively), we see that there is a sort of two tiered distribution with significant overlap in age.
-In the SoI with age and abundance errors shown in the lower right panel, a very similar distribution can be seen in all \FeH{} bins.
+In the SoI with age and abundance errors shown in the lower right panel, a similar distribution can be seen in all \FeH{} bins.
 An examination of the true distribution in the SoI (upper right panel), we see that the two distributions are in fact very cleanly separated in age.
-We do not know the true underlying distribution in the Milky Way, but these panels show that the general picture shown in our SoI is consistent with the Milky Way.
+
+There is also a population of young, $\alpha$-rich stars in the APOKASC-3 data.
+These may or may not reflect the typical or average ISM chemistry.
+Arguments have been made that they are old stars with misclassified astroseismic ages due to binary mass transfer \citep[and references therein]{2023A&A...671A..21J}.
+However, some appear to be genuinely young \citep[and references therein]{2024arXiv241002962L}, with a range of explanations given \citep[e.g.][]{2015A&A...576L..12C,2021MNRAS.508.4484J,2023arXiv231105815S}.
+Disentangling these effects is far from clear and beyond the scope of this work.
+At least some of the young, $\alpha$-rich stars in Figure~\ref{fig:alpha} do not reflect the ISM chemistry at their inferred astroseismic age, and so would not be included in the TNG model.
+With this caveat, the two appear to be consistent.
 
 \subsection{Cause of Quiescence}\label{ssec:cause_qui}
-It is natural to question why the minimum in the SFR occurs.
-In Paper~I, AGN activity from a merger was the suspected cause.
-Here, we can see that there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
-Based on this burst, it is reasonable to suspect that AGN activity is also responsible for the quiescent period in our SoI.
+In Paper~I, AGN activity from a merger was the suspected cause for the quiescent period.
+In our SoI, there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
+Based on this burst, it is also reasonable to suspect that AGN activity is also responsible for the quiescent period in our SoI.
 However, we argue that the cause of the localized spike in the BH accretion rate is not due to a merger but instead due to the formation/strengthening of a bar.
@@
 
-As described in Section~\ref{ssec:sequence_of_events}, the following sequence of events occurs: the bar strengthens and then the BH accretion rate spikes, all while the SFR of the galaxy declines.
+As described in Section~\ref{ssec:sequence_of_events}, the bar strengthens and then the BH accretion rate spikes, all while the SFR of the galaxy declines.
 This is suggestive of the following causal sequence:
@@
 However, there is a significant body of theoretical and observational work in support of this picture.
-Bars and other non-axisymmetric features have long been argued to funnel gas into the centers of galaxies on theoretical grounds \citep{1989Natur.338...45S,2010MNRAS.407.1529H}.In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.
+Bars and other non-axisymmetric features have long been argued to funnel gas into the centers of galaxies on theoretical grounds \citep{1989Natur.338...45S,2010MNRAS.407.1529H}.
+In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.
 Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
@@
 This implies the possibility of starvation as a quenching mechanism.
-However, the average depletion time in the preceding 5 snapshots (which are each $\sim150\,\Myr$ apart) is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its CGM.
+However, the average depletion time in the preceding 5 snapshots (which are each $\sim150\,\Myr$ apart) is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its environment.
 A definitive account, difficult with the current simulation outputs because of its sparse snapshot spacing, requires further work.
@@
 \section{Conclusions}\label{sec:conc}
-In this work, we examined a specific subhalo in Illustris TNG50.
-This subhalo is at a Milky Way-progenitor mass at high-$z$ ($z\sim2$).
+In this work, we examined a subhalo of interest in Illustris TNG50.
+This SoI is at a Milky Way-progenitor mass at $z=1.5$.
 After applying a post-processing step that increased the \MgFe{} of star particles formed before $z=1.5$, this subhalo hosts a strong bimodality in the plane of \MgFe{} and \FeH{}, shown in Figure~\ref{fig:fig1}.
-This post-processing is justified by arguing that the SFE of dense gas is too low in TNG \citep[][see discussion in Section~\ref{ssec:sfe}]{2024arXiv240909121H}.
-
-This bimodality can be traced to an event that occurred at an age of $10.6\,\Gyr$, or formation time of $\sim3.2\,\Gyr$ ($z\sim2$).
-Shown as a vertical dashed line in Figure~\ref{fig:alpha}, star particles which form before this form at high-$\alpha$ while stars which form after form at lower $\alpha$.
-At the dashed line, there is a gap.
-We argue that the presence of this gap is responsible for the valley in the bimodality (Figure~\ref{fig:fig1}).
-It is accompanied by a global reduction in the SFR by about a factor of 6 (upper panel of Figure~\ref{fig:history}).
+This post-processing is justified by arguing that the SFE of dense gas is too low in TNG \citep[][see discussion in our Section~\ref{ssec:sfe}]{2024arXiv240909121H}.
 

### 2024-10-09 paper/ms.tex
Add citations

@@
 
-In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history, which has two effects.
+In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history (an observational claim with a broader period of quiescence was made in \citet{2016A&A...589A..66H}).
+This period has two effects.
 First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia\footnote{These SNe occur on different timescales (10s of Myr after star formation for Type~II, as compared to 100s of Myr to Gyrs for Type~Ia), so if the SFR drops, the number of Type~II SNe drops faster than Type~Ia.}, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
 Second, the lower SFR results in fewer stars forming in the region between the high- and low-$\alpha$ sequences, reducing the occurance of this transitional population in present-day observations.
+The combination of these two effects creates the valley between the high- and low-$\alpha$ sequences.
 This mechanism resembles two-phase infall models that incorporate a temporary halt in star formation \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period in Paper~I is much shorter.
-The combination of these two effects creates the valley between the high- and low-$\alpha$ sequences.
 
@@
 
+At a BH mass of $\sim10^8\,\Msun$, the low-accretion kinetic mode tends to dominate across the TNG box \citep{2017MNRAS.465.3291W}.
+Interestingly, the BH here crosses this threshold at the $t=3.28\,\Gyr$ snapshot.
+
 \subsection{One-Zone Model}\label{ssec:onezone}
@@
 Bars and other non-axisymmetric features have long been argued to funnel gas into the centers of galaxies on theoretical grounds \citep{1989Natur.338...45S,2010MNRAS.407.1529H}.
-In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.
-Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+It was recently shown by \citet{2024arXiv240906783F} that bars can induce quiescence by accelerating the growth of a SMBH, but they found there can be many Gyr between bar formation and quenching.
+In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.\footnote{\citet{2022A&A...668L...3L} studied a galaxy from TNG100 in which a merger induced AGN activity that ejected gas from its center.
+A bar then formed out of the gas-poor disk.} Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
 

### 2024-10-09 paper/ms.tex
Update for APOKASC3

@@
 The effect of the $\alpha$-enhancement is clear, as it separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$).
-The lower panels show on the left the Milky Way and on the center and right the data from TNG but with $15\%$ age errors and $0.01\,\dex$ errors in \MgFe{}.
+The lower panels show on the left the Milky Way and on the center and right the data from TNG but with $12.5\%$ age errors and $0.01\,\dex$ errors in \MgFe{}.
 When the simulations are given these errors, we see that the before and after star particles smear such that the two populations significantly overlap in ages.
@@
 In the lower row, the left panel shows data from the Milky Way, while the middle and right panels correspond to the fiducial and $\alpha$-enhanced SoI, respectively.
-For the simulations, we introduce Gaussian errors of $15\%$ in age and $0.01,\dex$ in \MgFe{}.
-These error values align with the observational uncertainties from the APOKASC2 and APOGEE datasets, which the Milky Way panel (lower left) is based on (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
+For the simulations, we introduce Gaussian errors of $12.5\%$ in age and $0.01,\dex$ in \MgFe{}.
+These error values align with the observational uncertainties from the APOKASC-3 and APOGEE datasets, which the Milky Way panel (lower left) is based on (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
 While the error in \MgFe{} is insignificant, the age error ($1.5\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
@@
 \section{Observational Errors}\label{app:obs_err}
-In Figure~\ref{fig:alpha}, we assumed observational errors of $15\%$ in age and $0.01\,\dex$ in \MgFe{}.
-In Figure~\ref{fig:obs_err}, we plot the quoted observational errors of the APOKASC2 (left) and ASPCAP (right) datasets, showing both \FeH{} and \MgFe{} (blue and orange, respectively).
-We show our $15\%$ age error and $0.01\,\dex$ abundance error assumptions as black lines.
+In Figure~\ref{fig:alpha}, we assumed observational errors of $12.5\%$ in age and $0.01\,\dex$ in \MgFe{}.
+In Figure~\ref{fig:obs_err}, we plot the quoted observational errors of the APOKASC-3 (left) and ASPCAP (right) datasets, showing both \FeH{} and \MgFe{} (blue and orange, respectively).
+We show our $12.5\%$ age error and $0.01\,\dex$ abundance error assumptions as black lines.
 For the age error, we used the maximum of the upper and lower estimates from \citet{2018ApJS..239...32P}.
-Our assumed errors are generally consistent with the errors.
+As a dashed line we show our $25\%$ age error cut for stars plotted in Figure~\ref{fig:obs_err}.
+Our assumed errors are generally consistent with the observed.
 Our error in \MgFe{} is a bit smaller than in ASPCAP, but the age estimates are by far the more constraining of the two.
@@
   \includegraphics[width=\columnwidth]{fig/obs_error.pdf}
-  \caption{The observational errors of the APOKASC2 (left) and ASPCAP dataset (right).
-We show, on the left, a line indicating a $15\%$ error in observed age and on the right a vertical line indicating a $0.01\,\dex$ error.}
+  \caption{The observational errors of the APOKASC-3 (left) and ASPCAP dataset (right).
+We show, on the left, a line indicating a $12.5\%$ error in observed age and on the right a vertical line indicating a $0.01\,\dex$ error.
+On the left, a dashed line indicates the $25\%$ error cut used for inclusion in Figure~\ref{fig:alpha}.}
   \label{fig:obs_err}

### 2024-10-11 paper/ms.tex
Some small edits and title

@@
 \usepackage{enumitem}
+\usepackage{booktabs}
 
@@
 
-\title{Rising from the Ashes II: Can Bar Formation Lead to Abundance Bimodalities?}
+\title{Rising from the Ashes II: The Bar-driven Abundance Bimodality in the Milky Way}
 
@@
 We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a sequence of starburst, brief quiescence, and then rejuvenation.
+
     Following a minor post-processing adjustment -— motivated by recent findings on the star formation efficiency in TNG -- which increases the \alphaFe{} values of older star particles, we demonstrate that this galaxy exhibits a pronounced bimodal distribution in the \alphaFe{}-\FeH{} plane.
+
+    This sequence results in a pronounced abundance bimodality after a post-processing adjustment of the \alphaFe{} of old stars which is designed to mimic a higher star formation efficiency in dense gas.
+
     The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
@@
 
-\begin{table}[htb]
+% Please add the following required packages to your document preamble:
+\begin{table}[]
   \centering
-  \begin{tabular}{ll}
-  \multicolumn{2}{c}{dark matter}                                                                  \\ \hline
+  \begin{tabular}{@{}ll@{}}
+  \toprule
+  \multicolumn{2}{c}{dark matter}                                                  \\ \midrule
   \multicolumn{1}{l|}{$M_{200}$}                      & $4.97\times10^{12}\,\Msun$ \\
@@
                                                       &                            \\
-  \multicolumn{2}{c}{baryons}                                                                      \\ \hline
+  \multicolumn{2}{c}{baryons}                                                      \\ \midrule
   \multicolumn{1}{l|}{$\rhalf$}                       & $2\,\kpc$                  \\
@@
   \multicolumn{1}{l|}{$M_{\textrm{BH}}$}              & $2.9\times10^{8}\,\Msun$   \\
-  \multicolumn{1}{l|}{$\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{Edd}}$} & $4.5\times10^{-5}$        
+  $\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{Edd}}$      & $4.5\times10^{-5}$         \\ \bottomrule
   \end{tabular}
-  \caption{Summary statistics of our subhalo of interest at $z=0$ (392276).
+  \caption{Summary statistics of our subhalo of interest at $z=0$.
 $M_{200}$ and $R_{200}$ are relative to the mean density of the universe, the SFR is for all gas bound to the subhalo, and the BH refers to the central BH.}
@@
 
-The quantity of particular importance to our results is the star formation efficiency (SFE) timescale $\tau_\star$:
+The quantity of particular importance to our results is the star formation efficiency (SFE) timescale $\tau_\star$ (also known as the depletion time):
 \begin{equation}
@@
 This $\alpha$-enhancement corresponds to a more rapid decline in \alphaFe{} over time at high redshifts.
-Figure~\ref{fig:vice} suggests that a low SFE at high densities may plausibly explain the absence of a steep decline in \alphaFe{} in the fiducial TNG model.
+We demonstrate the physical motivation behind this $\alpha$-enhnacement in Figure~\ref{fig:vice}.
 
@@
 
-This analysis illustrates that a higher SFE at early times (high redshift) leads to a faster decrease in \MgFe{}.
+This analysis illustrates that a higher SFE at early times (high-$z$) leads to a faster decline in \MgFe{}.
 Recent work has suggested that the SFE in such dense regions in TNG may indeed be too low, as discussed in Section~\ref{ssec:sfe}.
+The post-processing $\alpha$-enhancement in Section~\ref{ssec:tng} is meant to mimic a SFE correction of high-$z$ dense gas.
 

### 2024-10-11 paper/ms.tex
Fix abstract
Lars edits

@@
 
-\title{Rising from the Ashes II: The Bar-driven Abundance Bimodality in the Milky Way}
+\title{Rising from the Ashes II: The Bar-driven Abundance Bimodality of the Milky Way}
 
@@
 We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a sequence of starburst, brief quiescence, and then rejuvenation.
-
-    Following a minor post-processing adjustment -— motivated by recent findings on the star formation efficiency in TNG -- which increases the \alphaFe{} values of older star particles, we demonstrate that this galaxy exhibits a pronounced bimodal distribution in the \alphaFe{}-\FeH{} plane.
-
     This sequence results in a pronounced abundance bimodality after a post-processing adjustment of the \alphaFe{} of old stars which is designed to mimic a higher star formation efficiency in dense gas.
-
     The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
@@
 First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia\footnote{These SNe occur on different timescales (10s of Myr after star formation for Type~II, as compared to 100s of Myr to Gyrs for Type~Ia), so if the SFR drops, the number of Type~II SNe drops faster than Type~Ia.}, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
-Second, the lower SFR results in fewer stars forming in the region between the high- and low-$\alpha$ sequences, reducing the occurance of this transitional population in present-day observations.
+Second, the lower SFR results in fewer stars forming in the region between the high- and low-$\alpha$ sequences, reducing the occurrence of this transitional population in present-day observations.
 The combination of these two effects creates the valley between the high- and low-$\alpha$ sequences.
@@
 \subsection{IllustrisTNG Sample}\label{ssec:tng}
-We use Illustris TNG50 \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$).
+We use Illustris TNG50 \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N, 2019ComAC...6....2N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$).
 It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG model \citep{2013MNRAS.436.3031V, 2017MNRAS.465.3291W, 2018MNRAS.473.4077P}.
@@
 % Please add the following required packages to your document preamble:
-\begin{table}[]
-  \centering
-  \begin{tabular}{@{}ll@{}}
-  \toprule
-  \multicolumn{2}{c}{dark matter}                                                  \\ \midrule
-  \multicolumn{1}{l|}{$M_{200}$}                      & $4.97\times10^{12}\,\Msun$ \\
-  \multicolumn{1}{l|}{$R_{200}$}                      & $532\,\kpc$                \\
+\begin{deluxetable}{lc}
+  \tablecaption{Summary statistics of our subhalo of interest at $z=0$.
+$M_{200}$ and $R_{200}$ are relative to the mean density of the universe, the SFR is for all gas bound to the subhalo, and the BH refers to the central BH.
+\label{tab:summ}}
+  \tablewidth{0pt}
+  \tablehead{
+    % \colhead{} & \colhead{}
+  }
+  \startdata
+  \multicolumn{2}{c}{\textbf{dark matter}} \\ \hline
+  $M_{200}$ & $4.97\times10^{12}\,\Msun$ \\
+  $R_{200}$ & $532\,\kpc$ \\
   & \\
-  \multicolumn{2}{c}{baryons}                                                      \\ \midrule
-  \multicolumn{1}{l|}{$\rhalf$}                       & $2\,\kpc$                  \\
-  \multicolumn{1}{l|}{$M_{\textrm{star}}(r<4\rhalf)$} & $7.6\times10^{12}\,\Msun$  \\
-  \multicolumn{1}{l|}{$M_{\textrm{gas}}(r<4\rhalf)$}  & $2.6\times10^{11}\,\Msun$  \\
-  \multicolumn{1}{l|}{$\textrm{SFR}$}                 & $0.56\,\Msunyr$            \\
-  \multicolumn{1}{l|}{$M_{\textrm{BH}}$}              & $2.9\times10^{8}\,\Msun$   \\
-  $\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{Edd}}$      & $4.5\times10^{-5}$         \\ \bottomrule
-  \end{tabular}
-  \caption{Summary statistics of our subhalo of interest at $z=0$.
-$M_{200}$ and $R_{200}$ are relative to the mean density of the universe, the SFR is for all gas bound to the subhalo, and the BH refers to the central BH.}
-  \label{tab:summ}
-  \end{table}
+  \multicolumn{2}{c}{\textbf{baryons}} \\ \hline
+  $\rhalf$ & $2\,\kpc$ \\
+  $M_{\textrm{star}}(r<4\rhalf)$ & $7.6\times10^{12}\,\Msun$ \\
+  $M_{\textrm{gas}}(r<4\rhalf)$ & $2.6\times10^{11}\,\Msun$ \\
+  $\textrm{SFR}$ & $0.56\,\Msunyr$ \\
+  $M_{\textrm{BH}}$ & $2.9\times10^{8}\,\Msun$ \\
+  $\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{Edd}}$ & $4.5\times10^{-5}$ \\
+  \enddata
+\end{deluxetable}
 
@@
 
-In the SoI, there is an age gap at $sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
+In the SoI, there is an age gap at $\sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
 Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
@@
 This $\alpha$-enhancement corresponds to a more rapid decline in \alphaFe{} over time at high redshifts.
-We demonstrate the physical motivation behind this $\alpha$-enhnacement in Figure~\ref{fig:vice}.
+We demonstrate the physical motivation behind this $\alpha$-enhancement in Figure~\ref{fig:vice}.
 
@@
 \subsection{Cause of Bimodality}\label{ssec:bim_cause}
-Here we argue that the available evidence for the cause of the bimodality is consistent with the scenario presented in Paper~I.
-They presented an idealized simulation resembling the merger between the Milky Way and GSE.
-They varied the orbital parameters slightly in a grid of 27 simulations and found that simulations which had a brief quiescent period as a result of the merger led to a bimodal abundance distribution.
-They argued that AGN activity was responsible for this brief quenching.
+We argue that the available evidence for the cause of the bimodality aligns with the scenario outlined in Paper~I.
+That study presented an idealized simulation resembling the merger between the Milky Way and GSE, where the orbital parameters were varied slightly across a grid of 27 simulations.
+The results showed that simulations featuring a brief quiescent period due to the merger produced a bimodal abundance distribution.
+In this scenario, gas expulsion by AGN activity was identified as the driving force behind the quenching.
 
@@
 We place it at a lookback time of $10.6\,\Gyr$ or a cosmic time of $\sim3.2\,\Gyr$ or $z\sim2.05$.\footnote{The transition between the high- and low-$\alpha$ sequences occurs approximately $1\,\Gyr$ before $z=1.5$, where the $\alpha$-enhancement begins.
-This, combined with the fact that not all of the subhalos in our sample display bimodalities (Appendix~\ref{app:rand_fig1}), shows that the $\alpha$-enhancement is not the direct cause of the bimodality.} The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} to prevent overlap).
+This, combined with the fact that not all of the subhalos in our sample display bimodalities (Appendix~\ref{app:rand_fig1}), shows that the $\alpha$-enhancement is not the direct cause of the bimodality.} The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs.
+star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} to prevent overlap).
 Stars formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
@@
 The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models.
-Isolating the cause of the ``incorrect''\footnote{Our case study of a single subhalo, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} \MgFe{} vs time evolution at high-$z$ is not straightforward nor, in our opinion, even possible.
+Isolating the cause of the ``incorrect''\footnote{Our case study of a single subhalo, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} \MgFe{} vs.
+time evolution at high-$z$ is not straightforward nor, in our opinion, even possible.
 However, we do offer one reasonable explanation: the SFE at high densities, more present at high-$z$, is too low.
@@
 The details of our setup is given in Section~\ref{ssec:onezone_met}.
-We vary the SFE of the model ($\dot{Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), and examine the impact on the \MgFe{} ratio as a function of time.
+We vary the SFE of the model ($\dot{\Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), and examine the impact on the \MgFe{} ratio as a function of time.
 We find that a higher SFE does lead to a more rapid reduction in \MgFe{}.
@@
 
-An intuitive understanding of the impact the decline in \alphaFe{} vs time has is that, when \alphaFe{} declines rapidly, it is a better estimator of age.
+An intuitive understanding of the impact the decline in \alphaFe{} vs.
+time has is that, when \alphaFe{} declines rapidly, it is a better estimator of age.
 When \alphaFe{} is a better estimator of age, events which are separated temporally become better separated in the abundance plane.
@@
 \subsection{Direct Comparison to Observations}\label{ssec:compare_obs}
-The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC-3 catalog.
+The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs.
+age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC-3 catalog.
 In the bins where the bimodality is strongest (blue and orange, $\FeH=-0.5$ and $-0.25$, respectively), we see that there is a sort of two tiered distribution with significant overlap in age.
@@
 
-This bimodality can be traced to an event that occurred at an age of $10.6\,\Gyr$, or formation time of $\sim3.2\,\Gyr$ ($z\sim2$).
+This bimodality can be traced to an event that occurred at an age of $10.6\,\Gyr$, or cosmic time of $\sim3.2\,\Gyr$ ($z\sim2$).
 Shown as a vertical dashed line in Figure~\ref{fig:alpha}, star particles that form before this time are at high-\MgFe{}, while star particles that form after are at low-\MgFe{}.
@@
 This argument is the same as presented in Paper~I and is consistent with the one-zone chemical evolution models of \citet{2020MNRAS.498.1364J}.
-When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the distribution observed in the Milky Way (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).
+When observational errors are added to the subhalo's abundance vs.
+age distribution, we show that it is broadly consistent with the distribution observed in the Milky Way (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).
 

### 2024-10-11 paper/ms.tex
Charlie comments

@@
 The quiescent period in this galaxy is not associated with a merger but by the formation of a bar followed by AGN activity.
-This galaxy indicates a novel scenario in which the $\alpha$-bimodality in the Milky Way is caused by AGN-induced quenching triggered by the formation of its bar.
+This galaxy indicates a novel scenario in which the $\alpha$-bimodality in the Milky Way is caused by the formation of the bar via AGN-induced quenching.
 We predict that abundance bimodalities should be more common in barred as opposed to unbarred galaxies.
@@
 Two classes of elements have received particular attention in the Milky Way due to their disparate formation channels: iron-peak (such as Fe) and $\alpha$-elements (produced through the $\alpha$-process, such as O and Mg).
-Iron-peak elements are produced in both Type~Ia and Type~II supernovae (SNe) whereas $\alpha$-elements are produced predominantly through Type~II SNe.
+Enrichment of iron-peak elements is primarily through Type~Ia and Type~II supernovae (SNe), whereas enrichment of $\alpha$-elements is primarily only through Type~II SNe.
 In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences shown in Figure~\ref{fig:fig1} \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
@@
 Third and finally, the bimodality is generated through a merger process, either by enhancing the star formation rate (SFR) of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
-Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
+Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports the merger-related scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
 
@@
 In this work, we study a subhalo, or galaxy, from the Illustris TNG50 simulation demonstrating this.
-This subhalo of interest (SoI) exhibits the sequence of events presented in Paper~I after a simple post-processing step which increases the \alphaFe{} of old star particles.
+This galaxy exhibits the sequence of events presented in Paper~I after a simple post-processing step which increases the \alphaFe{} of old star particles.
 This post-processing is motivated by recent work demonstrating that the star formation efficiency (SFE) of the dense gas present at high-$z$ is too low in the TNG model \citep{2024arXiv240909121H}.
-The SoI undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
+The galaxy undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
 However, instead of being preceded by a merger, the quenching is preceded by apparent bar-induced AGN activity.
@@
 
-In Section~\ref{sec:methods}, we discuss our selection technique which led to discovering the SoI, the observations we use for comparison, as well as a simple one zone chemical evolution model we use to justify our post-processing step.
+In Section~\ref{sec:methods}, we discuss our selection technique which led to discovering the galaxy, the observations we use for comparison, as well as a simple one zone chemical evolution model we use to justify our post-processing step.
 In Section~\ref{sec:results}, we present the main results which we discuss and interpret in Section~\ref{sec:disc}.
@@
 A summary of its key properties is given in Table~\ref{tab:summ}.
-We refer to this subhalo as our subhalo of interest (SoI).
 
@@
 
-The SoI, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column).
+Our galaxy, on the other hand, does not show a clearly bimodal structure in the fiducial simulation (middle column).
 There is some structure in the $\FeH=-0.75$ bin.
@@
 When the simulations are given these errors, we see that the before and after star particles smear such that the two populations significantly overlap in ages.
-In the $\alpha$-enhanced SoI, two populations emerge in each bin which overlapped in the fiducial distribution.
+In the $\alpha$-enhanced galaxy, two populations emerge in each bin which overlapped in the fiducial distribution.
 This feature more closely resembles the Milky Way, which displays such populations where the bimodality is strongest -- $\FeH=-0.5$ (blue) and $-0.25$ (orange).}
@@
 The abundance distributions shown in Figure~\ref{fig:fig1} can be better understood by examining the evolution of \MgFe{} with time of the individual stars/star particles.
-In the upper panels of Figure~\ref{fig:alpha} we show the true distribution of \MgFe{} as a function of time for the fiducial SoI in the middle and for the post-processed, $\alpha$-enhanced subhalo to the right.
+In the upper panels of Figure~\ref{fig:alpha} we show the true distribution of \MgFe{} as a function of time for the fiducial galaxy in the middle and for the post-processed, $\alpha$-enhanced subhalo to the right.
 We use age instead of formation time in order to better facilitate comparisons to observations.
@@
 
-In the SoI, there is an age gap at $\sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
+In our galaxy, there is an age gap at $\sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
 Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
@@
 
-In the lower row, the left panel shows data from the Milky Way, while the middle and right panels correspond to the fiducial and $\alpha$-enhanced SoI, respectively.
+In the lower row, the left panel shows data from the Milky Way, while the middle and right panels correspond to the fiducial and $\alpha$-enhanced galaxy, respectively.
 For the simulations, we introduce Gaussian errors of $12.5\%$ in age and $0.01,\dex$ in \MgFe{}.
@@
 While the error in \MgFe{} is insignificant, the age error ($1.5\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
-Despite this, the $\alpha$-enhanced SoI still shows two distinct populations, although their ages now overlap more significantly.
+Despite this, the $\alpha$-enhanced galaxy still shows two distinct populations, although their ages now overlap more significantly.
 
-Interestingly, the Milky Way distribution (lower left panel) exhibits similarities to the $\alpha$-enhanced SoI.
+Interestingly, the Milky Way distribution (lower left panel) exhibits similarities to the $\alpha$-enhanced galaxy.
 Specifically, in the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively), there appear to be two populations that overlap in age but remain distinct in \MgFe{}.
@@
 
-To understand the key events driving the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of several properties of the SoI in Figure~\ref{fig:history}.
+To understand the key events driving the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of several properties of our galaxy in Figure~\ref{fig:history}.
 The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$ from the high- to low-$\alpha$ sequences, as in Figure~\ref{fig:alpha}.
-The upper panel in the left column shows the the SFR (computed for all gas cells in the SoI).
+The upper panel in the left column shows the the SFR (computed for all gas cells in the galaxy).
 There are two peaks at $t\sim2.5\,\Gyr$ and $t\sim4.5\,\Gyr$ with maximum values of $50\,\Msun/\textrm{yr}$ and $30\,\Msun/\textrm{yr}$, respectively.
@@
 The middle panels track the accretion rate of the central BH as a fraction of the Eddington rate.
-Early in the SoI's history ($t<2\,\Gyr$), the BH experiences high accretion, which steadily declines until $t\sim5\,\Gyr$.
+Early in our galaxy's history ($t<2\,\Gyr$), the BH experiences high accretion, which steadily declines until $t\sim5\,\Gyr$.
 Around $t\sim3.2\,\Gyr$, the BH accretion rate peaks again, reaching approximately $30\%$ of the Eddington limit, placing the BH in quasar mode and injecting significant thermal energy into the galaxy's center.
@@
 
-The lower panel illustrates the growth of the SoI's virial mass ($M_{200}$).
+The lower panel illustrates the growth of the galaxy's virial mass ($M_{200}$).
 Early on ($t<4\,\Gyr$), $M_{200}$ increases roughly linearly, reaching about $2 \times 10^{12}\,\Msun$.
@@
   \includegraphics[width=\textwidth]{fig/alyssa.pdf}
-  \caption{Surface density projections of gas (top row) and star particles (middle row) in our SoI across snapshots at different times during the high- to low-$\alpha$ transition.
+  \caption{Surface density projections of gas (top row) and star particles (middle row) in our galaxy across snapshots at different times during the high- to low-$\alpha$ transition.
 Below the projections is a plot showing the SFR, BH accretion rate (in units of $\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$), and bar strength ($A_2/A_0$ for $R<2$ kpc).
@@
 \section{Discussion}\label{sec:disc}
-In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our SoI before and after our $\alpha$-enhancement post-processing procedure.
-It is clear that the TNG SoI is unimodal before the $\alpha$-enhancement and multi-modal afterwards.
-Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the SoI?, and (2) what justifies the $\alpha$-enhancement?
+In Figure~\ref{fig:fig1}, we compared the abundance plane between the Milky Way and our galaxy before and after our $\alpha$-enhancement post-processing procedure.
+It is clear that the TNG galaxy is unimodal before the $\alpha$-enhancement and multi-modal afterwards.
+Here, we briefly discuss two main points: (1) assuming the $\alpha$-enhancement is justified, what leads to the bimodality in the TNG galaxy?, and (2) what justifies the $\alpha$-enhancement?
 We then extend our comparison to data and argue the quiescent period is driven by a bar-induced AGN episode.
@@
 
-Once the $\alpha$-enhancement post-processing has been done, the SoI that we have studied in this work is consistent with this scenario.
+Once the $\alpha$-enhancement post-processing has been done, the galaxy that we have studied in this work is consistent with this scenario.
 The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} denotes the transition between the high- and low-$\alpha$ sequences.
@@
 
-It is also worth noting that in both the fiducial and $\alpha$-enhanced SoI show a slight rebound effect in \MgFe{}.
+It is also worth noting that in both the fiducial and $\alpha$-enhanced galaxy show a slight rebound effect in \MgFe{}.
 The star particles which form directly after the dashed line have a slightly lower \MgFe{} than stars which form after.
@@
 In the bins where the bimodality is strongest (blue and orange, $\FeH=-0.5$ and $-0.25$, respectively), we see that there is a sort of two tiered distribution with significant overlap in age.
-In the SoI with age and abundance errors shown in the lower right panel, a similar distribution can be seen in all \FeH{} bins.
-An examination of the true distribution in the SoI (upper right panel), we see that the two distributions are in fact very cleanly separated in age.
+In the galaxy with age and abundance errors shown in the lower right panel, a similar distribution can be seen in all \FeH{} bins.
+An examination of the true distribution in the galaxy (upper right panel), we see that the two distributions are in fact very cleanly separated in age.
 
@@
 In Paper~I, AGN activity from a merger was the suspected cause for the quiescent period.
-In our SoI, there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
-Based on this burst, it is also reasonable to suspect that AGN activity is also responsible for the quiescent period in our SoI.
+In our galaxy here, there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
+Based on this burst, it is also reasonable to suspect that AGN activity is also responsible for the quiescent period in our galaxy.
 However, we argue that the cause of the localized spike in the BH accretion rate is not due to a merger but instead due to the formation/strengthening of a bar.
@@
 This implies the possibility of starvation as a quenching mechanism.
-However, the average depletion time in the preceding 5 snapshots (which are each $\sim150\,\Myr$ apart) is $220\,\Myr$, so clearly the SoI is accreting high amounts of gas from its environment.
+However, the average depletion time in the preceding 5 snapshots (which are each $\sim150\,\Myr$ apart) is $220\,\Myr$, so clearly the galaxy is accreting high amounts of gas from its environment.
 A definitive account, difficult with the current simulation outputs because of its sparse snapshot spacing, requires further work.
@@
 In this work, we examined a subhalo of interest in Illustris TNG50.
-This SoI is at a Milky Way-progenitor mass at $z=1.5$.
+This galaxy is at a Milky Way-progenitor mass at $z=1.5$.
 After applying a post-processing step that increased the \MgFe{} of star particles formed before $z=1.5$, this subhalo hosts a strong bimodality in the plane of \MgFe{} and \FeH{}, shown in Figure~\ref{fig:fig1}.
@@
 In Figures~\ref{fig:app0} to \ref{fig:app16}, we show a version of Figure~\ref{fig:fig1} but for a random selection of subhalos from our broader sample of 168 Milky Way-progenitors at $z=1.5$ in TNG50.
-It is from this sample that we selected our SoI.
-We first show our SoI at $z=1.5$ in Figure~\ref{fig:app0}, and then show our random sample of 16.
+It is from this sample that we selected our galaxy of interest.
+We first show this galaxy at $z=1.5$ in Figure~\ref{fig:app0}, and then show our random sample of 16.
 
@@
   \includegraphics[width=\textwidth]{fig/app_172175.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for our SoI at $z=1.5$.}
+  \caption{The same as Figure~\ref{fig:fig1}, but for our galaxy of interest at $z=1.5$.}
   \label{fig:app0}

### 2024-10-16 paper/ms.tex
More edits based on coauthors

@@
 After the $\alpha$-enhancement, a few have strongly bimodal features: 172175, 178140, 193025.
+It is worth noting that the post-processing is not in itself responsible for the emergence of bimodality, as it only does so for a fraction of the galaxies shown in Appendix~\ref{app:rand_fig1}.
+Furthermore, if a galaxy had \alphaFe{} slowly and continuously decrease with time, then our $\alpha$-enhancement would not give rise to a bimodality since it is also a continuous adjustment.
 
@@
 We make use of two observational data sets.
-First, we use the ASPCAP DR17 catalog of stellar abundances \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G}.
+First, we use the stellar abundances from the ASPCAP pipeline of APOGEE DR17 \citep[][J.A.~Holtzman et al., in preparation]{2016AJ....151..144G,2017AJ....154...28B,2017AJ....154...94M,2022ApJS..259...35A}.
 We make the same selection cuts as in Section~2.4 of Paper I.
@@
 
-The quantity of particular importance to our results is the star formation efficiency (SFE) timescale $\tau_\star$ (also known as the depletion time):
+The quantity of particular importance to our results is the depletion time $\tau_{\textrm{dep}}$, also known as the inverse of the star formation efficiency (SFE)\footnote{Note that the SFE we discuss here is averaged over a representative patch (e.g., kpc-size) and is not the dimensionless fraction of a giant molecular cloud that is converted into stars over its lifetime.} or the SFE timescale:
 \begin{equation}
-\tau_\star \equiv \frac{M_{\textrm{gas}}}{\SFR},
+\tau_{\textrm{dep}} \equiv \frac{M_{\textrm{gas}}}{\SFR},
 \end{equation}
@@
 This timescale can be equivalently expressed as the ratio of the corresponding surface densities $\Sigma_{\textrm{gas}}$ and $\dot{\Sigma}_{\textrm{star}}$.
-$\tau_\star$ is the inverse of the SFE itself, describing the rate of star formation per unit gas mass.
-In principle, $\tau_\star$ should vary with $M_{\textrm{gas}}$ because the observed relation between $\dot{\Sigma}_{\textrm{star}}$ and $\Sigma_{\textrm{gas}}$ is non-linear; classically, $\dot{\Sigma}_{\textrm{star}} \propto \Sigma_{\textrm{gas}}^N$ where $N \approx 1.5$ (e.g.
+$\tau_{\textrm{dep}}$ is the inverse of the SFE itself, describing the rate of star formation per unit gas mass.
+In principle, $\tau_{\textrm{dep}}$ should vary with $M_{\textrm{gas}}$ because the observed relation between $\dot{\Sigma}_{\textrm{star}}$ and $\Sigma_{\textrm{gas}}$ is non-linear; classically, $\dot{\Sigma}_{\textrm{star}} \propto \Sigma_{\textrm{gas}}^N$ where $N \approx 1.5$ (e.g.
 \citealt{Schmidt1959, Kennicutt1998}).
-For simplicity, we hold $\tau_\star$ constant in this paper, which corresponds to a linear relation.
-In Section~\ref{ssec:onezone} below, we present models using $\tau_\star = 0.5$, $1$, and $5\,\Gyr$.
+For simplicity, we hold $\tau_{\textrm{dep}}$ constant in this paper, which corresponds to a linear relation.
+In Section~\ref{ssec:onezone} below, we present models using $\tau_{\textrm{dep}} = 0.5$, $1$, and $5\,\Gyr$.
 
@@
 for every solar mass of stars formed, $2\,\Msun$ of interstellar gas is lost to an outflow).
-These parameter choices lead to an SFH that initially rises from zero and approaches a constant value of $\sim1.9\,\Msunyr$.
+These parameter choices lead to a SFH that initially rises from zero and approaches a constant value of $\sim1.9\,\Msunyr$.
 With these choices, the predicted abundance evolution is insensitive to the overall normalization of the accretion and star formation histories, since a larger accretion rate forms more stars and metals but simultaneously introduces more H into the interstellar medium.
@@
 
-With the exception of our SN yields, we find through experimentation that the decline in \MgFe{} with time is most significantly sensitive to the value of $\tau_\star$.
+With the exception of our SN yields, we find through experimentation that the decline in \MgFe{} with time is most significantly sensitive to the value of $\tau_{\textrm{dep}}$.
 We therefore expect its connection to the decline in \MgFe{} on which this paper is focused to be robust.
@@
 
-To understand the key events driving the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of several properties of our galaxy in Figure~\ref{fig:history}.
+To understand the key events driving the behavior around the dashed line in Figure~\ref{fig:alpha}, we examine the evolution of several properties of our galaxy in Figure~\ref{fig:history}: its SFH, the BH accretion rate, and the growth of the virial mass.
 The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$ from the high- to low-$\alpha$ sequences, as in Figure~\ref{fig:alpha}.
@@
 The middle right panel shows the period between $t=2$ and $5\,\Gyr$.
+We can see that the decline in the galaxy's SFR is contemperaneous with this increase in the BH accretion rate.
 
@@
 After this, the mass remains relatively stable until jumps occur around $t\sim10$ and $\sim12\,\Gyr$, indicative of mergers.
+These late-time mergers raise the virial mass to $5 \times 10^{12},\Msun$, well above the typical Milky Way estimate of $1$--$1.5\times 10^{12},\Msun$ \citep[e.g.][]{2016ARA&A..54..529B}.
+However, during the high- to low-$\alpha$ transition, the virial mass remains consistent with a Milky Way progenitor, making this galaxy a suitable analog.
 There are no mergers related to the earlier quiescent period around $t\sim3.2\,\Gyr$, as no major mass jumps are observed during this time.
@@
 
-Figure~\ref{fig:seq} presents surface density projections of gas and stars at different stages of the high- to low-$\alpha$ transition.
+In order to gain a more intuitive sense of the events around the high- to low-$\alpha$ transition, we show surface density projections alongside key summary statistics of our galaxy in Figure~\ref{fig:seq}.
 The upper panels show gas density, while the middle panels display stellar density.
-Time progresses from $\sim2.4$ to $\sim3.6\,\textrm{Gyr}$, corresponding to redshifts ranging from $z\sim2.7$ to $z\sim1.8$.
+Time progresses from $\sim2.4$ to $\sim3.6\,\textrm{Gyr}$, corresponding to redshifts ranging from $z\sim2.7$ to $z\sim1.8$, and the high- to low-$\alpha$ transition is indicated with a vertical dashed line.
 
@@
 
-At a BH mass of $\sim10^8\,\Msun$, the low-accretion kinetic mode tends to dominate across the TNG box \citep{2017MNRAS.465.3291W}.
-Interestingly, the BH here crosses this threshold at the $t=3.28\,\Gyr$ snapshot.
-
 \subsection{One-Zone Model}\label{ssec:onezone}
@@
 The upper panel shows the evolution of \MgFe{} over $2\,\Gyr$, while the lower panel shows the negative of its time derivative.
-Increasing the SFE (decreasing $\tau_\star$) leads to a more rapid decline in \MgFe{}.
+Increasing the SFE (decreasing $\tau_{\textrm{dep}}$) leads to a more rapid decline in \MgFe{}.
 At its steepest decline ($t\sim0.5\,\Gyr$), increasing the SFE by an order of magnitude results in a slope nearly twice as steep.
@@
 The evolution of \MgFe{} in three one-zone GCE models with varying SFEs is shown in the upper panel of Figure~\ref{fig:vice} (models described in Section~\ref{ssec:onezone_met}).
-A higher SFE (lower $\tau_\star$) leads to a faster reduction in \MgFe{}.
-In the model with the highest SFE ($2\,\Gyr^{-1}$, $\tau_\star=0.5\,\Gyr$, blue), \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ over $2\,\Gyr$.
-In contrast, the model with the lowest SFE ($0.2\,\Gyr^{-1}$, $\tau_\star=5\,\Gyr$, red) only reaches $\sim0.2\,\dex$ within the same period.
+A higher SFE (lower $\tau_{\textrm{dep}}$) leads to a faster reduction in \MgFe{}.
+In the model with the highest SFE ($2\,\Gyr^{-1}$, $\tau_{\textrm{dep}}=0.5\,\Gyr$, blue), \MgFe{} drops from $\sim0.45$ to $0.08\,\dex$ over $2\,\Gyr$.
+In contrast, the model with the lowest SFE ($0.2\,\Gyr^{-1}$, $\tau_{\textrm{dep}}=5\,\Gyr$, red) only reaches $\sim0.2\,\dex$ within the same period.
 
@@
 For our post-processing, we assumed an additional decrease rate of $0.1\,\dex/\Gyr$.
-Such a difference is well within the range of \MgFe{} slopes seen in our different $\tau_{\star}$ models, implying a factor of only $\sim2$ to $5$ in the SFE is needed to reach our post-processing slope.
+Such a difference is well within the range of \MgFe{} slopes seen in our different $\tau_{\textrm{dep}}$ models, implying a factor of only $\sim2$ to $5$ in the SFE is needed to reach our post-processing slope.
 

### 2024-10-19 paper/ms.tex
Updates to paper

@@
 However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality.
-We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a sequence of starburst, brief quiescence, and then rejuvenation.
-This sequence results in a pronounced abundance bimodality after a post-processing adjustment of the \alphaFe{} of old stars which is designed to mimic a higher star formation efficiency in dense gas.
-The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period.
-The quiescent period in this galaxy is not associated with a merger but by the formation of a bar followed by AGN activity.
+We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes subsequent phases of starburst, brief quiescence, and then rejuvenation.
+This scenario results in a pronounced abundance bimodality after a post-processing adjustment of the \alphaFe{} of old stars designed to mimic a higher star formation efficiency in dense gas.
+The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period, which is not associated with a merger but by the formation of a bar followed by AGN activity.
 This galaxy indicates a novel scenario in which the $\alpha$-bimodality in the Milky Way is caused by the formation of the bar via AGN-induced quenching.
-We predict that abundance bimodalities should be more common in barred as opposed to unbarred galaxies.
+In addition to a stellar age gap in the Milky Way, we predict that abundance bimodalities should be more common in barred as opposed to unbarred galaxies.
   \end{abstract}
@@
 Enrichment of iron-peak elements is primarily through Type~Ia and Type~II supernovae (SNe), whereas enrichment of $\alpha$-elements is primarily only through Type~II SNe.
-In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences shown in Figure~\ref{fig:fig1} \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
+In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences as shown in the upper left panel of Figure~\ref{fig:fig1} \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
 
@@
 
-In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history (an observational claim with a broader period of quiescence was made in \citet{2016A&A...589A..66H}).
+In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history (an observational claim with a longer period of quiescence was made in \citet{2016A&A...589A..66H}).
 This period has two effects.
 First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia\footnote{These SNe occur on different timescales (10s of Myr after star formation for Type~II, as compared to 100s of Myr to Gyrs for Type~Ia), so if the SFR drops, the number of Type~II SNe drops faster than Type~Ia.}, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
-Second, the lower SFR results in fewer stars forming in the region between the high- and low-$\alpha$ sequences, reducing the occurrence of this transitional population in present-day observations.
+Second, the lower SFR results in fewer stars forming in the intermediate region between the high- and low-$\alpha$ sequences, reducing the occurrence of this transitional population in present-day observations.
 The combination of these two effects creates the valley between the high- and low-$\alpha$ sequences.
@@
 In Paper~I, we used idealized simulations of a galaxy merger that triggered the quiescent period.
-However, in that work we argued the merger was unnecessary.
+However, in that work we argued that it was the quiescent period, not the merger, which was necessary to produce a bimodality.
 In this work, we study a subhalo, or galaxy, from the Illustris TNG50 simulation demonstrating this.
-This galaxy exhibits the sequence of events presented in Paper~I after a simple post-processing step which increases the \alphaFe{} of old star particles.
-This post-processing is motivated by recent work demonstrating that the star formation efficiency (SFE) of the dense gas present at high-$z$ is too low in the TNG model \citep{2024arXiv240909121H}.
+This galaxy exhibits the sequence of events presented in Paper~I after a post-processing step, motivated by recent work showing that the star formation efficiency (SFE) of dense gas at high-$z$ is too low in the TNG model \citep{2024arXiv240909121H}, which increases the \alphaFe{} of old star particles.
 The galaxy undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.
@@
 
+We select subhalo 172175 (the ID at snapshot 40) for its resemblance to the Milky Way.
+We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
+A summary of its key properties is given in Table~\ref{tab:summ}.
+
 % Please add the following required packages to your document preamble:
@@
 
-We select subhalo 172175 (the ID at snapshot 40) for its resemblance to the Milky Way.
-We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
-A summary of its key properties is given in Table~\ref{tab:summ}.
-
 \subsection{Observations}\label{ssec:obs}
@@
 This catalog uses a combination of APOGEE spectroscopic parameters and \textit{Kepler} time series photometry to compute astroseismic ages.
-Using only stars with $25\%$ age uncertainties (taken as the maximum of the upper and lower uncertainty), we cross-match this catalog to our larger sample from ASPCAP which results in a sample of 1201 stars.
+Using only stars with $25\%$ age uncertainties (taken as the maximum of the upper and lower uncertainty), we cross-match this catalog to our larger sample from ASPCAP which results in a sample of 2525 stars.
 
@@
 The lower panels show 1D histograms of \MgFe{} in bins centered on these values.
-The bins have width $0.2$/$0.05\,\dex$, which is reflected in the width of the colored, shaded regions in the upper panels.
+The bins have width $0.1\,\dex$, which is reflected in the width of the colored, shaded regions in the upper panels.
 The rationale for the higher plotted \FeH{} in the simulations reflects the empirical location of the bimodalities.
@@
 In the lower row, the left panel shows data from the Milky Way, while the middle and right panels correspond to the fiducial and $\alpha$-enhanced galaxy, respectively.
-For the simulations, we introduce Gaussian errors of $12.5\%$ in age and $0.01,\dex$ in \MgFe{}.
+For the simulations, we introduce Gaussian errors of $12.5\%$ in age and $0.01\,dex$ in \MgFe{}.
 These error values align with the observational uncertainties from the APOKASC-3 and APOGEE datasets, which the Milky Way panel (lower left) is based on (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
-While the error in \MgFe{} is insignificant, the age error ($1.5\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
+While the error in \MgFe{} is insignificant, the age error ($1.25\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
 Despite this, the $\alpha$-enhanced galaxy still shows two distinct populations, although their ages now overlap more significantly.
 
-Interestingly, the Milky Way distribution (lower left panel) exhibits similarities to the $\alpha$-enhanced galaxy.
+The Milky Way distribution (lower left panel) exhibits some similarities to the $\alpha$-enhanced galaxy.
 Specifically, in the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively), there appear to be two populations that overlap in age but remain distinct in \MgFe{}.
 These are the bins where the bimodality is most pronounced (as seen in the upper left panel of Figure~\ref{fig:fig1}).
+In the Milky Way there also appears to be a population of $\alpha$-rich stars down to low ages (see discussion in Section~\ref{ssec:compare_obs}).
 
@@
 There are no mergers related to the earlier quiescent period around $t\sim3.2\,\Gyr$, as no major mass jumps are observed during this time.
-The lower right panel shows the period between $t=2$ and $5\,\Gyr$.
+The lower right panel shows the lack of mergers in more detail during the period between $t=2$ and $5\,\Gyr$.
 
@@
   \includegraphics[width=\textwidth]{fig/alyssa.pdf}
-  \caption{Surface density projections of gas (top row) and star particles (middle row) in our galaxy across snapshots at different times during the high- to low-$\alpha$ transition.
+  \caption{\textbf{Quiescence separating the high- and low-$\alpha$ sequences is preceded by AGN activity associated with bar formation.} Surface density projections of gas (top row) and star particles (middle row) in our galaxy across snapshots at different times during the high- to low-$\alpha$ transition.
 Below the projections is a plot showing the SFR, BH accretion rate (in units of $\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$), and bar strength ($A_2/A_0$ for $R<2$ kpc).
@@
 
-This Figure shows the following sequence of events:
+This figure shows the following sequence of events:
 \begin{enumerate}
@@
 
-Once the $\alpha$-enhancement post-processing has been done, the galaxy that we have studied in this work is consistent with this scenario.
-The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} denotes the transition between the high- and low-$\alpha$ sequences.
-We place it at a lookback time of $10.6\,\Gyr$ or a cosmic time of $\sim3.2\,\Gyr$ or $z\sim2.05$.\footnote{The transition between the high- and low-$\alpha$ sequences occurs approximately $1\,\Gyr$ before $z=1.5$, where the $\alpha$-enhancement begins.
-This, combined with the fact that not all of the subhalos in our sample display bimodalities (Appendix~\ref{app:rand_fig1}), shows that the $\alpha$-enhancement is not the direct cause of the bimodality.} The upper right panel of Figure~\ref{fig:alpha} shows 2D histograms of \MgFe{} vs.
-star particle age in fixed bins of \FeH{} (each color is a different \FeH{} bin, and an offset is given to \MgFe{} to prevent overlap).
-Stars formed before the dashed line had a steep decline of \MgFe{} with time, while the relation in star particles formed after the dashed line is much more flat.
-At the $\alpha$-transition, we see a gap in the $\FeH=-0.5$ and $-0.25$ bins.
+Once the $\alpha$-enhancement post-processing has been done, the galaxy that we have studied in this work is consistent with the quiescent scenario proposed in Paper~I.
+The distribution of \MgFe{} with star particle age is a useful way to test this scenario, which we plot in the upper right panel of Figure~\ref{fig:alpha} in fixed bins of \FeH{} (each color is a different \FeH{} bin).
+The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} marks the transition between the high- and low-$\alpha$ sequences.
+We place this transition at a lookback time of $10.6,\Gyr$, corresponding to a cosmic time of approximately $3.2,\Gyr$ or redshift $z\sim2.05$.
+\footnote{The transition between the high- and low-$\alpha$ sequences occurs approximately $1\,\Gyr$ before $z=1.5$, where the $\alpha$-enhancement begins.
+This, combined with the fact that not all of the subhalos in our sample display bimodalities (Appendix~\ref{app:rand_fig1}), shows that the $\alpha$-enhancement is not the direct cause of the bimodality.} Star particles formed before this transition show a steep decline in \MgFe{} over time, with a drop of approximately $0.3\,\dex$ in just $2\,\Gyr$.
+In contrast, the stars formed after the dashed line exhibit a much flatter trend, with no noticeable gradient in \MgFe{} for the next couple of Gyr.
 
+At the transition, we can see a gap in the $\FeH=-0.5$, $-0.25$, and $0\,\dex$ bins (orange, green, and red, respectively).
+The gap has a width of about $300\,\Myr$ in the $-0.5$ and $-0.25\,\dex$ bins, while it is more extended at about $750\,\Myr$ in the $0\,\dex$ bin.
 The age gap in each \FeH{} bin of Figure~\ref{fig:alpha} is contemperaneous with a minimum in the global SFR.
@@
 During this period of suppressed SF, we argue that the lack of enrichment of Type~II relative to Type~Ia SNe leads to a lower rate of Mg production.
+The typical lifetime of a Type~II SN progenitor in this model is $\sim40\,\Myr$ \citep{2018MNRAS.473.4077P}, and so the hundreds of Myr of suppressed SF is short enough to restrict the production of $\alpha$-elements.
 Therefore, \MgFe{} rapidly declines.
@@
 
-It is also worth noting that in both the fiducial and $\alpha$-enhanced galaxy show a slight rebound effect in \MgFe{}.
-The star particles which form directly after the dashed line have a slightly lower \MgFe{} than stars which form after.
+Notably, both the fiducial and $\alpha$-enhanced galaxy show a slight rebound effect in \MgFe{}.
+The star particles which form directly after the dashed line when the SFR has just recovered have a slightly lower \MgFe{} than stars which form later on, by about $0.1$ to $0.2\,\dex$.
 This was also predicted in Figure~9 of Paper~I, where it was argued that during the period of suppressed star formation, the \alphaFe{} ratio of the star-forming gas drops sharply due to the reduced contribution of Type~II relative to Type~Ia SNe.
@@
 The details of our setup is given in Section~\ref{ssec:onezone_met}.
-We vary the SFE of the model ($\dot{\Sigma}_{\textrm{star}}/\Sigma_{\textrm{gas}}$), and examine the impact on the \MgFe{} ratio as a function of time.
+We vary the SFE of the model ($\textrm{SFR}/M_{\textrm{gas}}$), and examine the impact on \MgFe{} as a function of time.
 We find that a higher SFE does lead to a more rapid reduction in \MgFe{}.
@@
 In this work we have argued that the formation of the Milky Way's bar could be responsible.
-In external galaxies, we predict that the presence of a bar is correlated with the presence of an $\alpha$-bimodality.
+Regardless of this scenario's relevance to the Milky Way, we also predict that the presence of a bar in external galaxies is correlated with the presence of an $\alpha$-bimodality.
 

### 2024-10-28 paper/ms.tex
More edits from vadim and james

@@
 However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality.
-We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes subsequent phases of starburst, brief quiescence, and then rejuvenation.
+We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes sequential phases of starburst, brief quiescence, and then rejuvenation.
 This scenario results in a pronounced abundance bimodality after a post-processing adjustment of the \alphaFe{} of old stars designed to mimic a higher star formation efficiency in dense gas.
-The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period, which is not associated with a merger but by the formation of a bar followed by AGN activity.
+The high- and low-$\alpha$ sequences are separated in time by the brief quiescent period, which is not associated with a merger but by the formation of a bar followed by AGN activity.
 This galaxy indicates a novel scenario in which the $\alpha$-bimodality in the Milky Way is caused by the formation of the bar via AGN-induced quenching.
@@
 In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences as shown in the upper left panel of Figure~\ref{fig:fig1} \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
+The Milky Way is the only galaxy for which such a structure has been definitively shown to exist.\footnote{Note claims of a detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}
 
-Broadly speaking, there are three approaches to explaining the bimodality.
+The origin of the bimodality is a topic of active debate, with three main scenarios proposed to explain it.
 First, it is a result of internal secular processes that generate the bimodality through radial migration \citep{2009MNRAS.396..203S,2021MNRAS.507.5882S,2023MNRAS.523.3791C} or clump formation \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.
@@
 However, in that work we argued that it was the quiescent period, not the merger, which was necessary to produce a bimodality.
-In this work, we study a subhalo, or galaxy, from the Illustris TNG50 simulation demonstrating this.
+To demonstrate this, here we study a galaxy from the Illustris TNG50 cosmological simulation.
 This galaxy exhibits the sequence of events presented in Paper~I after a post-processing step, motivated by recent work showing that the star formation efficiency (SFE) of dense gas at high-$z$ is too low in the TNG model \citep{2024arXiv240909121H}, which increases the \alphaFe{} of old star particles.
@@
 We use Illustris TNG50 \citep{2019MNRAS.490.3196P, 2019MNRAS.490.3234N, 2019ComAC...6....2N}, a cosmological simulation of a $\sim50\,\textrm{cMpc}$ box at high resolution ($m_{\textrm{baryon}}\sim8.5\times10^4\,\Msun$).
-It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG model \citep{2013MNRAS.436.3031V, 2017MNRAS.465.3291W, 2018MNRAS.473.4077P}.
+It uses the gravito-magneto-hydrodynamics code \texttt{AREPO} \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P}, along with the TNG galaxy formation model \citep{2013MNRAS.436.3031V, 2017MNRAS.465.3291W, 2018MNRAS.473.4077P}.
 This model includes several subgrid processes, including a wind generation model, chemical enrichment from SNe and asymptotic giant branch stars, and thermal and kinetic feedback from AGN.
 
-One piece of the TNG model of note for this work is the black hole (BH) accretion and feedback method \citep{2017MNRAS.465.3291W}.
+There are two pieces of the TNG model of note for this work.
+First is the black hole (BH) accretion and feedback method \citep{2017MNRAS.465.3291W}.
 The BH accretion rate ($\dot{M}_{\textrm{BH}}$) is computed using the local structure of the gas phase with the Bondi-Hoyle-Lyttleton formula \citep{1939PCPS...35..405H,1944MNRAS.104..273B,1952MNRAS.112..195B}, with a maximum of the Eddington accretion rate ($\dot{M}_{\textrm{edd}}$).
@@
 If the Eddington ratio ($\dot{M}_{\textrm{BH}}/\dot{M}_{\textrm{edd}}$) exceeds a threshold ($M_{\textrm{BH}}$-dependent, but $\sim0.001$--$0.1$), the BH is in the quasar mode and injects a large amount of thermal energy into its surroundings.
+
+Second, is the star formation (SF) model, specifically how the SFR of a gas cell is set. Gas above the threshold density $\rho_{\textrm{th}}$ is given a SFR of $m_{\textrm{cell}}/t_{*}(\rho)$, where,
+\begin{equation*}
+t_{*}(\rho)=2.2\,\Gyr \left(\frac{\rho}{\rho_{\textrm{th}}}\right)^{-0.5}\textrm{.}
+\end{equation*}
+The threshold density is approximately $0.1\,\textrm{cm}^{-3}$.
+This model was originally conceived because it matched well the observed Kennicut-Schmidt relation \citep{Kennicutt1998,2003MNRAS.339..289S}.
+As will be discussed later, this relation is calibrated against normal star-forming galaxies, and so may underpredict the SFR at high gas densities.
 
@@
 
-We examine the abundance distribution in the \MgFe{}-\FeH{} plane for this sample of subhalos by visual inspection.
+We then visually inspected the abundance distribution in the \MgFe{}-\FeH{} plane for this sample of subhalos.
 Few subhalos display multimodal structure and, when present, is much weaker compared to that observed in the Milky Way.
-We then apply a post-processing step to the \MgFe{} of the stars, adding a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$ to each star particle, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$), and $t_{\textrm{form}}$ is the formation time of the star particle.
+We then apply a post-processing step to the \MgFe{} of the stars, adding a value of,
+\begin{equation*}
+  0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)\textrm{,}
+\end{equation*}
+to each star particle, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$), and $t_{\textrm{form}}$ is the formation time of the star particle.
 After this adjustment, which we justify in Section~\ref{ssec:sfe} based on TNG underpredicting the SFE of dense gas, we observe that the abundance structure becomes significantly more pronounced.
 
-We show the abundance distributions (replicating Figure~\ref{fig:fig1}) of 16 random subhalos from our catalog, and the subhalo we selected, in Appendix~\ref{app:rand_fig1}.
+We show the abundance distributions of 16 random subhalos from our $z=1.5$ catalog, and the subhalo we selected, in Appendix~\ref{app:rand_fig1}.
 Of these subhalos, some structure is present, but none have a strong bimodality as seen in the Milky Way.
@@
 
-We select subhalo 172175 (the ID at snapshot 40) for its resemblance to the Milky Way.
+We select subhalo 172175 (the Subfind ID at snapshot 40) for its resemblance to the Milky Way.
 We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
@@
 \begin{deluxetable}{lc}
-  \tablecaption{Summary statistics of our subhalo of interest at $z=0$.
+  \tablecaption{Summary statistics of our TNG galaxy at $z=0$.
 $M_{200}$ and $R_{200}$ are relative to the mean density of the universe, the SFR is for all gas bound to the subhalo, and the BH refers to the central BH.
@@
 \subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
-One-zone galactic chemical evolution (GCE) models describe enrichment in an idealized gas reservoir in which newly synthesized metals mix instantaneously (see, e.g., the reviews by \citealt{Tinsley1980} and \citealt{Matteucci2021}).
+As discussed in Section~\ref{ssec:tng}, we apply post-processing to enhance the $\alpha$-abundance of old star particles, motivated by the underprediction of the SFR in dense gas within TNG.
+To explore this, we use one-zone galactic chemical evolution (GCE) models, which describe enrichment in an idealized gas reservoir where newly synthesized metals mix instantaneously (see, e.g., the reviews by \citealt{Tinsley1980} and \citealt{Matteucci2021}).
 Our parameter choices in this paper are based on the models in \citet{2022arXiv220402989C}.
@@
 
-The quantity of particular importance to our results is the depletion time $\tau_{\textrm{dep}}$, also known as the inverse of the star formation efficiency (SFE)\footnote{Note that the SFE we discuss here is averaged over a representative patch (e.g., kpc-size) and is not the dimensionless fraction of a giant molecular cloud that is converted into stars over its lifetime.} or the SFE timescale:
+The quantity of particular importance to our results is the depletion time $\tau_{\textrm{dep}}$, also known as the inverse of the star formation efficiency (SFE)\footnote{Note that the SFE we discuss here is averaged over a representative patch (e.g., kpc-size) and is not the dimensionless fraction of a giant molecular cloud that is converted into stars over its lifetime or local freefall time.} or the SFE timescale:
 \begin{equation}
@@
 This timescale can be equivalently expressed as the ratio of the corresponding surface densities $\Sigma_{\textrm{gas}}$ and $\dot{\Sigma}_{\textrm{star}}$.
-$\tau_{\textrm{dep}}$ is the inverse of the SFE itself, describing the rate of star formation per unit gas mass.
 In principle, $\tau_{\textrm{dep}}$ should vary with $M_{\textrm{gas}}$ because the observed relation between $\dot{\Sigma}_{\textrm{star}}$ and $\Sigma_{\textrm{gas}}$ is non-linear; classically, $\dot{\Sigma}_{\textrm{star}} \propto \Sigma_{\textrm{gas}}^N$ where $N \approx 1.5$ (e.g.
@@
 These parameter choices lead to a SFH that initially rises from zero and approaches a constant value of $\sim1.9\,\Msunyr$.
-With these choices, the predicted abundance evolution is insensitive to the overall normalization of the accretion and star formation histories, since a larger accretion rate forms more stars and metals but simultaneously introduces more H into the interstellar medium.
+With these choices, the predicted abundance evolution of individual elements is insensitive to the overall normalization of the accretion and star formation histories, since a larger accretion rate forms more stars and metals but simultaneously introduces more H into the interstellar medium.
+The evolution of \MgFe{} is unchanged by these parameters.
 
@@
 $\{Z_{\text{Fe},\odot}, Z_{\text{Mg},\odot}\} = \{13.7, 6.71\} \times 10^{-4}$).
-We adopt SN yields of Fe and Mg based on \citeauthor{Weinberg2023}'s \citeyearpar{Weinberg2023} recommendations for Type~II SNe:
+We adopt SN yields of Fe and Mg based on \citeauthor{2024ApJ...973..122W}'s \citeyearpar{2024ApJ...973..122W} recommendations for Type~II SNe:
 \begin{itemize}
@@
 
-We use the yields recommended by \citet{Weinberg2023} because they are based on an empirical determination of the mean $^{56}$Ni yield from Type~II SNe by \citet{Rodriguez2021, Rodriguez2023} applied to multi-element abundance distributions in the Milky Way.
+We use the yields recommended by \citet{2024ApJ...973..122W} because they are based on an empirical determination of the mean $^{56}$Ni yield from Type~II SNe by \citet{Rodriguez2021, Rodriguez2023} applied to multi-element abundance distributions in the Milky Way.
 Theoretically predicted SN yields \citep[e.g.][]{Seitenzahl2013, Sukhbold2016, Limongi2018, Gronow2021} are subject to substantial theoretical uncertainties.
@@
 
-With the exception of our SN yields, we find through experimentation that the decline in \MgFe{} with time is most significantly sensitive to the value of $\tau_{\textrm{dep}}$.
+With the exception of our SN yields, we find through experimentation that the decline in \MgFe{} with time is most significantly sensitive to the value of $\tau_{\textrm{dep}}$, as mentioned before.
 We therefore expect its connection to the decline in \MgFe{} on which this paper is focused to be robust.
@@
   \includegraphics[width=\textwidth]{fig/392276.pdf}
-  \caption{\textbf{When old stars are $\alpha$-enhanced, our subhalo of interest from TNG displays a prominent bimodality.} The upper left panel shows the distribution in the \MgFe{}-\FeH{} plane of the Milky Way, demonstrating a clear bimodality (data selection given in text).
+  \caption{\textbf{When old stars are $\alpha$-enhanced, our galaxy from TNG displays a prominent bimodality.} The upper left panel shows the distribution in the \MgFe{}-\FeH{} plane of the Milky Way, demonstrating a clear bimodality (data selection given in text).
 The lower left panel shows the 1D histograms of \MgFe{} at fixed \FeH{} values of $-0.5$, $-0.25$, $0$, and $0.25$ (blue, orange, green, and red, respectively).
 In the Milky Way, the bimodality is strongest at low metallicities while disappearing at high metallicities.
-The middle column shows the same plots but for our TNG subhalo of interest (392276) and with the fixed \FeH{} values $0.25\,\dex$ lower.
+The middle column shows the same plots but for our TNG galaxy (392276) and with the fixed \FeH{} values $0.25\,\dex$ lower.
 Only faint structure is seen in the lowest bin (blue, $-0.75\,\dex$).
@@
 The main result of our paper is given in Figure~\ref{fig:fig1}.
-Here, we compare the abundance plane in the Milky Way (left column) to that of our subhalo of interest (middle and right columns).
+Here, we compare the abundance plane in the Milky Way (left column) to that of our TNG galaxy (middle and right columns).
 The upper panels show the 2D distribution in the space of \MgFe{}-\FeH{}.
@@
 There is some structure in the $\FeH=-0.75$ bin.
-The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with a modification to increase \MgFe{} values of older stars formed before $z=1.5$ (see Sections~\ref{ssec:tng} and \ref{ssec:onezone}).
+The right panel of Figure~\ref{fig:fig1} shows the same distribution as in the middle panel, but with a modification to increase \MgFe{} values of older stars formed before $z=1.5$ (see Sections~\ref{ssec:tng} and \ref{ssec:onezone}, as well as the upper panels of Figure~\ref{fig:alpha} for a visual demonstration).
 A multimodal structure emerges with three clear modes at $\MgFe\sim0.8$, $0.5$, and $0.2\,\dex$.
@@
   \includegraphics[width=\textwidth]{fig/392276_alpha.pdf}
-  \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs in simulation.} The upper panels show \MgFe{} as a function of age for our subhalo in TNG.
+  \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs separated by quiescence in simulation.} The upper panels show \MgFe{} as a function of age for our subhalo in TNG.
 The colors indicate stellar populations at fixed values of \FeH{}, which are the same as in Figure~\ref{fig:fig1}.
@@
 
-In our galaxy, there is an age gap at $\sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
+In our simulated galaxy, there is an age gap at $\sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
 Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
@@
 
-In the lower row, the left panel shows data from the Milky Way, while the middle and right panels correspond to the fiducial and $\alpha$-enhanced galaxy, respectively.
-For the simulations, we introduce Gaussian errors of $12.5\%$ in age and $0.01\,dex$ in \MgFe{}.
-These error values align with the observational uncertainties from the APOKASC-3 and APOGEE datasets, which the Milky Way panel (lower left) is based on (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
+In the lower row, the left panel displays data from the Milky Way, while the middle and right panels show the fiducial and $\alpha$-enhanced galaxy simulations, respectively.
+Gaussian errors of $12.5\%$ in age and $0.01\,dex$ in \MgFe{} were introduced in the simulations which align with the observational uncertainties in the APOKASC-3 and APOGEE datasets (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
+
 While the error in \MgFe{} is insignificant, the age error ($1.25\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
@@
   \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200.pdf}
-  \caption{\textbf{The evolutionary history of our subhalo of interest.} The left column shows the SFH, BH accretion rate, and virial mass ($M_{200}$) over the entire time span, while the right column zooms in on the period from $t=2\,\Gyr$ to $t=5\,\Gyr$.
+  \caption{\textbf{The evolutionary history of our TNG galaxy.} The left column shows the SFH, BH accretion rate, and virial mass ($M_{200}$) over the entire time span, while the right column zooms in on the period from $t=2\,\Gyr$ to $t=5\,\Gyr$.
 The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$, corresponding to the separation between the high- and low-$\alpha$ sequences (as shown in Figure~\ref{fig:alpha}).
@@
 However, during the high- to low-$\alpha$ transition, the virial mass remains consistent with a Milky Way progenitor, making this galaxy a suitable analog.
-There are no mergers related to the earlier quiescent period around $t\sim3.2\,\Gyr$, as no major mass jumps are observed during this time.
+There are no mergers related to the earlier quiescent period around $t\sim3.2\,\Gyr$ (no major mass jumps are observed during this time), implying the AGN activity is not merger-driven.
 The lower right panel shows the lack of mergers in more detail during the period between $t=2$ and $5\,\Gyr$.
 
-\subsection{Sequence of Events}\label{ssec:sequence_of_events}
+\subsection{Bar-Driven Quenching}\label{ssec:sequence_of_events}
 \begin{figure*}
@@
 
-In order to gain a more intuitive sense of the events around the high- to low-$\alpha$ transition, we show surface density projections alongside key summary statistics of our galaxy in Figure~\ref{fig:seq}.
+We find that a quenching episode is driven by the formation of a bar contemperaneous with an increase in AGN activity, shown in Figure~\ref{fig:seq}.
 The upper panels show gas density, while the middle panels display stellar density.
@@
 
-\subsection{One-Zone Model}\label{ssec:onezone}
+\subsection{\alphaFe{} with Varying SFE}\label{ssec:onezone}
 
@@
 This $\alpha$-enhancement corresponds to a more rapid decline in \alphaFe{} over time at high redshifts.
-We demonstrate the physical motivation behind this $\alpha$-enhancement in Figure~\ref{fig:vice}.
+Here we show that the steeper \alphaFe{} evolution implied by this $\alpha$-enhancement of old stars can be physically justified as a boost to the SFE of dense gas.
 
@@
 That study presented an idealized simulation resembling the merger between the Milky Way and GSE, where the orbital parameters were varied slightly across a grid of 27 simulations.
-The results showed that simulations featuring a brief quiescent period due to the merger produced a bimodal abundance distribution.
-In this scenario, gas expulsion by AGN activity was identified as the driving force behind the quenching.
+The results showed that simulations featuring a brief quiescent period produced a bimodal abundance distribution.
+Two conditions for the bimodality to arise have to be met: (1) a declining \alphaFe{} with time (here done through our post-processing step, see Figure~\ref{fig:alpha}), and (2) a gap in SFR.
+In Paper~I, the gap in SFR was due to a merger, but here we argue it is due to the formation of a bar.
 
-Once the $\alpha$-enhancement post-processing has been done, the galaxy that we have studied in this work is consistent with the quiescent scenario proposed in Paper~I.
+The galaxy that we have studied in this work is consistent with the quiescent scenario proposed in Paper~I.
 The distribution of \MgFe{} with star particle age is a useful way to test this scenario, which we plot in the upper right panel of Figure~\ref{fig:alpha} in fixed bins of \FeH{} (each color is a different \FeH{} bin).
-The vertical dashed line in Figures~\ref{fig:alpha} and \ref{fig:history} marks the transition between the high- and low-$\alpha$ sequences.
-We place this transition at a lookback time of $10.6,\Gyr$, corresponding to a cosmic time of approximately $3.2,\Gyr$ or redshift $z\sim2.05$.
+The vertical dashed line at $z\sim2$ in Figures~\ref{fig:alpha} and \ref{fig:history} marks the transition between the high- and low-$\alpha$ sequences.
 \footnote{The transition between the high- and low-$\alpha$ sequences occurs approximately $1\,\Gyr$ before $z=1.5$, where the $\alpha$-enhancement begins.
-This, combined with the fact that not all of the subhalos in our sample display bimodalities (Appendix~\ref{app:rand_fig1}), shows that the $\alpha$-enhancement is not the direct cause of the bimodality.} Star particles formed before this transition show a steep decline in \MgFe{} over time, with a drop of approximately $0.3\,\dex$ in just $2\,\Gyr$.
-In contrast, the stars formed after the dashed line exhibit a much flatter trend, with no noticeable gradient in \MgFe{} for the next couple of Gyr.
-
-At the transition, we can see a gap in the $\FeH=-0.5$, $-0.25$, and $0\,\dex$ bins (orange, green, and red, respectively).
-The gap has a width of about $300\,\Myr$ in the $-0.5$ and $-0.25\,\dex$ bins, while it is more extended at about $750\,\Myr$ in the $0\,\dex$ bin.
-The age gap in each \FeH{} bin of Figure~\ref{fig:alpha} is contemperaneous with a minimum in the global SFR.
-We can see in the upper panel of Figure~\ref{fig:history} that this dashed line lies almost exactly at the point of a local minimum in the SFH.
-This minimum, which is $\sim3\,\Msunyr$, is 10--15$\times$ smaller than the maxima before and after it.
+This, combined with the fact that not all of the subhalos in our sample display bimodalities (Appendix~\ref{app:rand_fig1}), shows that the $\alpha$-enhancement is not the direct cause of the bimodality.} At the transition, there is a $\sim300\,\Myr$ quiescent period during which the SFR drops by a factor of $\sim10$ to $15$.
 
@@
 
-\subsection{Steepening of $\alpha$ Decline}\label{ssec:sfe}
-As described in Section~\ref{ssec:tng}, we applied a post-processing to the \MgFe{} of star particles in the TNG simulation.
-Specifically, for star particles formed before $z=1.5$, we added to their \MgFe{} a value of $0.1\times\left(t_{1.5}-t_{\textrm{form}}\right)$, where $t_{1.5}$ is the age of the universe at $z=1.5$ ($\sim4.3\,\Gyr$) and $t_{\textrm{form}}$ is the formation time.
-This post-processed subhalo is presented alongside the fiducial subhalo in the right and middle columns, respectively, of Figures~\ref{fig:fig1} and \ref{fig:alpha}.
+\subsection{Motivation for $\alpha$-Post Processing}\label{ssec:sfe}
+As described in Section~\ref{ssec:tng}, we applied a post-processing which increased the \MgFe{} of star particles at $z>1.5$ in a time-linear manner, discussed in Section~\ref{ssec:tng}.
+The post-processed subhalo is presented alongside the fiducial subhalo in the right and middle columns, respectively, of Figures~\ref{fig:fig1} and \ref{fig:alpha}.
 
 The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models.
-Isolating the cause of the ``incorrect''\footnote{Our case study of a single subhalo, selected in a non-reproducible manner, is hardly cause to firmly assert that the fiducial evolution in TNG50 is incorrect.} \MgFe{} vs.
-time evolution at high-$z$ is not straightforward nor, in our opinion, even possible.
+Isolating the cause of the potentially too shallow evolution of \MgFe{} vs.
+time at high-$z$ is not straightforward nor, in our opinion, even possible.
 However, we do offer one reasonable explanation: the SFE at high densities, more present at high-$z$, is too low.
@@
 
-\citet{2024arXiv240909121H} demonstrated that the pressure regulated feedback model of \citet{2022ApJ...936..137O} predicts higher SFRs of patches of gaseous disks in TNG50 than the fiducial model by up to an order of magnitude.
+The TNG model predicts depletion times at high gas surface densities ($\tau_{\textrm{dep}}\sim0.5-1\,\Gyr$ at $\Sigma_{\textrm{gas}} ~ 100-300\,\Msun/\pc^2$) which are a factor of $\sim2$--$3$ longer than derived for starburst galaxies at similar densities of $\tau_{\textrm{dep}}\sim30$--$300\,Myr$ assuming \citet{2013ARA&A..51..207B} X(CO) \citep[see][]{2019ApJ...872...16D,2021ApJ...908...61K,2024arXiv240909121H}.
 This is well within our needed factor of $\sim2$ to $5$ in the SFE (see Figure~\ref{fig:vice}).
@@
 Based on this burst, it is also reasonable to suspect that AGN activity is also responsible for the quiescent period in our galaxy.
-However, we argue that the cause of the localized spike in the BH accretion rate is not due to a merger but instead due to the formation/strengthening of a bar.
+However, we argued in Section~\ref{ssec:sequence_of_events} that the cause of the localized spike in the BH accretion rate is not due to a merger but instead due to the formation/strengthening of a bar.
 
-In Figure~\ref{fig:seq}, we combine a visual inspection of the gas (upper row) and stellar (middle row) surface densities with the evolution of three key quantites (lower plot): SFR, BH accretion rate, and bar strength in blue, orange, and red, respectively.
-These are shown for nine snapshots, from snapshot 27 to 35, corresponding to redshift $2.73$ to $1.82$ or cosmic time from $2.38\,\Gyr$ to $3.59\,\Gyr$.
-A vertical dashed line is included in the lower panel separating the formation of the low- and high-$\alpha$ sequence at an age of $10.6\,\Gyr$ (cosmic time $\sim3.2\,\Gyr$), as in Figures~\ref{fig:alpha} and \ref{fig:history}.
-
-As described in Section~\ref{ssec:sequence_of_events}, the bar strengthens and then the BH accretion rate spikes, all while the SFR of the galaxy declines.
-This is suggestive of the following causal sequence:
-\begin{enumerate}
-  \item a bar forms through an internal instability, which
-  \item drives a large amount of gas to the center of the galaxy, which
-  \item triggers a high BH accretion rate and quasar-mode thermal feedback, which
-  \item clears gas out of the galaxy leading to quiescence.
-\end{enumerate}
-This quiescent period then leads to the bimodality, as discussed in Section~\ref{ssec:bim_cause}.
-It is not possible to prove the causality of this sequence of events because of the sparse snapshot spacing in TNG50, and so this is left to future work.
-
-However, there is a significant body of theoretical and observational work in support of this picture.
+There is a significant body of theoretical and observational work in support of this picture.
 Bars and other non-axisymmetric features have long been argued to funnel gas into the centers of galaxies on theoretical grounds \citep{1989Natur.338...45S,2010MNRAS.407.1529H}.
@@
 Since barred galaxies preferentially host AGN, we therefore predict that barred galaxies would preferentially host $\alpha$-bimodalities.
-The GECKOS survey, which aims to constrain the $\alpha$-bimodality of edge-on galaxies using integral field spectroscopy at different altitudes, could test this \citep{2024IAUS..377...27V}.
+The GECKOS survey, which aims to constrain the $\alpha$-bimodality of a sample of edge-on galaxies, about half of which are barred, using integral field spectroscopy at different altitudes, could test this \citep[and J.
+v.~d.~Sande, private communication]{2024IAUS..377...27V}.
 On the other hand, the strength of a bar is not associated with the strength of the host AGN \citep[e.g.]{2022A&A...661A.105S}.
@@
 \section{Conclusions}\label{sec:conc}
-In this work, we examined a subhalo of interest in Illustris TNG50.
-This galaxy is at a Milky Way-progenitor mass at $z=1.5$.
+In this work, we examined a galaxy in Illustris TNG50 which is at a Milky Way-progenitor mass at $z=1.5$.
 After applying a post-processing step that increased the \MgFe{} of star particles formed before $z=1.5$, this subhalo hosts a strong bimodality in the plane of \MgFe{} and \FeH{}, shown in Figure~\ref{fig:fig1}.
@@
 
-This bimodality can be traced to an event that occurred at an age of $10.6\,\Gyr$, or cosmic time of $\sim3.2\,\Gyr$ ($z\sim2$).
-Shown as a vertical dashed line in Figure~\ref{fig:alpha}, star particles that form before this time are at high-\MgFe{}, while star particles that form after are at low-\MgFe{}.
-This time is associated with a global reduction in the SFR (Figure~\ref{fig:history}), which appears to be related to AGN activity induced by the formation of a bar (Figure~\ref{fig:seq}).
+The formation of the bimodality, when the galaxy transition from producing high- to low-\MgFe{} star particles (Figure~\ref{fig:alpha}), is coincident with a global supression of star formation (Figure~\ref{fig:history}).
+This suppression of star formation is preceded by the formation of a bar and subsequent AGN activity (Figure~\ref{fig:seq}).
 
@@
 \begin{acknowledgements}
+  We would like to thank Marc Pinsonneault and Jesse van de Sande for helpful discussions, and M. Piinsonneault for sharing early access to the APOKASC-3 dataset.
+
   This work has made use of data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
 Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
+
+  Funding for the Sloan Digital Sky 
+  Survey IV has been provided by the 
+  Alfred P. Sloan Foundation, the U.S. 
+  Department of Energy Office of 
+  Science, and the Participating 
+  Institutions.
+
+  SDSS-IV acknowledges support and 
+  resources from the Center for High 
+  Performance Computing  at the 
+  University of Utah. The SDSS 
+  website is www.sdss4.org.
+
+  SDSS-IV is managed by the 
+  Astrophysical Research Consortium 
+  for the Participating Institutions 
+  of the SDSS Collaboration including 
+  the Brazilian Participation Group, 
+  the Carnegie Institution for Science, 
+  Carnegie Mellon University, Center for 
+  Astrophysics | Harvard \& 
+  Smithsonian, the Chilean Participation 
+  Group, the French Participation Group, 
+  Instituto de Astrof\'isica de 
+  Canarias, The Johns Hopkins 
+  University, Kavli Institute for the 
+  Physics and Mathematics of the 
+  Universe (IPMU) / University of 
+  Tokyo, the Korean Participation Group, 
+  Lawrence Berkeley National Laboratory, 
+  Leibniz Institut f\"ur Astrophysik 
+  Potsdam (AIP),  Max-Planck-Institut 
+  f\"ur Astronomie (MPIA Heidelberg), 
+  Max-Planck-Institut f\"ur 
+  Astrophysik (MPA Garching), 
+  Max-Planck-Institut f\"ur 
+  Extraterrestrische Physik (MPE), 
+  National Astronomical Observatories of 
+  China, New Mexico State University, 
+  New York University, University of 
+  Notre Dame, Observat\'ario 
+  Nacional / MCTI, The Ohio State 
+  University, Pennsylvania State 
+  University, Shanghai 
+  Astronomical Observatory, United 
+  Kingdom Participation Group, 
+  Universidad Nacional Aut\'onoma 
+  de M\'exico, University of Arizona, 
+  University of Colorado Boulder, 
+  University of Oxford, University of 
+  Portsmouth, University of Utah, 
+  University of Virginia, University 
+  of Washington, University of 
+  Wisconsin, Vanderbilt University, 
+  and Yale University.
+
 \end{acknowledgements}
@@
 We first show this galaxy at $z=1.5$ in Figure~\ref{fig:app0}, and then show our random sample of 16.
+As discussed in the main text, three (172175, 178140, and 193025) display prominent bimodalities, indicating that bimodalities like the Milky Way's may not be uncommon in the entire simulation domain.
+All show more multimodal structure after the post-processing.
+The fact that bimodalities like in the main galaxy studied in this work (172175; Figure~\ref{fig:app0}) only appears in a few out of the 16 shown here indicates that the post-processing is not solely responsible for the bimodality.
 

### 2025-02-17 paper/ms.tex
Update for ApJv1

@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn,linenumbers]{aastex631}
 
@@
 
-\author{Vadim Semenov}
+\author{Vadim A. Semenov}
 \affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/392276.pdf}
+  \includegraphics[width=\textwidth]{392276.pdf}
   \caption{\textbf{When old stars are $\alpha$-enhanced, our galaxy from TNG displays a prominent bimodality.} The upper left panel shows the distribution in the \MgFe{}-\FeH{} plane of the Milky Way, demonstrating a clear bimodality (data selection given in text).
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/392276_alpha.pdf}
+  \includegraphics[width=\textwidth]{392276_alpha.pdf}
   \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs separated by quiescence in simulation.} The upper panels show \MgFe{} as a function of age for our subhalo in TNG.
@@
   \centering
-  \includegraphics[width=\columnwidth]{fig/392276_SFH_AGN_M200.pdf}
+  \includegraphics[width=\columnwidth]{392276_SFH_AGN_M200.pdf}
   \caption{\textbf{The evolutionary history of our TNG galaxy.} The left column shows the SFH, BH accretion rate, and virial mass ($M_{200}$) over the entire time span, while the right column zooms in on the period from $t=2\,\Gyr$ to $t=5\,\Gyr$.
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/alyssa.pdf}
+  \includegraphics[width=\textwidth]{alyssa.pdf}
   \caption{\textbf{Quiescence separating the high- and low-$\alpha$ sequences is preceded by AGN activity associated with bar formation.} Surface density projections of gas (top row) and star particles (middle row) in our galaxy across snapshots at different times during the high- to low-$\alpha$ transition.
@@
   \centering
-  \includegraphics[width=\columnwidth]{fig/mgfe_vice.pdf}
+  \includegraphics[width=\columnwidth]{mgfe_vice.pdf}
   \caption{\textbf{A higher star formation efficiency leads to a steeper decline in \MgFe{}.} In both panels, the lines show the time evolution of \MgFe{} in a simple one-zone chemical evolution model, described in Section~\ref{ssec:onezone_met}.
@@
 \begin{acknowledgements}
-  We would like to thank Marc Pinsonneault and Jesse van de Sande for helpful discussions, and M. Piinsonneault for sharing early access to the APOKASC-3 dataset.
+  We would like to thank Marc Pinsonneault and Jesse van de Sande for helpful discussions, and M.
+Pinsonneault for sharing early access to the APOKASC-3 dataset.
+AB would like to thank Todd Phillips for helpful discussions.
+
+  JWJ acknowledges support from a Carnegie Theoretical Astrophysics Center postdoctoral fellowship.
+Support for VS was provided by Harvard University through the Institute for Theory and Computation Fellowship.
+LH acknowledges support by the Simons Collaboration on ``Learning the Universe.''
 
@@
   \centering
-  \includegraphics[width=\columnwidth]{fig/obs_error.pdf}
+  \includegraphics[width=\columnwidth]{obs_error.pdf}
   \caption{The observational errors of the APOKASC-3 (left) and ASPCAP dataset (right).
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_172175.pdf}
+  \includegraphics[width=\textwidth]{app_172175.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for our galaxy of interest at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_163071.pdf}
+  \includegraphics[width=\textwidth]{app_163071.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_178140.pdf}
+  \includegraphics[width=\textwidth]{app_178140.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_179009.pdf}
+  \includegraphics[width=\textwidth]{app_179009.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_193025.pdf}
+  \includegraphics[width=\textwidth]{app_193025.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_196834.pdf}
+  \includegraphics[width=\textwidth]{app_196834.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_202467.pdf}
+  \includegraphics[width=\textwidth]{app_202467.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_208267.pdf}
+  \includegraphics[width=\textwidth]{app_208267.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_222555.pdf}
+  \includegraphics[width=\textwidth]{app_222555.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_235345.pdf}
+  \includegraphics[width=\textwidth]{app_235345.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_245661.pdf}
+  \includegraphics[width=\textwidth]{app_245661.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_254663.pdf}
+  \includegraphics[width=\textwidth]{app_254663.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_260347.pdf}
+  \includegraphics[width=\textwidth]{app_260347.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_265671.pdf}
+  \includegraphics[width=\textwidth]{app_265671.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_282632.pdf}
+  \includegraphics[width=\textwidth]{app_282632.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_287601.pdf}
+  \includegraphics[width=\textwidth]{app_287601.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
@@
   \centering
-  \includegraphics[width=\textwidth]{fig/app_292983.pdf}
+  \includegraphics[width=\textwidth]{app_292983.pdf}
   \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}

### 2025-02-18 paper/ms.tex
Update alpha and obs errors

@@
   \includegraphics[width=\textwidth]{392276_alpha.pdf}
-  \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs separated by quiescence in simulation.} The upper panels show \MgFe{} as a function of age for our subhalo in TNG.
+  \caption{\textbf{Bimodality in the abundance plane is linked to distinct epochs separated by quiescence in simulation.} The upper row shows \MgFe{} as a function of age for our subhalo in TNG.
 The colors indicate stellar populations at fixed values of \FeH{}, which are the same as in Figure~\ref{fig:fig1}.
@@
 The effect of the $\alpha$-enhancement is clear, as it separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$).
-The lower panels show on the left the Milky Way and on the center and right the data from TNG but with $12.5\%$ age errors and $0.01\,\dex$ errors in \MgFe{}.
-When the simulations are given these errors, we see that the before and after star particles smear such that the two populations significantly overlap in ages.
-In the $\alpha$-enhanced galaxy, two populations emerge in each bin which overlapped in the fiducial distribution.
-This feature more closely resembles the Milky Way, which displays such populations where the bimodality is strongest -- $\FeH=-0.5$ (blue) and $-0.25$ (orange).}
+\edit1{The middle row shows the same TNG and $\alpha$-enhanced TNG data, but with added uncertainties of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.} When given these errors, the before and after star particles smear such that the two populations significantly overlap in ages.
+\edit1{The lower row shows on the left the Milky Way data and on the right the same TNG data with artificial errors but subsampled to the same number of stars older than $5\,\Gyr$ as in the observations (because the simulation sample has almost no star particles younger than $5\,\Gyr$).
+The limited sample size of the observations makes a direct comparison difficult.}}
   \label{fig:alpha}
@@
 These panels show 2D histograms, with a logarithmic colormap normalized to the maximum of the plot.
-To prevent overlap, the values of \MgFe{} are given offsets of $0$, $-0.5$, $-1$, and $-1.5$, in order of increasing \FeH{}.
+To prevent overlap, the values of \MgFe{} are given offsets of $0$, $-0.5$, $-1$, and $-1.5\,\dex$, in order of increasing \FeH{}.
 
 In our simulated galaxy, there is an age gap at $\sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
-Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after.
+Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after, \edit1{even in the fiducial case}.
 In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly reduced \MgFe{} than stars which form a short time later.
 
-In the lower row, the left panel displays data from the Milky Way, while the middle and right panels show the fiducial and $\alpha$-enhanced galaxy simulations, respectively.
-Gaussian errors of $12.5\%$ in age and $0.01\,dex$ in \MgFe{} were introduced in the simulations which align with the observational uncertainties in the APOKASC-3 and APOGEE datasets (see Appendix~\ref{app:obs_err} for detailed plots of observational errors).
+\edit1{In the middle row, the center and right panels show the simulated galaxies with Gaussian errors of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}, aligning with the observational uncertainties in the APOKASC-3 and APOGEE datasets (see Appendix~\ref{app:obs_err}).
+The error in \MgFe{} is insignificant, but the age error ($1.25\,\Gyr$ at $10\,\Gyr$) significantly blurs the distribution, particularly across the dashed line that marks the transition between sequences.
+Despite this, the $\alpha$-enhanced galaxy still shows two distinct populations, although their ages now overlap more significantly.}
 
-While the error in \MgFe{} is insignificant, the age error ($1.25\,\Gyr$ at $10\,\Gyr$) blurs the distribution, particularly around the dashed line that marks the transition between sequences.
-Despite this, the $\alpha$-enhanced galaxy still shows two distinct populations, although their ages now overlap more significantly.
-
-The Milky Way distribution (lower left panel) exhibits some similarities to the $\alpha$-enhanced galaxy.
-Specifically, in the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively), there appear to be two populations that overlap in age but remain distinct in \MgFe{}.
-These are the bins where the bimodality is most pronounced (as seen in the upper left panel of Figure~\ref{fig:fig1}).
-In the Milky Way there also appears to be a population of $\alpha$-rich stars down to low ages (see discussion in Section~\ref{ssec:compare_obs}).
+\edit1{The lower row compares Milky Way data (left) with simulations of fiducial (middle) and $\alpha$-enhanced (right) galaxies.
+Here, the simulations have been subsampled to match the observed sample size of stars older than $5\,\Gyr$ in each metallicity bin.
+We match the sample size only to old stars because our simulated sample has almost no star particles younger than $5\,\Gyr$.
+When subsampled with observational errors, the $\FeH=-0.5$ bin in the simulation (orange right panel) very faintly shows a hint of two stacked distributions which might also be present in the $\FeH=-0.25$ bin in the data (orange left panel).
+The limited sample size makes it impossible to draw any strong conclusions.}
 
@@
 \subsection{Direct Comparison to Observations}\label{ssec:compare_obs}
-The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs.
-age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC-3 catalog.
-In the bins where the bimodality is strongest (blue and orange, $\FeH=-0.5$ and $-0.25$, respectively), we see that there is a sort of two tiered distribution with significant overlap in age.
-In the galaxy with age and abundance errors shown in the lower right panel, a similar distribution can be seen in all \FeH{} bins.
-An examination of the true distribution in the galaxy (upper right panel), we see that the two distributions are in fact very cleanly separated in age.
+\edit1{We attempted a direct comparison between our TNG galaxy and the Milky Way in the lower row of Figure~\ref{fig:alpha} (see Section~\ref{ssec:alpha_time}).
+In the simulations, the presence of the bimodality is obvious from a stacked distribution.
+However, this distribution is not obvious in the observations, primarily because the sample size of observations at old ages where the bimodality is present ($>5\,\Gyr$) is quite small.
+Nonetheless, the presence of a clean gap in stellar ages between the high- and low-$\alpha$ is completely washed out by the age uncertainties.}
 
@@
 This argument is the same as presented in Paper~I and is consistent with the one-zone chemical evolution models of \citet{2020MNRAS.498.1364J}.
-When observational errors are added to the subhalo's abundance vs.
-age distribution, we show that it is broadly consistent with the distribution observed in the Milky Way (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).
+\edit1{Because of observational errors in age, it is not possible to make a direct comparison between the simulated galaxy and datae (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).}
 
@@
 \section{Observational Errors}\label{app:obs_err}
-In Figure~\ref{fig:alpha}, we assumed observational errors of $12.5\%$ in age and $0.01\,\dex$ in \MgFe{}.
+\edit1{In Figure~\ref{fig:alpha}, we assumed observational errors of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.
 In Figure~\ref{fig:obs_err}, we plot the quoted observational errors of the APOKASC-3 (left) and ASPCAP (right) datasets, showing both \FeH{} and \MgFe{} (blue and orange, respectively).
-We show our $12.5\%$ age error and $0.01\,\dex$ abundance error assumptions as black lines.
-For the age error, we used the maximum of the upper and lower estimates from \citet{2018ApJS..239...32P}.
+We show our $12.5\%$ age error as a black line in the left panel.
+We take the age error to be the maximum of the upper and lower errors from \citet{2018ApJS..239...32P}.
+In the right panel, we show blue and orange vertical lines at $0.01$ and $0.015\,\dex$ for \FeH{} and \MgFe{}, respectively.
+These are approximately the 99th percentiles of each error distribution.
 As a dashed line we show our $25\%$ age error cut for stars plotted in Figure~\ref{fig:obs_err}.
-Our assumed errors are generally consistent with the observed.
-Our error in \MgFe{} is a bit smaller than in ASPCAP, but the age estimates are by far the more constraining of the two.
+Our assumed errors are generally consistent with the errors quoted in the dataset, with a conservative estimate for the abundance errors.}
 
@@
   \includegraphics[width=\columnwidth]{obs_error.pdf}
-  \caption{The observational errors of the APOKASC-3 (left) and ASPCAP dataset (right).
-We show, on the left, a line indicating a $12.5\%$ error in observed age and on the right a vertical line indicating a $0.01\,\dex$ error.
+  \caption{The observational errors of \edit1{astroseismic ages from APOKASC-3} (left) and \edit1{abundances from ASPCAP DR17} (right).
+We show, on the left, a line indicating a $12.5\%$ error in observed age and on the right a vertical line indicating a \edit1{$0.01$ and $0.015\,\dex$ error in \FeH{} and \MgFe{}, respectively}.
 On the left, a dashed line indicates the $25\%$ error cut used for inclusion in Figure~\ref{fig:alpha}.}

### 2025-02-18 paper/ms.tex
Update app fig

@@
 \edit1{The middle row shows the same TNG and $\alpha$-enhanced TNG data, but with added uncertainties of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.} When given these errors, the before and after star particles smear such that the two populations significantly overlap in ages.
-\edit1{The lower row shows on the left the Milky Way data and on the right the same TNG data with artificial errors but subsampled to the same number of stars older than $5\,\Gyr$ as in the observations (because the simulation sample has almost no star particles younger than $5\,\Gyr$).
+\edit1{There is a second population of stars linked to another gap at $\sim8\,\Gyr$, discussed in the text.
+The lower row shows on the left the Milky Way data and on the right the same TNG data with artificial errors but subsampled to the same number of stars older than $5\,\Gyr$ as in the observations (because the simulation sample has almost no star particles younger than $5\,\Gyr$).
 The limited sample size of the observations makes a direct comparison difficult.}}
@@
 Despite this, the $\alpha$-enhanced galaxy still shows two distinct populations, although their ages now overlap more significantly.}
+
+\edit1{The upper and middle row shows that there is a potential third population of star particles in the simulation, which is most visible in the $\FeH=-0.25$ and $0\,\dex$ bins (green and red, respectively).
+A minor gap in the upper panels is present at an age of $\sim8\,\Gyr$, which we discuss further in Section~\ref{ssec:evol}.}
 
@@
 In the span of a single snapshot (roughly $150\,\Myr$), the SFR increases from about $3\,\Msun/\textrm{yr}$ to $10\,\Msun/\textrm{yr}$.
+
+\edit1{There is also a more minor period of quiescence at a cosmic time of $\sim6\,\Gyr$, followed by a period of SF at a much lower rate.
+This is likely linked to the third population separated by an age gap at $\sim8\,\Gyr$ seen in Figure~\ref{fig:alpha}.}
 
@@
 A definitive account, difficult with the current simulation outputs because of its sparse snapshot spacing, requires further work.
+\edit1{We also delay to future work the cause of the secondary quiescence period at $\sim6\,\Gyr$, briefly discussed in Section~\ref{ssec:evol}.}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{app_172175.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for our galaxy of interest at $z=1.5$.}
+  \includegraphics[width=\textwidth]{app_392276.pdf}
+  \caption{The abundance plane made in a manner similar to Figure~\ref{fig:fig1}. We show }
   \label{fig:app0}
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_163071.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app1}
-\end{figure*}
+\figsetstart
+\figsetnum{7}
+\figsettitle{Abundance plane for a random subset of sample galaxies in this work.}
+\figsetgrpstart
+\figsetgrpnum{7.1}
+\figsetgrptitle{Abundance plane for subhalo 392276.}
+\figsetplot{app_172175.pdf}
+\figsetgrpnote{Abundance plane for subhalo 392276.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.1}
+\figsetgrptitle{Abundance plane for subhalo 172175.}
+\figsetplot{app_172175.pdf}
+\figsetgrpnote{Abundance plane for subhalo 172175.}
+\figsetgrpend
+\figsetend
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_178140.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app2}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_2.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app1}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_179009.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app3}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_10.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app2}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_193025.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app4}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_143882.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app3}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_196834.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app5}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_167392.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app4}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_202467.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app6}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_289388.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app5}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_208267.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app7}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_300903.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app6}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_222555.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app8}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_348901.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app7}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_235345.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app9}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_398784.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app8}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_245661.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app10}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_404818.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app9}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_254663.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app11}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_425719.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app10}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_260347.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app12}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_439099.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app11}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_265671.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app13}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_465255.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app12}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_282632.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app14}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_494709.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app13}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_287601.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app15}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_510273.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app14}
+% \end{figure*}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=\textwidth]{app_292983.pdf}
-  \caption{The same as Figure~\ref{fig:fig1}, but for a random subhalo from our catalog at $z=1.5$.}
-  \label{fig:app16}
-\end{figure*}
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_547293.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app15}
+% \end{figure*}
+
+% \begin{figure*}
+%   \centering
+%   \includegraphics[width=\textwidth]{app_576516.pdf}
+%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+%   \label{fig:app16}
+% \end{figure*}
 

### 2025-02-18 paper/ms.tex
Update appendix figs

@@
 \section{Random Selection of Subhalos}\label{app:rand_fig1}
-In Figures~\ref{fig:app0} to \ref{fig:app16}, we show a version of Figure~\ref{fig:fig1} but for a random selection of subhalos from our broader sample of 168 Milky Way-progenitors at $z=1.5$ in TNG50.
-It is from this sample that we selected our galaxy of interest.
-We first show this galaxy at $z=1.5$ in Figure~\ref{fig:app0}, and then show our random sample of 16.
-As discussed in the main text, three (172175, 178140, and 193025) display prominent bimodalities, indicating that bimodalities like the Milky Way's may not be uncommon in the entire simulation domain.
-All show more multimodal structure after the post-processing.
-The fact that bimodalities like in the main galaxy studied in this work (172175; Figure~\ref{fig:app0}) only appears in a few out of the 16 shown here indicates that the post-processing is not solely responsible for the bimodality.
+\edit1{In Figure~\ref{fig:app0}, we show the abundance plane of our fiducial galaxy at $z=0$.
+This reproduces the middle column of Figure~\ref{fig:fig1}.
+We also show the effect of our $\alpha$-enhancement procedure on this distribution when applied, from left to right, at redshifts of $1$, $1.5$, and $2$.
+(The $z=1.5$ column reproduces the right column of Figure~\ref{fig:fig1}).
+Qualitatively, the time at which the $\alpha$-enhancement is applied does not alter whether substructure arises in this plane.
+However, when it is applied at lower $z$, the peaks between modes do appear to be slightly further apart.}
+
+\edit1{We show the same figure but with an additional random selection of 16 galaxies in the Milky Way-progenitor mass sample as a figure set (17 images), which is available in the online journal.
+Six additional galaxies (143882, 167392, 348901, 425719, 439099, and 465255) display bimodalities, though none as prominent as the main galaxy studied in this work.
+Some substructure is present in many galaxies.
+In general, the $\alpha$-enhancement increases the strength of substructure in the abundance planes.
+The fact that bimodalities like in the main galaxy studied in this work do not universally appear in $\alpha$-enhanced galaxies indicates that the $\alpha$-enhancement is not solely responsible for the bimodality.}
+
+\edit1{The timing of the $\alpha$-enhancement does not have a major effect on our fiducial galaxy (Figure~\ref{fig:app0}).
+However, for some (e.g., the green $\FeH=-0.25$ bin in 439099), structure arises only when the $\alpha$-enhancement is applied at sufficiently low redshift.
+We interpret this as the presence of some substructure inducing activity between $z=1$ and 2.}
 
@@
   \includegraphics[width=\textwidth]{app_392276.pdf}
-  \caption{The abundance plane made in a manner similar to Figure~\ref{fig:fig1}. We show }
+  \caption{\edit1{Abundance plane of the fiducial galaxy at $z=0$ and the effects of $\alpha$-enhancement applied at different redshifts.
+The leftmost panel shows the fiducial galaxy without enhancement, reproducing the middle column of Figure~\ref{fig:fig1}.
+The subsequent panels from left to right show the results of applying $\alpha$-enhancement at redshifts of 1, 1.5, and 2, respectively.
+The $z=1.5$ column reproduces the right column of Figure~\ref{fig:fig1}.
+The presence of substructure in the abundance plane is consistent across different application times of $\alpha$-enhancement, though applying it at lower redshifts appears to slightly increase the separation between modal peaks.
+This figure is part of a set of 17 images available in the online journal, showing similar plots for 16 additional galaxies from our Milky Way-progenitor mass sample.
+The varied responses to $\alpha$-enhancement across the sample, with only six additional galaxies (143882, 167392, 348901, 425719, 439099, and 465255) displaying bimodalities, suggest that while $\alpha$-enhancement generally increases substructure, it is not solely responsible for creating bimodalities in abundance planes.}}
   \label{fig:app0}
@@
 \figsetnum{7}
-\figsettitle{Abundance plane for a random subset of sample galaxies in this work.}
+\figsettitle{Abundance plane for a random subset of galaxies in our Milky Way-progenitor mass sample, with and without $\alpha$-enhancement.}
 \figsetgrpstart
 \figsetgrpnum{7.1}
-\figsetgrptitle{Abundance plane for subhalo 392276.}
-\figsetplot{app_172175.pdf}
+\figsetgrptitle{Subhalo 392276.}
+\figsetplot{app_392276.pdf}
 \figsetgrpnote{Abundance plane for subhalo 392276.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.1}
-\figsetgrptitle{Abundance plane for subhalo 172175.}
-\figsetplot{app_172175.pdf}
-\figsetgrpnote{Abundance plane for subhalo 172175.}
+\figsetgrpnum{7.2}
+\figsetgrptitle{Subhalo 2.}
+\figsetplot{app_2.pdf}
+\figsetgrpnote{Abundance plane for subhalo 2.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.3}
+\figsetgrptitle{Subhalo 10.}
+\figsetplot{app_10.pdf}
+\figsetgrpnote{Abundance plane for subhalo 10.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.4}
+\figsetgrptitle{Subhalo 143882.}
+\figsetplot{app_143882.pdf}
+\figsetgrpnote{Abundance plane for subhalo 143882.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.5}
+\figsetgrptitle{Subhalo 167392.}
+\figsetplot{app_167392.pdf}
+\figsetgrpnote{Abundance plane for subhalo 167392.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.6}
+\figsetgrptitle{Subhalo 289388.}
+\figsetplot{app_289388.pdf}
+\figsetgrpnote{Abundance plane for subhalo 289388.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.7}
+\figsetgrptitle{Subhalo 300903.}
+\figsetplot{app_300903.pdf}
+\figsetgrpnote{Abundance plane for subhalo 300903.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.8}
+\figsetgrptitle{Subhalo 348901.}
+\figsetplot{app_348901.pdf}
+\figsetgrpnote{Abundance plane for subhalo 348901.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.9}
+\figsetgrptitle{Subhalo 398784.}
+\figsetplot{app_398784.pdf}
+\figsetgrpnote{Abundance plane for subhalo 398784.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.10}
+\figsetgrptitle{Subhalo 404818.}
+\figsetplot{app_404818.pdf}
+\figsetgrpnote{Abundance plane for subhalo 404818.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.11}
+\figsetgrptitle{Subhalo 425719.}
+\figsetplot{app_425719.pdf}
+\figsetgrpnote{Abundance plane for subhalo 425719.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.12}
+\figsetgrptitle{Subhalo 439099.}
+\figsetplot{app_439099.pdf}
+\figsetgrpnote{Abundance plane for subhalo 439099.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.13}
+\figsetgrptitle{Subhalo 465255.}
+\figsetplot{app_465255.pdf}
+\figsetgrpnote{Abundance plane for subhalo 465255.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.14}
+\figsetgrptitle{Subhalo 494709.}
+\figsetplot{app_494709.pdf}
+\figsetgrpnote{Abundance plane for subhalo 494709.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.15}
+\figsetgrptitle{Subhalo 510273.}
+\figsetplot{app_510273.pdf}
+\figsetgrpnote{Abundance plane for subhalo 510273.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.16}
+\figsetgrptitle{Subhalo 547293.}
+\figsetplot{app_547293.pdf}
+\figsetgrpnote{Abundance plane for subhalo 547293.}
+\figsetgrpend
+\figsetgrpstart
+\figsetgrpnum{7.17å}
+\figsetgrptitle{Subhalo 576516.}
+\figsetplot{app_576516.pdf}
+\figsetgrpnote{Abundance plane for subhalo 576516.}
 \figsetgrpend
@@
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_2.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app1}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_2.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app1}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_10.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app2}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_10.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app2}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_143882.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app3}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_143882.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app3}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_167392.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app4}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_167392.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app4}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_289388.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app5}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_289388.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app5}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_300903.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app6}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_300903.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app6}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_348901.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app7}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_348901.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app7}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_398784.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app8}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_398784.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app8}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_404818.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app9}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_404818.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app9}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_425719.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app10}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_425719.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app10}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_439099.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app11}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_439099.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app11}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_465255.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app12}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_465255.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app12}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_494709.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app13}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_494709.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app13}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_510273.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app14}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_510273.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app14}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_547293.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app15}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_547293.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app15}
+\end{figure*}
 
-% \begin{figure*}
-%   \centering
-%   \includegraphics[width=\textwidth]{app_576516.pdf}
-%   \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
-%   \label{fig:app16}
-% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=\textwidth]{app_576516.pdf}
+  \caption{The same as Figure~\ref{fig:app0}, but for a random galaxy from our initial catalog.}
+  \label{fig:app16}
+\end{figure*}
 

### 2025-02-18 paper/ms.tex
Small adjustment for appendix

@@
 
-We show the abundance distributions of 16 random subhalos from our $z=1.5$ catalog, and the subhalo we selected, in Appendix~\ref{app:rand_fig1}.
+We show the abundance distributions of 16 random subhalos from our \edit1{Milky Way-progenitor mass} catalog, and the subhalo we selected, \edit1{at $z=0$} in Appendix~\ref{app:rand_fig1}.
 Of these subhalos, some structure is present, but none have a strong bimodality as seen in the Milky Way.
-After the $\alpha$-enhancement, a few have strongly bimodal features: 172175, 178140, 193025.
-It is worth noting that the post-processing is not in itself responsible for the emergence of bimodality, as it only does so for a fraction of the galaxies shown in Appendix~\ref{app:rand_fig1}.
+\edit1{After the $\alpha$-enhancement, six of the additional galaxies shown seem to have bimodal features: 143882, 167392, 348901, 425719, 439099, and 465255.
+However, none are as prominent as the fiducial galaxy (392276).} It is worth noting that the post-processing is not in itself responsible for the emergence of bimodality, as it only does so for a fraction of the galaxies shown in Appendix~\ref{app:rand_fig1}.
 Furthermore, if a galaxy had \alphaFe{} slowly and continuously decrease with time, then our $\alpha$-enhancement would not give rise to a bimodality since it is also a continuous adjustment.
+\edit1{Appendix~\ref{app:rand_fig1} also shows the effect of choosing a different redshift at which to apply the enhancement ($z=1$, 1.5, and 2), which does not qualitatively change the bimodal structure in our fiducial galaxy.}
 

### 2025-02-18 paper/ms.tex
Clarify kinematic vs chemical disks

@@
 Enrichment of iron-peak elements is primarily through Type~Ia and Type~II supernovae (SNe), whereas enrichment of $\alpha$-elements is primarily only through Type~II SNe.
-In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences as shown in the upper left panel of Figure~\ref{fig:fig1} \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}.
+
+The bimodality inherits a long history of attempts to decompose the disk dating back to \citet{1983MNRAS.202.1025G}, who showed that the vertical distribution of stars is well-fit by a double exponential.
+This led to a separation based on kinematics between the ``thin'' and ``thick'' disk.
+It was later shown that the thick disk is more $\alpha$-enhanced than the thin disk \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R}.
+However, it was not until more recently that it became obvious there is a clean separation between two sequences in the abundance plane, i.e., the $\alpha$-rich and $\alpha$-door disk \citep{2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}, also shown in the upper left panel of Figure~\ref{fig:fig1}.
 The Milky Way is the only galaxy for which such a structure has been definitively shown to exist.\footnote{Note claims of a detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}
@@
 Second, the bimodality is generated through gas infall scenarios, either from specific gas accretion episodes from the intergalactic medium \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}, or through a more self-consistent collapse sequence of the circumgalactic medium driven through feedback \citep{2021MNRAS.501.5176K}.
-Third and finally, the bimodality is generated through a merger process, either by enhancing the star formation rate (SFR) of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
+\edit1{Third and finally, the bimodality is generated through a merger process, either by enhancing the star formation rate (SFR) of the Galaxy \citep{2018MNRAS.474.3629G}}\footnote{\edit1{\citet{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} also explored the $\alpha$-enhancement of the thick disk resulting from gas-rich mergers.
+However, they did not explore the arising of a clean separation purely in chemistry.}} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
 Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports the merger-related scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.

### 2025-02-19 paper/ms.tex
Fix Brook et al citations and add Lu/Ratcliffe citations

@@
 However, they did not explore the arising of a clean separation purely in chemistry.}} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
-Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports the merger-related scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
+
+\edit1{The merger hypothesis is supported by strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports the merger-related scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
+In deriving stellar birth radii from assuming a linear relation between \FeH{} and radius with a time-evolving slope, \citet{2024MNRAS.535..392L} argued that the bimodality resulted from a steepening of the metallicity gradient at the time of the GSE merger \citep[see also][]{2023MNRAS.525.2208R}.
+This provides further evidence that the bimodality formed around the same time as the GSE merger, although the case for a causal connection is less clear.}
 

### 2025-02-19 paper/ms.tex
Add more bar formation timing citations throughout

@@
 In deriving stellar birth radii from assuming a linear relation between \FeH{} and radius with a time-evolving slope, \citet{2024MNRAS.535..392L} argued that the bimodality resulted from a steepening of the metallicity gradient at the time of the GSE merger \citep[see also][]{2023MNRAS.525.2208R}.
-This provides further evidence that the bimodality formed around the same time as the GSE merger, although the case for a causal connection is less clear.}
+This provides further evidence that the bimodality formed around the same time as the GSE merger, although the case for a causal connection is less clear -- the bar seemed to form around the same time \citep[e.g][]{2019MNRAS.490.4740B,2024MNRAS.530.2972S}.}
 
@@
 
+\edit1{Note that in the Milky Way the bar is estimated to have formed approximately $8\,\Gyr$ ago \citep{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, coinciding with the epoch when the bimodality is observed to emerge \citep{2013A&A...560A.109H,2023MNRAS.525.2208R,2024MNRAS.535..392L}.}
+
 \subsection{\alphaFe{} with Varying SFE}\label{ssec:onezone}
@@
 
-\subsection{Motivation for $\alpha$-Post Processing}\label{ssec:sfe}
+\subsection{Motivation for $\alpha$ Post-processing}\label{ssec:sfe}
 As described in Section~\ref{ssec:tng}, we applied a post-processing which increased the \MgFe{} of star particles at $z>1.5$ in a time-linear manner, discussed in Section~\ref{ssec:tng}.
@@
 However, we argued in Section~\ref{ssec:sequence_of_events} that the cause of the localized spike in the BH accretion rate is not due to a merger but instead due to the formation/strengthening of a bar.
+\edit1{This connection is further supported by estimates that the Milky Way's bar formed $\sim8\,\Gyr$ ago \citep[e.g.,][]{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, roughly concurrent with the formation of the bimodality \citep{2013A&A...560A.109H,2023MNRAS.525.2208R,2024MNRAS.535..392L}.}
 
@@
 This suppression of star formation is preceded by the formation of a bar and subsequent AGN activity (Figure~\ref{fig:seq}).
+\edit1{This scenario is plausible for the Milky Way, as recent estimates indicate that the bar formed around $8\,\Gyr$ ago \citep{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, coinciding with the onset of the bimodality.}
 

### 2025-02-19 paper/ms.tex
Change from global to Z-dependent SFR

@@
 \newcommand{\Msunyr}{\ensuremath{\Msun/\textrm{yr}}}
+\newcommand{\Msunyrdex}{\ensuremath{\Msun/\textrm{yr}/\textrm{dex}}}
 \newcommand{\Atmax}{\ensuremath{A_{2,\textrm{max}}}}
@@
 
-In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history (an observational claim with a longer period of quiescence was made in \citet{2016A&A...589A..66H}).
-This period has two effects.
-First, the reduced SFR lowers the number of $\alpha$-producing Type~II SNe relative to Type~Ia\footnote{These SNe occur on different timescales (10s of Myr after star formation for Type~II, as compared to 100s of Myr to Gyrs for Type~Ia), so if the SFR drops, the number of Type~II SNe drops faster than Type~Ia.}, causing a sharp decline in the \alphaFe{} ratio in the star-forming gas.
-Second, the lower SFR results in fewer stars forming in the intermediate region between the high- and low-$\alpha$ sequences, reducing the occurrence of this transitional population in present-day observations.
-The combination of these two effects creates the valley between the high- and low-$\alpha$ sequences.
-This mechanism resembles two-phase infall models that incorporate a temporary halt in star formation \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period in Paper~I is much shorter.
+In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history \edit1{in a narrow metallicity bin, assuming the gas-phase \alphaFe{} is declining sufficiently rapidly.}\footnote{An observational claim with a longer period of global quiescence was made in \citet{2016A&A...589A..66H}.} The lower SFR results in fewer stars forming in the intermediate region between the high- and low-$\alpha$ sequences, reducing the occurrence of this transitional population in present-day observations.
+\edit1{A global quiescent period is sufficient for producing such gaps in the metallicity-dependent SFR, though it is not necessary.} This mechanism resembles two-phase infall models that incorporate a temporary halt in star formation \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period in Paper~I is much shorter.
 
@@
 
-We select subhalo 172175 (the Subfind ID at snapshot 40) for its resemblance to the Milky Way.
+\edit1{We used \texttt{FOF} and \texttt{SUBFIND} in order to identify substructure \citep{2005Natur.435..629S,2009MNRAS.399..497D}.} We select subhalo 172175 (the \texttt{SUBFIND} ID at snapshot 40) for its resemblance to the Milky Way.
 We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
@@
 
-\subsection{Observations}\label{ssec:obs}
+\subsection{Observational Data}\label{ssec:obs}
 We make use of two observational data sets.
@@
 The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$ from the high- to low-$\alpha$ sequences, as in Figure~\ref{fig:alpha}.
-The upper panel in the left column shows the the SFR (computed for all gas cells in the galaxy).
+The upper panel in the left column shows the the SFR (computed for all gas cells in the \edit1{\texttt{SUBFIND} subhalo}).
 There are two peaks at $t\sim2.5\,\Gyr$ and $t\sim4.5\,\Gyr$ with maximum values of $50\,\Msun/\textrm{yr}$ and $30\,\Msun/\textrm{yr}$, respectively.
@@
 The lower right panel shows the lack of mergers in more detail during the period between $t=2$ and $5\,\Gyr$.
+
+\edit1{As discussed in Paper~I, the key to generating an $\alpha$-bimodality is halting star formation within specific metallicity ranges.
+A global quiescent period is a sufficient but not necessary condition for the formation of such gaps.
+To illustrate this point, we present Figure~\ref{fig:zSFH}, which compares the global SFH in black with the SFH in narrow metallicity bins, color-coded to match the bins shown in Figure~\ref{fig:fig1}.
+This plot uses the $z=0$ distribution of star particle formation times, resulting in minor differences from the SFH shown in Figure~\ref{fig:history}.
+Notably, we observe a significant drop in the SFR within these metallicity bins, lasting up to $\sim1\,\Gyr$.
+However, because the timing of these metallicity-dependent gaps differs, the total SFR never falls below $\sim10\,\Msunyr$.}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{392276_zSFH.pdf}
+  \caption{\edit1{Global star formation history (black) compared with the star formation history in narrow metallicity bins, color-coded as in Figure~\ref{fig:fig1}.
+This plot demonstrates that the key condition for generating an $\alpha$-bimodality, the cessation of star formation in specific metallicity ranges, is satisfied.
+The metallicity-dependent SFR drops nearly to zero in every bin for periods extending up to $\sim1\,\Gyr$.
+The timing and duration of metallicity-dependent gaps can vary, preventing the total SFR from falling below $\sim10\,\Msunyr$.}}
+  \label{fig:zSFH}
+\end{figure}
 
@@
 Figure~\ref{fig:history} shows that it reaches its second maximum of $30.9\,\Msunyr$ at $4.5\,\Gyr$.
+\edit1{We show in Figure~\ref{fig:zSFH} that the global SF suppression is coincident with a much more dramatic metallicity dependent SF gap, with the SFR dropping nearly to $0\,\Msunyrdex$ in several bins.}
 \end{enumerate}
@@
 The results showed that simulations featuring a brief quiescent period produced a bimodal abundance distribution.
-Two conditions for the bimodality to arise have to be met: (1) a declining \alphaFe{} with time (here done through our post-processing step, see Figure~\ref{fig:alpha}), and (2) a gap in SFR.
+Two conditions for the bimodality to arise have to be met: (1) a declining \alphaFe{} with time (here done through our post-processing step, see Figure~\ref{fig:alpha}), and (2) a gap in \edit1{the metallicity-dependent} SFR.
 In Paper~I, the gap in SFR was due to a merger, but here we argue it is due to the formation of a bar.
@@
 
-During this period of suppressed SF, we argue that the lack of enrichment of Type~II relative to Type~Ia SNe leads to a lower rate of Mg production.
-The typical lifetime of a Type~II SN progenitor in this model is $\sim40\,\Myr$ \citep{2018MNRAS.473.4077P}, and so the hundreds of Myr of suppressed SF is short enough to restrict the production of $\alpha$-elements.
-Therefore, \MgFe{} rapidly declines.
-This, combined with a lack of SF in the first place, leads to a scarcity of star particles in the intermediate region between the high- and low-$\alpha$ sequences.
-A more in-depth explanation is given in Section~4.1 in Paper~I.
+\edit1{This global quiescent period is symptomatic of a more dramatic reduction in the star formation rate in narrow metallicity bins, which almost entirely vanishes (Figure~\ref{fig:zSFH}).
+As we showed in Paper~I, it is the metallicity-dependent quiescence in the presence of a declining gas-phase \MgFe{} -- not global quiescence -- that leads to an $\alpha$-bimodality.
+In the fiducial TNG model, the \MgFe{} reduction with time is not rapid enough, leading to the post-processing discussed in Section~\ref{ssec:sfe}.
+In the real universe, a global quiescent period of a duration of $\sim300\,\Myr$ would lead to a reduction in enrichment from Type~II relative to Type~Ia SNe leads to a lower rate of Mg production.
+The typical lifetime of a Type~II SN progenitor in this model is $\sim40\,\Myr$ \citep{2018MNRAS.473.4077P}, and so the hundreds of Myr of suppressed SF would be short enough to restrict the production of $\alpha$-elements.}
 
@@
 The star particles which form directly after the dashed line when the SFR has just recovered have a slightly lower \MgFe{} than stars which form later on, by about $0.1$ to $0.2\,\dex$.
-This was also predicted in Figure~9 of Paper~I, where it was argued that during the period of suppressed star formation, the \alphaFe{} ratio of the star-forming gas drops sharply due to the reduced contribution of Type~II relative to Type~Ia SNe.
+\edit1{We argue that it is plausible that} during the period of suppressed star formation, the \alphaFe{} ratio of the star-forming gas drops sharply due to the reduced contribution of Type~II relative to Type~Ia SNe.
 Later, the \alphaFe{} of the gas will recover when the SFR also recovers, but there is a brief window when old, low-$\alpha$ stars can form.
@@
 In our galaxy here, there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
-Based on this burst, it is also reasonable to suspect that AGN activity is also responsible for the quiescent period in our galaxy.
+Based on this burst, it is also reasonable to suspect that AGN activity is also responsible for the quiescent period in our galaxy, \edit1{noting that the real cause of the formation of the $\alpha$-bimodality is a metallicity-dependent quiescent period (see Paper~I and Figure~\ref{fig:zSFH})}.
 However, we argued in Section~\ref{ssec:sequence_of_events} that the cause of the localized spike in the BH accretion rate is not due to a merger but instead due to the formation/strengthening of a bar.
@@
 
-The formation of the bimodality, when the galaxy transition from producing high- to low-\MgFe{} star particles (Figure~\ref{fig:alpha}), is coincident with a global supression of star formation (Figure~\ref{fig:history}).
+The formation of the bimodality, when the galaxy transitions from producing high- to low-\MgFe{} star particles (Figure~\ref{fig:alpha}), is coincident with \edit1{both a global and metallicity-dependent suppression of star formation (Figures~\ref{fig:history} and \ref{fig:zSFH})}.
 This suppression of star formation is preceded by the formation of a bar and subsequent AGN activity (Figure~\ref{fig:seq}).
@@
 
-We argue that the reduction in the SFR has two effects which lead to the $\alpha$-bimodality.
-First, a lower production of Mg relative to Fe is the natural result of a lack of Type~II relative to Type~Ia SNe.
-The latter remain high due to their longer timescales, expediting a drop in \MgFe{}.
-Second, the lack of SF means that stars at \MgFe{} intermediate between the high- and low-$\alpha$ sequences never form.
-This argument is the same as presented in Paper~I and is consistent with the one-zone chemical evolution models of \citet{2020MNRAS.498.1364J}.
-\edit1{Because of observational errors in age, it is not possible to make a direct comparison between the simulated galaxy and datae (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).}
+\edit1{The lack of star formation in a narrow metallicity bin in the presence of a decline in \MgFe{} naturally leads to a gap in the present-day distribution of \MgFe{} (see Paper~I).
+However, in the fiducial TNG  model, the decline in \MgFe{} is not rapid enough during the period of quiescence to produce an $\alpha$-bimodality.
+Our post-processing $\alpha$-enhancement artificially injects this declination.
+In the real universe, a global reduction in the SFR may expedite the drop in \MgFe{} since the number of Type~II relative to Type~Ia SNe would drop.}
 
@@
 Regardless of this scenario's relevance to the Milky Way, we also predict that the presence of a bar in external galaxies is correlated with the presence of an $\alpha$-bimodality.
+\edit1{Because of observational errors in age, it is not possible to make a direct comparison between the simulated galaxy and dataset (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).
+In the future, more numerous and precise age estimates of old, metal-poor stars may be able to distinguish the formation scenarios of the $\alpha$-bimodality.}
 
@@
 \figsetstart
-\figsetnum{7}
+\figsetnum{8}
 \figsettitle{Abundance plane for a random subset of galaxies in our Milky Way-progenitor mass sample, with and without $\alpha$-enhancement.}
 \figsetgrpstart
-\figsetgrpnum{7.1}
+\figsetgrpnum{8.1}
 \figsetgrptitle{Subhalo 392276.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.2}
+\figsetgrpnum{8.2}
 \figsetgrptitle{Subhalo 2.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.3}
+\figsetgrpnum{8.3}
 \figsetgrptitle{Subhalo 10.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.4}
+\figsetgrpnum{8.4}
 \figsetgrptitle{Subhalo 143882.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.5}
+\figsetgrpnum{8.5}
 \figsetgrptitle{Subhalo 167392.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.6}
+\figsetgrpnum{8.6}
 \figsetgrptitle{Subhalo 289388.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.7}
+\figsetgrpnum{8.7}
 \figsetgrptitle{Subhalo 300903.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.8}
+\figsetgrpnum{8.8}
 \figsetgrptitle{Subhalo 348901.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.9}
+\figsetgrpnum{8.9}
 \figsetgrptitle{Subhalo 398784.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.10}
+\figsetgrpnum{8.10}
 \figsetgrptitle{Subhalo 404818.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.11}
+\figsetgrpnum{8.11}
 \figsetgrptitle{Subhalo 425719.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.12}
+\figsetgrpnum{8.12}
 \figsetgrptitle{Subhalo 439099.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.13}
+\figsetgrpnum{8.13}
 \figsetgrptitle{Subhalo 465255.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.14}
+\figsetgrpnum{8.14}
 \figsetgrptitle{Subhalo 494709.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.15}
+\figsetgrpnum{8.15}
 \figsetgrptitle{Subhalo 510273.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.16}
+\figsetgrpnum{8.16}
 \figsetgrptitle{Subhalo 547293.}
@@
 \figsetgrpstart
-\figsetgrpnum{7.17å}
+\figsetgrpnum{8.17}
 \figsetgrptitle{Subhalo 576516.}

### 2025-02-20 paper/ms.tex
Bow down to AI overlords
Add thick disk papers

@@
 
-The bimodality inherits a long history of attempts to decompose the disk dating back to \citet{1983MNRAS.202.1025G}, who showed that the vertical distribution of stars is well-fit by a double exponential.
+\edit1{The bimodality inherits a long history of attempts to decompose the disk dating back to \citet{1983MNRAS.202.1025G}, who showed that the vertical distribution of stars is well-fit by a double exponential.
 This led to a separation based on kinematics between the ``thin'' and ``thick'' disk.
@@
 However, it was not until more recently that it became obvious there is a clean separation between two sequences in the abundance plane, i.e., the $\alpha$-rich and $\alpha$-door disk \citep{2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}, also shown in the upper left panel of Figure~\ref{fig:fig1}.
-The Milky Way is the only galaxy for which such a structure has been definitively shown to exist.\footnote{Note claims of a detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}
+The Milky Way is the only galaxy for which such a structure has been definitively shown to exist.\footnote{Note claims of a detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}}
+
+\edit1{The distinction between a chemical and kinematic decomposition of the disk is illustrated by a population of low-$\alpha$ stars on vertically extended orbits in the outer disk \citep{2015ApJ...808..132H,2016ApJ...823...30B}.
+This is thought to arise from flaring associated with radial migration \citep{2015ApJ...804L...9M,2016ApJ...831..139M}, or from other processes, including misaligned gas accretion and minor mergers \citep{2010MNRAS.408..783R,2009MNRAS.396..696S}.
+Nonetheless, in the outer disk the kinematically-defined thick disk has contributions from both the chemically defined high- and low-$\alpha$ sequences.}
 
@@
 
+\edit1{We acknowledge the use of OpenAI’s ChatGPT and Anthropic's Claude for assistance in editing this manuscript for clarity and conciseness and in generating small analysis scripts and code snippets.}
+
 \end{acknowledgements}

### 2025-02-20 paper/ms.tex
Thank referee and update yml
Fix typos

@@
 The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive satellite (Gaia-Sausage-Enceladus) at $z\sim2$.
-However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality.
+However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalence, morphology, and mechanism behind multimodality.
 We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes sequential phases of starburst, brief quiescence, and then rejuvenation.
@@
 The upper panels show the 2D distribution in the space of \MgFe{}-\FeH{}.
-We have applied the standard \texttt{scipy} implementation of a gaussian kernel density estimator to a Cartesian grid of points.
+We have applied the standard \texttt{scipy} implementation of a Gaussian kernel density estimator to a Cartesian grid of points.
 For each panel, we normalize so that the integral of the distribution is unity.
@@
 The middle right panel shows the period between $t=2$ and $5\,\Gyr$.
-We can see that the decline in the galaxy's SFR is contemperaneous with this increase in the BH accretion rate.
+We can see that the decline in the galaxy's SFR is contemporaneous with this increase in the BH accretion rate.
 
@@
 
-We find that a quenching episode is driven by the formation of a bar contemperaneous with an increase in AGN activity, shown in Figure~\ref{fig:seq}.
+We find that a quenching episode is driven by the formation of a bar contemporaneous with an increase in AGN activity, shown in Figure~\ref{fig:seq}.
 The upper panels show gas density, while the middle panels display stellar density.
@@
 \begin{acknowledgements}
-  We would like to thank Marc Pinsonneault and Jesse van de Sande for helpful discussions, and M.
+  \edit1{We would like to thank the referee for a thoughtful and helpful report.} We would like to thank Marc Pinsonneault and Jesse van de Sande for helpful discussions, and M.
 Pinsonneault for sharing early access to the APOKASC-3 dataset.

### 2025-02-28 paper/ms.tex
Update Micic citation

@@
 In observations, barred galaxies preferentially host AGN in star-forming galaxies \citep{2012ApJS..198....4O,2022A&A...661A.105S}.\footnote{\citet{2022A&A...668L...3L} studied a galaxy from TNG100 in which a merger induced AGN activity that ejected gas from its center.
-A bar then formed out of the gas-poor disk.} Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.
+A bar then formed out of the gas-poor disk.} Furthermore, at high-$z$, the AGN mechanism is thought to be responsible for quenching \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024ApJ...968L..21M,2024Natur.630...54B}.
 

### 2025-03-04 paper/ms.tex
Vadim edits

@@
 It was later shown that the thick disk is more $\alpha$-enhanced than the thin disk \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R}.
-However, it was not until more recently that it became obvious there is a clean separation between two sequences in the abundance plane, i.e., the $\alpha$-rich and $\alpha$-door disk \citep{2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}, also shown in the upper left panel of Figure~\ref{fig:fig1}.
+However, it was not until more recently that it became obvious there is a clean separation between two sequences in the abundance plane, i.e., the $\alpha$-rich and $\alpha$-poor disk \citep{2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}, also shown in the upper left panel of Figure~\ref{fig:fig1}.
 The Milky Way is the only galaxy for which such a structure has been definitively shown to exist.\footnote{Note claims of a detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}}
@@
 This is thought to arise from flaring associated with radial migration \citep{2015ApJ...804L...9M,2016ApJ...831..139M}, or from other processes, including misaligned gas accretion and minor mergers \citep{2010MNRAS.408..783R,2009MNRAS.396..696S}.
-Nonetheless, in the outer disk the kinematically-defined thick disk has contributions from both the chemically defined high- and low-$\alpha$ sequences.}
+Nonetheless, in the outer disk, the kinematically-defined thick disk has contributions from both the chemically defined high- and low-$\alpha$ sequences.}
 
@@
 
-\edit1{The merger hypothesis is supported by strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports the merger-related scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
+\edit1{Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports the merger-related scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
 In deriving stellar birth radii from assuming a linear relation between \FeH{} and radius with a time-evolving slope, \citet{2024MNRAS.535..392L} argued that the bimodality resulted from a steepening of the metallicity gradient at the time of the GSE merger \citep[see also][]{2023MNRAS.525.2208R}.

### 2025-04-16 paper/ms.tex
Fix citation

@@
 \edit1{The distinction between a chemical and kinematic decomposition of the disk is illustrated by a population of low-$\alpha$ stars on vertically extended orbits in the outer disk \citep{2015ApJ...808..132H,2016ApJ...823...30B}.
-This is thought to arise from flaring associated with radial migration \citep{2015ApJ...804L...9M,2016ApJ...831..139M}, or from other processes, including misaligned gas accretion and minor mergers \citep{2010MNRAS.408..783R,2009MNRAS.396..696S}.
+This is thought to arise from \edit2{inside-out formation} \citep[\edit2{which predict and claim a negative age gradient at high altitude}]{2015ApJ...804L...9M,2016ApJ...831..139M}, or from other processes, including misaligned gas accretion and minor mergers \citep{2010MNRAS.408..783R,2009MNRAS.396..696S}.
 Nonetheless, in the outer disk, the kinematically-defined thick disk has contributions from both the chemically defined high- and low-$\alpha$ sequences.}

### 2025-07-23 paper/ms.tex
Update for arxiv

--- 2025-03-04 paper/ms.tex
@@
-\documentclass[twocolumn,linenumbers]{aastex631}
+\documentclass[twocolumn]{aastex631}
 
@@
 
-\edit1{The bimodality inherits a long history of attempts to decompose the disk dating back to \citet{1983MNRAS.202.1025G}, who showed that the vertical distribution of stars is well-fit by a double exponential.
+The bimodality inherits a long history of attempts to decompose the disk dating back to \citet{1983MNRAS.202.1025G}, who showed that the vertical distribution of stars is well-fit by a double exponential.
 This led to a separation based on kinematics between the ``thin'' and ``thick'' disk.
@@
 However, it was not until more recently that it became obvious there is a clean separation between two sequences in the abundance plane, i.e., the $\alpha$-rich and $\alpha$-poor disk \citep{2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}, also shown in the upper left panel of Figure~\ref{fig:fig1}.
-The Milky Way is the only galaxy for which such a structure has been definitively shown to exist.\footnote{Note claims of a detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}}
+The Milky Way is the only galaxy for which such a structure has been definitively shown to exist.\footnote{Note claims of a detection \citep{2023ApJ...956L..14K} and nondetection \citep{2024IAUS..377..115N} in M31.}
 
-\edit1{The distinction between a chemical and kinematic decomposition of the disk is illustrated by a population of low-$\alpha$ stars on vertically extended orbits in the outer disk \citep{2015ApJ...808..132H,2016ApJ...823...30B}.
-This is thought to arise from flaring associated with radial migration \citep{2015ApJ...804L...9M,2016ApJ...831..139M}, or from other processes, including misaligned gas accretion and minor mergers \citep{2010MNRAS.408..783R,2009MNRAS.396..696S}.
-Nonetheless, in the outer disk, the kinematically-defined thick disk has contributions from both the chemically defined high- and low-$\alpha$ sequences.}
+The distinction between a chemical and kinematic decomposition of the disk is illustrated by a population of low-$\alpha$ stars on vertically extended orbits in the outer disk \citep{2015ApJ...808..132H,2016ApJ...823...30B}.
+This is thought to arise from inside-out formation \citep[which predict and claim a negative age gradient at high altitude]{2015ApJ...804L...9M,2016ApJ...831..139M}, or from other processes, including misaligned gas accretion and minor mergers \citep{2010MNRAS.408..783R,2009MNRAS.396..696S}.
+Nonetheless, in the outer disk, the kinematically-defined thick disk has contributions from both the chemically defined high- and low-$\alpha$ sequences.
 
@@
 Second, the bimodality is generated through gas infall scenarios, either from specific gas accretion episodes from the intergalactic medium \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}, or through a more self-consistent collapse sequence of the circumgalactic medium driven through feedback \citep{2021MNRAS.501.5176K}.
-\edit1{Third and finally, the bimodality is generated through a merger process, either by enhancing the star formation rate (SFR) of the Galaxy \citep{2018MNRAS.474.3629G}}\footnote{\edit1{\citet{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} also explored the $\alpha$-enhancement of the thick disk resulting from gas-rich mergers.
-However, they did not explore the arising of a clean separation purely in chemistry.}} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
+Third and finally, the bimodality is generated through a merger process, either by enhancing the star formation rate (SFR) of the Galaxy \citep{2018MNRAS.474.3629G}\footnote{\citet{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} also explored the $\alpha$-enhancement of the thick disk resulting from gas-rich mergers.
+However, they did not explore the arising of a clean separation purely in chemistry.} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}.
 
-\edit1{Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports the merger-related scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
+Strong evidence that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports the merger-related scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N,2024ApJ...972..112C}.
 In deriving stellar birth radii from assuming a linear relation between \FeH{} and radius with a time-evolving slope, \citet{2024MNRAS.535..392L} argued that the bimodality resulted from a steepening of the metallicity gradient at the time of the GSE merger \citep[see also][]{2023MNRAS.525.2208R}.
-This provides further evidence that the bimodality formed around the same time as the GSE merger, although the case for a causal connection is less clear -- the bar seemed to form around the same time \citep[e.g][]{2019MNRAS.490.4740B,2024MNRAS.530.2972S}.}
+This provides further evidence that the bimodality formed around the same time as the GSE merger, although the case for a causal connection is less clear -- the bar seemed to form around the same time \citep[e.g][]{2019MNRAS.490.4740B,2024MNRAS.530.2972S}.
 
-In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history \edit1{in a narrow metallicity bin, assuming the gas-phase \alphaFe{} is declining sufficiently rapidly.}\footnote{An observational claim with a longer period of global quiescence was made in \citet{2016A&A...589A..66H}.} The lower SFR results in fewer stars forming in the intermediate region between the high- and low-$\alpha$ sequences, reducing the occurrence of this transitional population in present-day observations.
-\edit1{A global quiescent period is sufficient for producing such gaps in the metallicity-dependent SFR, though it is not necessary.} This mechanism resembles two-phase infall models that incorporate a temporary halt in star formation \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period in Paper~I is much shorter.
+In \citet{2024arXiv240707985B} (hereafter Paper~I), we proposed an alternate scenario for the formation of the bimodality, driven by a brief ($\sim300\,\Myr$) quiescent period in the Galaxy's history in a narrow metallicity bin, assuming the gas-phase \alphaFe{} is declining sufficiently rapidly.\footnote{An observational claim with a longer period of global quiescence was made in \citet{2016A&A...589A..66H}.} The lower SFR results in fewer stars forming in the intermediate region between the high- and low-$\alpha$ sequences, reducing the occurrence of this transitional population in present-day observations.
+A global quiescent period is sufficient for producing such gaps in the metallicity-dependent SFR, though it is not necessary.
+This mechanism resembles two-phase infall models that incorporate a temporary halt in star formation \citep[][and references therein]{2024arXiv240511025S}, though the quiescent period in Paper~I is much shorter.
 
@@
 
-We show the abundance distributions of 16 random subhalos from our \edit1{Milky Way-progenitor mass} catalog, and the subhalo we selected, \edit1{at $z=0$} in Appendix~\ref{app:rand_fig1}.
+We show the abundance distributions of 16 random subhalos from our Milky Way-progenitor mass catalog, and the subhalo we selected, at $z=0$ in Appendix~\ref{app:rand_fig1}.
 Of these subhalos, some structure is present, but none have a strong bimodality as seen in the Milky Way.
-\edit1{After the $\alpha$-enhancement, six of the additional galaxies shown seem to have bimodal features: 143882, 167392, 348901, 425719, 439099, and 465255.
-However, none are as prominent as the fiducial galaxy (392276).} It is worth noting that the post-processing is not in itself responsible for the emergence of bimodality, as it only does so for a fraction of the galaxies shown in Appendix~\ref{app:rand_fig1}.
+After the $\alpha$-enhancement, six of the additional galaxies shown seem to have bimodal features: 143882, 167392, 348901, 425719, 439099, and 465255.
+However, none are as prominent as the fiducial galaxy (392276).
+It is worth noting that the post-processing is not in itself responsible for the emergence of bimodality, as it only does so for a fraction of the galaxies shown in Appendix~\ref{app:rand_fig1}.
 Furthermore, if a galaxy had \alphaFe{} slowly and continuously decrease with time, then our $\alpha$-enhancement would not give rise to a bimodality since it is also a continuous adjustment.
-\edit1{Appendix~\ref{app:rand_fig1} also shows the effect of choosing a different redshift at which to apply the enhancement ($z=1$, 1.5, and 2), which does not qualitatively change the bimodal structure in our fiducial galaxy.}
+Appendix~\ref{app:rand_fig1} also shows the effect of choosing a different redshift at which to apply the enhancement ($z=1$, 1.5, and 2), which does not qualitatively change the bimodal structure in our fiducial galaxy.
 
-\edit1{We used \texttt{FOF} and \texttt{SUBFIND} in order to identify substructure \citep{2005Natur.435..629S,2009MNRAS.399..497D}.} We select subhalo 172175 (the \texttt{SUBFIND} ID at snapshot 40) for its resemblance to the Milky Way.
+We used \texttt{FOF} and \texttt{SUBFIND} in order to identify substructure \citep{2005Natur.435..629S,2009MNRAS.399..497D}.
+We select subhalo 172175 (the \texttt{SUBFIND} ID at snapshot 40) for its resemblance to the Milky Way.
 We then studied the main descendant of this subhalo at $z=0$ (subhalo 392276 at snapshot 99).
@@
 The effect of the $\alpha$-enhancement is clear, as it separates the stars that form before and after this gap in ages (star particles which formed before $z=1.5$ are $\alpha$-enhanced, which occurs at an age of $\sim9.5\,\Gyr$).
-\edit1{The middle row shows the same TNG and $\alpha$-enhanced TNG data, but with added uncertainties of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.} When given these errors, the before and after star particles smear such that the two populations significantly overlap in ages.
-\edit1{There is a second population of stars linked to another gap at $\sim8\,\Gyr$, discussed in the text.
+The middle row shows the same TNG and $\alpha$-enhanced TNG data, but with added uncertainties of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.
+When given these errors, the before and after star particles smear such that the two populations significantly overlap in ages.
+There is a second population of stars linked to another gap at $\sim8\,\Gyr$, discussed in the text.
 The lower row shows on the left the Milky Way data and on the right the same TNG data with artificial errors but subsampled to the same number of stars older than $5\,\Gyr$ as in the observations (because the simulation sample has almost no star particles younger than $5\,\Gyr$).
-The limited sample size of the observations makes a direct comparison difficult.}}
+The limited sample size of the observations makes a direct comparison difficult.}
   \label{fig:alpha}
@@
 In our simulated galaxy, there is an age gap at $\sim10.6\,\Gyr$, which we mark with a vertical dashed line in the upper row.
-Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after, \edit1{even in the fiducial case}.
+Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after, even in the fiducial case.
 In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly reduced \MgFe{} than stars which form a short time later.
 
-\edit1{In the middle row, the center and right panels show the simulated galaxies with Gaussian errors of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}, aligning with the observational uncertainties in the APOKASC-3 and APOGEE datasets (see Appendix~\ref{app:obs_err}).
+In the middle row, the center and right panels show the simulated galaxies with Gaussian errors of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}, aligning with the observational uncertainties in the APOKASC-3 and APOGEE datasets (see Appendix~\ref{app:obs_err}).
 The error in \MgFe{} is insignificant, but the age error ($1.25\,\Gyr$ at $10\,\Gyr$) significantly blurs the distribution, particularly across the dashed line that marks the transition between sequences.
-Despite this, the $\alpha$-enhanced galaxy still shows two distinct populations, although their ages now overlap more significantly.}
+Despite this, the $\alpha$-enhanced galaxy still shows two distinct populations, although their ages now overlap more significantly.
 
-\edit1{The upper and middle row shows that there is a potential third population of star particles in the simulation, which is most visible in the $\FeH=-0.25$ and $0\,\dex$ bins (green and red, respectively).
-A minor gap in the upper panels is present at an age of $\sim8\,\Gyr$, which we discuss further in Section~\ref{ssec:evol}.}
+The upper and middle row shows that there is a potential third population of star particles in the simulation, which is most visible in the $\FeH=-0.25$ and $0\,\dex$ bins (green and red, respectively).
+A minor gap in the upper panels is present at an age of $\sim8\,\Gyr$, which we discuss further in Section~\ref{ssec:evol}.
 
-\edit1{The lower row compares Milky Way data (left) with simulations of fiducial (middle) and $\alpha$-enhanced (right) galaxies.
+The lower row compares Milky Way data (left) with simulations of fiducial (middle) and $\alpha$-enhanced (right) galaxies.
 Here, the simulations have been subsampled to match the observed sample size of stars older than $5\,\Gyr$ in each metallicity bin.
@@
 When subsampled with observational errors, the $\FeH=-0.5$ bin in the simulation (orange right panel) very faintly shows a hint of two stacked distributions which might also be present in the $\FeH=-0.25$ bin in the data (orange left panel).
-The limited sample size makes it impossible to draw any strong conclusions.}
+The limited sample size makes it impossible to draw any strong conclusions.
 
@@
 The vertical dashed line in each panel marks the transition at $t\sim3.2\,\Gyr$ from the high- to low-$\alpha$ sequences, as in Figure~\ref{fig:alpha}.
-The upper panel in the left column shows the the SFR (computed for all gas cells in the \edit1{\texttt{SUBFIND} subhalo}).
+The upper panel in the left column shows the the SFR (computed for all gas cells in the \texttt{SUBFIND} subhalo).
 There are two peaks at $t\sim2.5\,\Gyr$ and $t\sim4.5\,\Gyr$ with maximum values of $50\,\Msun/\textrm{yr}$ and $30\,\Msun/\textrm{yr}$, respectively.
@@
 
-\edit1{There is also a more minor period of quiescence at a cosmic time of $\sim6\,\Gyr$, followed by a period of SF at a much lower rate.
-This is likely linked to the third population separated by an age gap at $\sim8\,\Gyr$ seen in Figure~\ref{fig:alpha}.}
+There is also a more minor period of quiescence at a cosmic time of $\sim6\,\Gyr$, followed by a period of SF at a much lower rate.
+This is likely linked to the third population separated by an age gap at $\sim8\,\Gyr$ seen in Figure~\ref{fig:alpha}.
 
@@
 
-\edit1{As discussed in Paper~I, the key to generating an $\alpha$-bimodality is halting star formation within specific metallicity ranges.
+As discussed in Paper~I, the key to generating an $\alpha$-bimodality is halting star formation within specific metallicity ranges.
 A global quiescent period is a sufficient but not necessary condition for the formation of such gaps.
@@
 Notably, we observe a significant drop in the SFR within these metallicity bins, lasting up to $\sim1\,\Gyr$.
-However, because the timing of these metallicity-dependent gaps differs, the total SFR never falls below $\sim10\,\Msunyr$.}
+However, because the timing of these metallicity-dependent gaps differs, the total SFR never falls below $\sim10\,\Msunyr$.
 
@@
   \includegraphics[width=\columnwidth]{392276_zSFH.pdf}
-  \caption{\edit1{Global star formation history (black) compared with the star formation history in narrow metallicity bins, color-coded as in Figure~\ref{fig:fig1}.
+  \caption{Global star formation history (black) compared with the star formation history in narrow metallicity bins, color-coded as in Figure~\ref{fig:fig1}.
 This plot demonstrates that the key condition for generating an $\alpha$-bimodality, the cessation of star formation in specific metallicity ranges, is satisfied.
 The metallicity-dependent SFR drops nearly to zero in every bin for periods extending up to $\sim1\,\Gyr$.
-The timing and duration of metallicity-dependent gaps can vary, preventing the total SFR from falling below $\sim10\,\Msunyr$.}}
+The timing and duration of metallicity-dependent gaps can vary, preventing the total SFR from falling below $\sim10\,\Msunyr$.}
   \label{fig:zSFH}
@@
 Figure~\ref{fig:history} shows that it reaches its second maximum of $30.9\,\Msunyr$ at $4.5\,\Gyr$.
-\edit1{We show in Figure~\ref{fig:zSFH} that the global SF suppression is coincident with a much more dramatic metallicity dependent SF gap, with the SFR dropping nearly to $0\,\Msunyrdex$ in several bins.}
+We show in Figure~\ref{fig:zSFH} that the global SF suppression is coincident with a much more dramatic metallicity dependent SF gap, with the SFR dropping nearly to $0\,\Msunyrdex$ in several bins.
 \end{enumerate}
 
-\edit1{Note that in the Milky Way the bar is estimated to have formed approximately $8\,\Gyr$ ago \citep{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, coinciding with the epoch when the bimodality is observed to emerge \citep{2013A&A...560A.109H,2023MNRAS.525.2208R,2024MNRAS.535..392L}.}
+Note that in the Milky Way the bar is estimated to have formed approximately $8\,\Gyr$ ago \citep{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, coinciding with the epoch when the bimodality is observed to emerge \citep{2013A&A...560A.109H,2023MNRAS.525.2208R,2024MNRAS.535..392L}.
 
@@
 The results showed that simulations featuring a brief quiescent period produced a bimodal abundance distribution.
-Two conditions for the bimodality to arise have to be met: (1) a declining \alphaFe{} with time (here done through our post-processing step, see Figure~\ref{fig:alpha}), and (2) a gap in \edit1{the metallicity-dependent} SFR.
+Two conditions for the bimodality to arise have to be met: (1) a declining \alphaFe{} with time (here done through our post-processing step, see Figure~\ref{fig:alpha}), and (2) a gap in the metallicity-dependent SFR.
 In Paper~I, the gap in SFR was due to a merger, but here we argue it is due to the formation of a bar.
@@
 
-\edit1{This global quiescent period is symptomatic of a more dramatic reduction in the star formation rate in narrow metallicity bins, which almost entirely vanishes (Figure~\ref{fig:zSFH}).
+This global quiescent period is symptomatic of a more dramatic reduction in the star formation rate in narrow metallicity bins, which almost entirely vanishes (Figure~\ref{fig:zSFH}).
 As we showed in Paper~I, it is the metallicity-dependent quiescence in the presence of a declining gas-phase \MgFe{} -- not global quiescence -- that leads to an $\alpha$-bimodality.
@@
 In the real universe, a global quiescent period of a duration of $\sim300\,\Myr$ would lead to a reduction in enrichment from Type~II relative to Type~Ia SNe leads to a lower rate of Mg production.
-The typical lifetime of a Type~II SN progenitor in this model is $\sim40\,\Myr$ \citep{2018MNRAS.473.4077P}, and so the hundreds of Myr of suppressed SF would be short enough to restrict the production of $\alpha$-elements.}
+The typical lifetime of a Type~II SN progenitor in this model is $\sim40\,\Myr$ \citep{2018MNRAS.473.4077P}, and so the hundreds of Myr of suppressed SF would be short enough to restrict the production of $\alpha$-elements.
 
@@
 The star particles which form directly after the dashed line when the SFR has just recovered have a slightly lower \MgFe{} than stars which form later on, by about $0.1$ to $0.2\,\dex$.
-\edit1{We argue that it is plausible that} during the period of suppressed star formation, the \alphaFe{} ratio of the star-forming gas drops sharply due to the reduced contribution of Type~II relative to Type~Ia SNe.
+We argue that it is plausible that during the period of suppressed star formation, the \alphaFe{} ratio of the star-forming gas drops sharply due to the reduced contribution of Type~II relative to Type~Ia SNe.
 Later, the \alphaFe{} of the gas will recover when the SFR also recovers, but there is a brief window when old, low-$\alpha$ stars can form.
@@
 \subsection{Direct Comparison to Observations}\label{ssec:compare_obs}
-\edit1{We attempted a direct comparison between our TNG galaxy and the Milky Way in the lower row of Figure~\ref{fig:alpha} (see Section~\ref{ssec:alpha_time}).
+We attempted a direct comparison between our TNG galaxy and the Milky Way in the lower row of Figure~\ref{fig:alpha} (see Section~\ref{ssec:alpha_time}).
 In the simulations, the presence of the bimodality is obvious from a stacked distribution.
 However, this distribution is not obvious in the observations, primarily because the sample size of observations at old ages where the bimodality is present ($>5\,\Gyr$) is quite small.
-Nonetheless, the presence of a clean gap in stellar ages between the high- and low-$\alpha$ is completely washed out by the age uncertainties.}
+Nonetheless, the presence of a clean gap in stellar ages between the high- and low-$\alpha$ is completely washed out by the age uncertainties.
 
@@
 In our galaxy here, there is indeed a brief burst in AGN accretion at the time of the merger (middle panel of Figure~\ref{fig:history}).
-Based on this burst, it is also reasonable to suspect that AGN activity is also responsible for the quiescent period in our galaxy, \edit1{noting that the real cause of the formation of the $\alpha$-bimodality is a metallicity-dependent quiescent period (see Paper~I and Figure~\ref{fig:zSFH})}.
+Based on this burst, it is also reasonable to suspect that AGN activity is also responsible for the quiescent period in our galaxy, noting that the real cause of the formation of the $\alpha$-bimodality is a metallicity-dependent quiescent period (see Paper~I and Figure~\ref{fig:zSFH}).
 However, we argued in Section~\ref{ssec:sequence_of_events} that the cause of the localized spike in the BH accretion rate is not due to a merger but instead due to the formation/strengthening of a bar.
-\edit1{This connection is further supported by estimates that the Milky Way's bar formed $\sim8\,\Gyr$ ago \citep[e.g.,][]{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, roughly concurrent with the formation of the bimodality \citep{2013A&A...560A.109H,2023MNRAS.525.2208R,2024MNRAS.535..392L}.}
+This connection is further supported by estimates that the Milky Way's bar formed $\sim8\,\Gyr$ ago \citep[e.g.,][]{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, roughly concurrent with the formation of the bimodality \citep{2013A&A...560A.109H,2023MNRAS.525.2208R,2024MNRAS.535..392L}.
 
@@
 A definitive account, difficult with the current simulation outputs because of its sparse snapshot spacing, requires further work.
-\edit1{We also delay to future work the cause of the secondary quiescence period at $\sim6\,\Gyr$, briefly discussed in Section~\ref{ssec:evol}.}
+We also delay to future work the cause of the secondary quiescence period at $\sim6\,\Gyr$, briefly discussed in Section~\ref{ssec:evol}.
 
@@
 
-The formation of the bimodality, when the galaxy transitions from producing high- to low-\MgFe{} star particles (Figure~\ref{fig:alpha}), is coincident with \edit1{both a global and metallicity-dependent suppression of star formation (Figures~\ref{fig:history} and \ref{fig:zSFH})}.
+The formation of the bimodality, when the galaxy transitions from producing high- to low-\MgFe{} star particles (Figure~\ref{fig:alpha}), is coincident with both a global and metallicity-dependent suppression of star formation (Figures~\ref{fig:history} and \ref{fig:zSFH}).
 This suppression of star formation is preceded by the formation of a bar and subsequent AGN activity (Figure~\ref{fig:seq}).
-\edit1{This scenario is plausible for the Milky Way, as recent estimates indicate that the bar formed around $8\,\Gyr$ ago \citep{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, coinciding with the onset of the bimodality.}
+This scenario is plausible for the Milky Way, as recent estimates indicate that the bar formed around $8\,\Gyr$ ago \citep{2019MNRAS.490.4740B,2024MNRAS.530.2972S}, coinciding with the onset of the bimodality.
 
-\edit1{The lack of star formation in a narrow metallicity bin in the presence of a decline in \MgFe{} naturally leads to a gap in the present-day distribution of \MgFe{} (see Paper~I).
+The lack of star formation in a narrow metallicity bin in the presence of a decline in \MgFe{} naturally leads to a gap in the present-day distribution of \MgFe{} (see Paper~I).
 However, in the fiducial TNG  model, the decline in \MgFe{} is not rapid enough during the period of quiescence to produce an $\alpha$-bimodality.
 Our post-processing $\alpha$-enhancement artificially injects this declination.
-In the real universe, a global reduction in the SFR may expedite the drop in \MgFe{} since the number of Type~II relative to Type~Ia SNe would drop.}
+In the real universe, a global reduction in the SFR may expedite the drop in \MgFe{} since the number of Type~II relative to Type~Ia SNe would drop.
 
@@
 Regardless of this scenario's relevance to the Milky Way, we also predict that the presence of a bar in external galaxies is correlated with the presence of an $\alpha$-bimodality.
-\edit1{Because of observational errors in age, it is not possible to make a direct comparison between the simulated galaxy and dataset (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).
-In the future, more numerous and precise age estimates of old, metal-poor stars may be able to distinguish the formation scenarios of the $\alpha$-bimodality.}
+Because of observational errors in age, it is not possible to make a direct comparison between the simulated galaxy and dataset (Figure~\ref{fig:alpha} and Section~\ref{ssec:compare_obs}).
+In the future, more numerous and precise age estimates of old, metal-poor stars may be able to distinguish the formation scenarios of the $\alpha$-bimodality.
 
-\begin{acknowledgements}
-  \edit1{We would like to thank the referee for a thoughtful and helpful report.} We would like to thank Marc Pinsonneault and Jesse van de Sande for helpful discussions, and M.
+\section*{acknowledgements}
+  We would like to thank the referee for a thoughtful and helpful report.
+We would like to thank Marc Pinsonneault and Jesse van de Sande for helpful discussions, and M.
 Pinsonneault for sharing early access to the APOKASC-3 dataset.
@@
 
-\edit1{We acknowledge the use of OpenAI’s ChatGPT and Anthropic's Claude for assistance in editing this manuscript for clarity and conciseness and in generating small analysis scripts and code snippets.}
+We acknowledge the use of OpenAI’s ChatGPT and Anthropic's Claude for assistance in editing this manuscript for clarity and conciseness and in generating small analysis scripts and code snippets.
 
-\end{acknowledgements}
+% \end{acknowledgements}
 
@@
 \section{Observational Errors}\label{app:obs_err}
-\edit1{In Figure~\ref{fig:alpha}, we assumed observational errors of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.
+In Figure~\ref{fig:alpha}, we assumed observational errors of $12.5\%$ in age and $0.015\,\dex$ in \MgFe{}.
 In Figure~\ref{fig:obs_err}, we plot the quoted observational errors of the APOKASC-3 (left) and ASPCAP (right) datasets, showing both \FeH{} and \MgFe{} (blue and orange, respectively).
@@
 As a dashed line we show our $25\%$ age error cut for stars plotted in Figure~\ref{fig:obs_err}.
-Our assumed errors are generally consistent with the errors quoted in the dataset, with a conservative estimate for the abundance errors.}
+Our assumed errors are generally consistent with the errors quoted in the dataset, with a conservative estimate for the abundance errors.
 
@@
   \includegraphics[width=\columnwidth]{obs_error.pdf}
-  \caption{The observational errors of \edit1{astroseismic ages from APOKASC-3} (left) and \edit1{abundances from ASPCAP DR17} (right).
-We show, on the left, a line indicating a $12.5\%$ error in observed age and on the right a vertical line indicating a \edit1{$0.01$ and $0.015\,\dex$ error in \FeH{} and \MgFe{}, respectively}.
+  \caption{The observational errors of astroseismic ages from APOKASC-3 (left) and abundances from ASPCAP DR17 (right).
+We show, on the left, a line indicating a $12.5\%$ error in observed age and on the right a vertical line indicating a $0.01$ and $0.015\,\dex$ error in \FeH{} and \MgFe{}, respectively.
 On the left, a dashed line indicates the $25\%$ error cut used for inclusion in Figure~\ref{fig:alpha}.}
@@
 \section{Random Selection of Subhalos}\label{app:rand_fig1}
-\edit1{In Figure~\ref{fig:app0}, we show the abundance plane of our fiducial galaxy at $z=0$.
+In Figure~\ref{fig:app0}, we show the abundance plane of our fiducial galaxy at $z=0$.
 This reproduces the middle column of Figure~\ref{fig:fig1}.
@@
 Qualitatively, the time at which the $\alpha$-enhancement is applied does not alter whether substructure arises in this plane.
-However, when it is applied at lower $z$, the peaks between modes do appear to be slightly further apart.}
+However, when it is applied at lower $z$, the peaks between modes do appear to be slightly further apart.
 
-\edit1{We show the same figure but with an additional random selection of 16 galaxies in the Milky Way-progenitor mass sample as a figure set (17 images), which is available in the online journal.
+We show the same figure but with an additional random selection of 16 galaxies in the Milky Way-progenitor mass sample as a figure set (17 images), which is available in the online journal.
 Six additional galaxies (143882, 167392, 348901, 425719, 439099, and 465255) display bimodalities, though none as prominent as the main galaxy studied in this work.
@@
 In general, the $\alpha$-enhancement increases the strength of substructure in the abundance planes.
-The fact that bimodalities like in the main galaxy studied in this work do not universally appear in $\alpha$-enhanced galaxies indicates that the $\alpha$-enhancement is not solely responsible for the bimodality.}
+The fact that bimodalities like in the main galaxy studied in this work do not universally appear in $\alpha$-enhanced galaxies indicates that the $\alpha$-enhancement is not solely responsible for the bimodality.
 
-\edit1{The timing of the $\alpha$-enhancement does not have a major effect on our fiducial galaxy (Figure~\ref{fig:app0}).
+The timing of the $\alpha$-enhancement does not have a major effect on our fiducial galaxy (Figure~\ref{fig:app0}).
 However, for some (e.g., the green $\FeH=-0.25$ bin in 439099), structure arises only when the $\alpha$-enhancement is applied at sufficiently low redshift.
-We interpret this as the presence of some substructure inducing activity between $z=1$ and 2.}
+We interpret this as the presence of some substructure inducing activity between $z=1$ and 2.
 
@@
   \includegraphics[width=\textwidth]{app_392276.pdf}
-  \caption{\edit1{Abundance plane of the fiducial galaxy at $z=0$ and the effects of $\alpha$-enhancement applied at different redshifts.
+  \caption{Abundance plane of the fiducial galaxy at $z=0$ and the effects of $\alpha$-enhancement applied at different redshifts.
 The leftmost panel shows the fiducial galaxy without enhancement, reproducing the middle column of Figure~\ref{fig:fig1}.
@@
 This figure is part of a set of 17 images available in the online journal, showing similar plots for 16 additional galaxies from our Milky Way-progenitor mass sample.
-The varied responses to $\alpha$-enhancement across the sample, with only six additional galaxies (143882, 167392, 348901, 425719, 439099, and 465255) displaying bimodalities, suggest that while $\alpha$-enhancement generally increases substructure, it is not solely responsible for creating bimodalities in abundance planes.}}
+The varied responses to $\alpha$-enhancement across the sample, with only six additional galaxies (143882, 167392, 348901, 425719, 439099, and 465255) displaying bimodalities, suggest that while $\alpha$-enhancement generally increases substructure, it is not solely responsible for creating bimodalities in abundance planes.}
   \label{fig:app0}
